---
title: "R Notebook"
output: html_notebook
---
## Read met file.
## Read Observed data
## calculate Tt and Ttsum

```{r Load, warning=FALSE, fig.height=8, fig.width=8}
# install.packages("zoo")
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)
```
## Load metdata with Tt and Pmean for each experiment
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

metTt.address <- "D:\\R\\TtAll\\"
met <- read.table(paste0(metTt.address, "TtAll.txt"), 
                      header = TRUE)
metTtData <- met %>% mutate(Clock.Today = dmy(Clock.Today))%>%
  dplyr::filter(Tb==1)%>%
  mutate()
metTtData
str(metTtData)


```

### Load flowering data
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

flower.address <- "D:\\R\\"
flowerData <- read.table(paste0(flower.address, "Flowering.txt"),
                      header = TRUE)
str(flowerData)
flower<- flowerData %>%
  mutate(StartDate=dmy(StartDate),BVDate=dmy(BVDate),FloDate=dmy(FloDate)) %>%
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) 
summary(flower)

```
#### calculated thremal time between Startdate to Buds visual date
### merge two table together(Buds and Tt)
```{r}
ungroup.rowwise_df <- function(x) {
  class(x) <- c( "tbl_df", "data.frame")
  x
}


Uniflo <- unique(flower$ExpUnitCode)

Buds.all <- data.frame()
 
for(i in 1:length(Uniflo))
{

 # print(i)
  
 flower.sub <- flower %>%
   filter(ExpUnitCode==Uniflo[i]) 
  
 StDate <- ymd(flower.sub$StartDate)
 EndDate <- ymd(flower.sub$BVDate)
  
Met.sub<-metTtData %>%
  filter(between(Clock.Today,StDate,EndDate))
  

tt.df <- Met.sub %>% 
  rowwise() %>%
  mutate(ExpUnitCode=flower.sub$ExpUnitCode,
         Water=flower.sub$Water,
         GrowthSeason=flower.sub$GrowthSeason,
         Rotation=flower.sub$Rotation) %>%
         ungroup.rowwise_df()%>%
         mutate( Tt_beta_sum_BV = cumsum(TTbeta),
                  Tt_fick_sum_BV=cumsum(TTfick),
                  Tt_broken_sum_BV= cumsum(TTbroken))%>%
         mutate(Ppm_BV=mean(Pp), Tmean_BV=mean(mean))
 Buds.all <- rbind(Buds.all,tt.df)
}

```

```{r}
Buds<-flower%>%
  mutate(Clock.Today=ymd(BVDate))
Buds.all
merge.BV<-merge(Buds.all,Buds,by=c("Clock.Today","ExpUnitCode","Water","GrowthSeason","Rotation"))
metPp<-metTtData%>%
  dplyr::select(-year,-day,-rain,-maxt,-mint,-mean,-radn,-wind,-vp,-Tb,-Tbb,-TTbroken,-TbF,-TTfick,-TTbeta)
merge.BVs<-merge(merge.BV, metPp, by.x=c("StartDate"), by.y=c("Clock.Today"))%>%
  mutate(Pps=Pp.y)%>%
  mutate(Trend=ifelse(Ppm_BV>Pps,"Inc","Dec"))
```

#### calculated thremal time between Startdate to Flowering date
### merge two table together(flowering and Tt)
```{r}
flower1<-flower%>%
  dplyr::filter(!is.na(FloDate)) 
  
ungroup.rowwise_df <- function(x) {
  class(x) <- c( "tbl_df", "data.frame")
  x
}


Uniflo <- unique(flower1$ExpUnitCode)

flower.all <- data.frame()
 
for(i in 1:length(Uniflo))
{

 # print(i)
  
 flower.sub <- flower1 %>%
   filter(ExpUnitCode==Uniflo[i]) 
  
 StDate <- ymd(flower.sub$StartDate)
 EndDate <- ymd(flower.sub$FloDate)
  
Met.sub<-metTtData %>%
  filter(between(Clock.Today,StDate,EndDate))
  

tt.df <- Met.sub %>% 
  rowwise() %>%
  mutate(ExpUnitCode=flower.sub$ExpUnitCode,
         Water=flower.sub$Water,
         GrowthSeason=flower.sub$GrowthSeason,
         Rotation=flower.sub$Rotation) %>%
         ungroup.rowwise_df()%>%
         mutate( Tt_beta_sum_fl= cumsum(TTbeta),
                  Tt_fick_sum_fl=cumsum(TTfick),
                  Tt_broken_sum_fl= cumsum(TTbroken))%>%
         mutate(Ppm_fl=mean(Pp), Tmean_fl=mean(mean))
 flower.all <- rbind(flower.all,tt.df)
}

```

```{r}
flowering<-flower1%>%
        mutate(Clock.Today=ymd(FloDate))
flower.all
merge.fl<-merge(flower.all,flowering,by=c("Clock.Today","ExpUnitCode","Water","GrowthSeason","Rotation"))
metPp<-metTtData%>%
  dplyr::select(-year,-day,-rain,-maxt,-mint,-mean,-radn,-wind,-vp,-Tb,-Tbb,-TTbroken,-TbF,-TTfick,-TTbeta)
merge.fls<-merge(merge.fl, metPp, by.x=c("StartDate"), by.y=c("Clock.Today"))%>%
  mutate(Pps=Pp.y)%>%
  mutate(Trend=ifelse(Ppm_fl>Pps,"Inc","Dec"))


```
##load and plot Buds visual data 
```{r}
# flowerD<-flowerData%>%
#   dplyr::filter(Water=="irr")
# flowerD%>%
#   ggplot(aes(x=StartDate, y=Days, colour=factor(Name)))+geom_point(size=2)+theme_bw()+xlab("Date")+ylab("Days to buds visual")+
#  facet_wrap(~Stage)+
#   theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
#  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
####plot Buds visual data 
```{r}
merge.BVs
BudsD<-merge.BVs%>%
  dplyr::filter(Water=="irr")
BudsD%>%
  ggplot(aes(x=Ppm_BV, y=Tt_beta_sum_BV, colour=factor(Name)))+geom_point(size=2)+theme_bw()+xlab("Mean photoperiod ")+ylab("Tt0-bv")+
 facet_wrap(~Stage)+theme(legend.title=element_blank())+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
```{r}
merge.BVs
BudsD<-merge.BVs%>%
  dplyr::filter(Water=="irr")
  #dplyr::filter(Defoliation=="LL")

BudsD%>%
  ggplot(aes(x=Ppm_BV, y=Tt_beta_sum_BV, colour=factor(Name)))+geom_point(size=2)+theme_bw()+xlab("Mean photoperiod ")+ylab("Tt0-bv")+
 facet_grid(Trend~Stage)+theme(legend.title=element_blank())+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```




```{r}
# flowerD1<-flowerD%>%dplyr::filter(Stage!="Seedling")
# model1<-lm(flowerD1$Tt0.bv~flowerD1$Ps)
# model2<-lm(flowerD1$Tt0.bv~flowerD1$Psbv)
# summary(model1)
# summary(model2)
# plot(flowerD1$Tt0.bv~flowerD1$Ps)
# abline(model1)
```

```{r}
flowerD<-merge.fls%>%
  dplyr::filter(Water=="irr")
  #dplyr::filter(Defoliation=="LL")
flowerD%>%
  ggplot(aes(x=Ppm_fl, y=Tt_broken_sum_fl, colour=factor(Name)))+geom_point(size=2)+theme_bw()+xlab("Mean photoperiod ")+ylab("Tt0-fl")+
 facet_wrap(~Stage)+theme(legend.title=element_blank())+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```

```{r}
flowerD1<-flowerD%>%dplyr::filter(Stage!="Seedling")
model1<-lm(flowerD1$Tt_broken_sum_fl~flowerD1$Ppm_fl)
summary(model1)
plot(flowerD1$Tt_broken_sum_fl~flowerD1$Ppm_fl)
abline(model1)
```


```{r}
flowerD<-merge.fls%>%
  dplyr::filter(Water=="irr")
  #dplyr::filter(Defoliation=="LL")
flowerD%>%
  ggplot(aes(x=Ppm_fl, y=Tt_broken_sum_fl, colour=factor(Name)))+geom_point(size=2)+theme_bw()+xlab("Mean photoperiod ")+ylab("Tt0-fl")+
 facet_grid(Trend~Stage)+ theme(legend.title=element_blank())+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneValidation.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
summary(df)
head(df) # simulation results
```

# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"_Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)

# myDb %>%
#   dplyr::select(Name) %>%
#   unique()

```
## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,Lucerne.Phenology.FloweringDaysAfterCutting.Value..,Lucerne.Phenology.DaysAfterCutting.Value..) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  mutate(Floweringdays=as.factor(Lucerne.Phenology.FloweringDaysAfterCutting.Value..),Cuttingdays= as.factor(Lucerne.Phenology.DaysAfterCutting.Value..))%>%
  dplyr::select(-Lucerne.Phenology.FloweringDaysAfterCutting.Value..,-Lucerne.Phenology.DaysAfterCutting.Value..)

head(simD)
simD
obsF<-flower %>%
  mutate(Clock.Today= ymd(FloDate))
head(obsF)

mergedf<-merge(obsF,simD,by=c("Name","Clock.Today"))

summary(mergedf)
str(mergedf)
mergedf

```

```{r,fig.height=5, fig.width=7}

mergedf%>%
 dplyr::filter(Floweringdays!=0)%>%
ggplot(aes(x=Days,y=Floweringdays, colour=factor(Name)))+geom_point(size=2)+theme_bw()+xlab("Observed")+ ylab("Predicted")+
# facet_wrap(~Name)+
  theme(legend.title=element_blank())+
 #geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```

## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r, round(r2*100,1))

  return(out)

}
```


```{r}
mergedf %>%
  mutate(Observed= as.numeric(Days))%>%
  mutate(Predicted=as.numeric(Floweringdays))%>%
dplyr::filter(Collection=="2014_2018")%>%
group_by(Name) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 


```



