---
title: "R Notebook"
output: html_notebook
---

###Canopy analysis

```{r Load, warning=FALSE, fig.height=8, fig.width=8}
# install.packages("zoo")
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)
library(lme4)
library(reshape2)
```
## lode observed data
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsAll <- read.table(paste0(obsData, "ObsAll.txt"),
                   header = TRUE)
obsA<- obsAll %>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))
  
summary(obsA)
obsA
```
#Load Tt and Join Observed data together
##Select LAI variable
```{r}
upDir <- "D:/R/"
obsData <- "D:/R/TtAll/"

Tt<- read.table(paste0(obsData, "df.all.txt"),
               header = TRUE)
TtA <- Tt %>% mutate(Clock.Today=dmy(Clock.Today), ExpUnitCode=as.factor(ExpName))
TtA
ObsL.Raw <-merge(obsA,TtA,by=c("Clock.Today","ExpUnitCode"))
ObsL<-ObsL.Raw%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))%>%
  dplyr::filter(Water.x=="irr")%>%
  dplyr::filter(Defoliation.x=="LL")%>%
  dplyr::filter(FD.x=="FD5")%>%
  dplyr::filter(Variable=="LAI"|Variable=="NodeNumber")%>%
  dplyr::filter(Tb==1)
  

summary(ObsL)
```



```{r}
ObsLF<-ObsL%>%
  dplyr::filter(Name!="Iversen_8Waterirr"|GrowthRotation!="11")%>%
  dplyr::filter(Name!="Iversen_8Waterirr"|GrowthRotation!="22")%>%
  dplyr::filter(Name!="Iversen_8Waterirr"|GrowthRotation!="31")%>%
  dplyr::filter(Name!="Iversen_8Waterirr"|GrowthSeason.x!="4")%>%
  dplyr::filter(Name!="Iversen_8Waterirr"|GrowthRotation!="57")%>%
  dplyr::filter(Name!="Iversen_8Waterirr"|GrowthRotation!="61")%>%
 dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="14")%>%
 dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthSeason.x!="3")%>%
 dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthSeason.x!="4")%>%
 dplyr::filter(Name!="Iversen_9SowingDateSD1Waterirr"|GrowthRotation!="14")%>%
 dplyr::filter(Name!="Iversen_9SowingDateSD2Waterirr"|GrowthRotation!="21")%>%
 dplyr::filter(Name!="Iversen_9SowingDateSD2Waterirr"|GrowthRotation!="13")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD3Waterirr"|GrowthRotation!="21")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD4Waterirr"|GrowthRotation!="21")


```

# Create and test interpolation function 

###Node appearance data preparation
###Node appearance interpolate for each rotation
```{r}

# add function to "turn-off" rowise() in dplyr. FIXME: maybe there's a better/simpler solution?

UniExp <- unique(ObsLF$ExpUnitCode)

Inte.df <- data.frame()
  
for(i in 1:length(UniExp))
{
  
  ObsLA<-ObsLF%>%
   filter(ExpUnitCode==UniExp[i])
  
 LN<-ObsLA%>%
  unique()%>%
  tidyr::spread(Variable,Observed)
 
 LN.data<-LN%>%
  mutate( NodeNumber.y=approx(LN$Clock.Today, LN$NodeNumber, xout =LN$Clock.Today, 
         method="linear", 
         rule = 2)$y)##interpolate function 
  

 Inte.df <- rbind(Inte.df, LN.data)

}

summary(Inte.df)
Inte.df
#write.csv(df.all,"D:/R/TtAll/df.all.csv", row.names = FALSE)

```
###Plot LAI against Nodenumber
##Regrowth
```{r,fig.height=7, fig.width=10}
phyll <- "D:\\R\\"
StartGrazing <- read.table(paste0(phyll, "ExperimentList.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(GrowthRotation= as.factor(paste0(GrowthSeason,Rotation)))
Inte.df.Pp<- merge(StartGrazing1,Inte.df,by=c("Name","Collection","GrowthRotation"))


Leaf_Node<-Inte.df.Pp%>%
  dplyr::filter(LAI!=is.na(LAI))%>%
  dplyr::filter(Collection!="2010_2012")%>%
  dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="13")
df<-data.frame(a=c(2, 4.3, 7.8, 10,11),b=c(0, 1, 4, 6,7))
dfs<-data.frame(c=c(6,7.5,10.5,11),d=c(0,1,3,3.4))
Leaf_Node%>%
 dplyr::filter(NodeNumber.y<=11)%>%
  #dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  ggplot(aes(x=NodeNumber.y,y=LAI, color=Name))+theme_bw()+xlab("Node Number")+ylab("LAI(m^2/m^2)")+ 
  geom_line(data=df,aes(x=a,y=b), color="red")+
  geom_line(data=dfs,aes(x=c,y=d),color="blue")+
  geom_point(size=2)+
  #geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  #geom_text()+
  facet_wrap(~Stage,ncol=1)+
  #facet_grid(Trend~Stage)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
  
```

####analysis
```{r}
Leaf_Node1<-Leaf_Node%>%
  dplyr::filter(Stage!="Seedling")
x=Leaf_Node1$NodeNumber.y
y=Leaf_Node1$LAI

#mdl1 <- lm(y ~ x, data = Leaf_Node1)
#mdl2 <- lm(y ~ x + I(x^2), data = Leaf_Node1)
#mdl3 <- lm(y ~ x + I(x^2) + I(x^3), data = Leaf_Node1)
mdl4 <- lm(y ~ I(x^2), data = Leaf_Node1)
#mdl5<-lm(y ~ poly(x, 2, raw=TRUE),data = Leaf_Node1 )
summary(mdl4)

prd <- data.frame(x = seq(2, 14, by = 0.1))

result <- prd
#result$mdl1 <- predict(mdl1, newdata = prd)
#result$mdl2 <- predict(mdl2, newdata = prd)
#result$mdl3 <- predict(mdl3, newdata = prd)
result$mdl4 <- predict(mdl4, newdata = prd)
#result$mdl5 <- predict(mdl5, newdata = prd)

result <-  melt(result, id.vars = "x", variable.name = "model",
                value.name = "fitted")
ggplot(result, aes(x = x, y = fitted)) +
  theme_bw() +
  facet_wrap(~Stage,ncol=2)+
  geom_point(data = Leaf_Node1, aes(x = x, y = y)) +xlab("Main node number")+ylab("LAI (m^2/m^2)")+
  geom_line(aes(colour = model), size = 1)+
  theme(legend.title=element_blank(),legend.position = "blank")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```
###LAI aganist node number

```{r,fig.height=6, fig.width=10}
Leaf_Nodef<-Leaf_Node%>%
  dplyr::filter(Name=="Iversen_8Waterirr")%>%
  dplyr::filter(NodeNumber.y<=11)

Leaf_Nodef%>%
  ggplot(aes(x=NodeNumber.y, y=LAI))+geom_point(size=2)+theme_bw()+ylab("LAI (m^2/m^2)")+xlab("Node number")+ 
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
 facet_grid(GrowthSeason.x~Rotation.x)+ggtitle("Iversen_8Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
```{r,fig.height=6, fig.width=10}
Leaf_Node2<-Leaf_Node%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  dplyr::filter(NodeNumber.y<=11)

Leaf_Node2%>%
  ggplot(aes(x=NodeNumber.y, y=LAI))+geom_point(size=2)+theme_bw()+ylab("LAI (m^2/m^2)")+xlab("Node number")+ 
 geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  #stat_smooth(method="nls",formula =  y~a*exp(-x*b),method.args=list(start=c(a=2,b=2)),se=F,color="red")+
  #stat_smooth(method="lm",formula =  y~exp(-x),se=F,color="blue")
 facet_grid(GrowthSeason.x~Rotation.x)+ggtitle("Iversen_91DefoliationLL")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
```{r,fig.height=4, fig.width=10}
Leaf_Node3<-Leaf_Node%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD1Waterirr")%>%
  dplyr::filter(NodeNumber.y<=11)

Leaf_Node3%>%
  ggplot(aes(x=NodeNumber.y, y=LAI))+geom_point(size=2)+theme_bw()+ylab("LAI (m^2/m^2)")+xlab("Node number")+ 
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  #stat_smooth(method="nls",formula =  y~a*exp(-x*b),method.args=list(start=c(a=2,b=2)),se=F,color="red")+
  #stat_smooth(method="lm",formula =  y~exp(-x),se=F,color="blue")
 facet_grid(GrowthSeason.x~Rotation.x)+ggtitle("Iversen_9SowingDateSD1Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
```{r,fig.height=3, fig.width=10}
Leaf_Node4<-Leaf_Node%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD2Waterirr")%>%
  dplyr::filter(NodeNumber.y<=11)

Leaf_Node4%>%
  ggplot(aes(x=NodeNumber.y, y=LAI))+geom_point(size=2)+theme_bw()+ylab("LAI (m^2/m^2)")+xlab("Node number")+ 
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  #stat_smooth(method="nls",formula =  y~a*exp(-x*b),method.args=list(start=c(a=2,b=2)),se=F,color="red")+
  #stat_smooth(method="lm",formula =  y~exp(-x),se=F,color="blue")
 facet_grid(GrowthSeason.x~Rotation.x)+ggtitle("Iversen_9SowingDateSD2Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```

```{r,fig.height=3, fig.width=10}
Leaf_Node5<-Leaf_Node%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD3Waterirr")%>%
  dplyr::filter(NodeNumber.y<=11)

Leaf_Node5%>%
  ggplot(aes(x=NodeNumber.y, y=LAI))+geom_point(size=2)+theme_bw()+ylab("LAI (m^2/m^2)")+xlab("Node number")+ 
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  #stat_smooth(method="nls",formula =  y~a*exp(-x*b),method.args=list(start=c(a=2,b=2)),se=F,color="red")+
  #stat_smooth(method="lm",formula =  y~exp(-x),se=F,color="blue")
 facet_grid(GrowthSeason.x~Rotation.x)+ggtitle("Iversen_9SowingDateSD3Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
```{r,fig.height=4, fig.width=10}
Leaf_Node6<-Leaf_Node%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD4Waterirr")%>%
  dplyr::filter(NodeNumber.y<=11)

Leaf_Node6%>%
  ggplot(aes(x=NodeNumber.y, y=LAI))+geom_point(size=2)+theme_bw()+ylab("LAI (m^2/m^2)")+xlab("Node number")+ 
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  #stat_smooth(method="nls",formula =  y~a*exp(-x*b),method.args=list(start=c(a=2,b=2)),se=F,color="red")+
  #stat_smooth(method="lm",formula =  y~exp(-x),se=F,color="blue")
 facet_grid(GrowthSeason.x~Rotation.x)+ggtitle("Iversen_9SowingDateSD4Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```


```{r,fig.height=4, fig.width=10}
Leaf_Node7<-Leaf_Node%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(NodeNumber.y<=11)

Leaf_Node7%>%
  ggplot(aes(x=NodeNumber.y, y=LAI))+geom_point(size=2)+theme_bw()+ylab("LAI (m^2/m^2)")+xlab("Node number")+ 
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  #stat_smooth(method="nls",formula =  y~a*exp(-x*b),method.args=list(start=c(a=2,b=2)),se=F,color="red")+
  #stat_smooth(method="lm",formula =  y~exp(-x),se=F,color="blue")
 facet_grid(GrowthSeason.x~Rotation.x)+ggtitle("Iversen_121DefoliationLLFDFD5")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
```{r}
SlopeLN<-Leaf_Node%>%
  dplyr::filter(NodeNumber.y<=11)%>%
  group_by(Name,GrowthSeason.x,Rotation.x,Tmean,Ppm,Stage,Ps,Collection,GrowthRotation,Trend)%>%
 do(mod = lm(LAI~NodeNumber.y,data=.)) %>%
  mutate(slopeLN = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)

SlopeLN%>%
  dplyr::filter(Stage!="Seedling")%>%
   ggplot(aes(x=Tmean, y=slopeLN,color=Name,label=GrowthRotation))+
  #geom_point(size=2)+
  geom_text()+
  theme_bw()+ylab("LAI per node")+xlab("Photoperiod (h)")+ 
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  #stat_smooth(method="nls",formula =  y~a*exp(-x*b),method.args=list(start=c(a=2,b=2)),se=F,color="red")+
  #stat_smooth(method="lm",formula =  y~exp(-x),se=F,color="blue")+
 #facet_wrap(~Trend,ncol=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))


```


###leaf and node appearance in the same Tt before interpolate
```{r,fig.height=6, fig.width=10}
obsLAI<-ObsLF%>%
  dplyr::filter(Name=="Iversen_8Waterirr")%>%
  dplyr::filter(Variable=="LAI")
obsNode<-ObsLF%>%
  dplyr::filter(Name=="Iversen_8Waterirr")%>%
  dplyr::filter(Variable=="NodeNumber")
obsLAI%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd)")+ylab("Node Number")+ 
  geom_point(data=obsNode, aes(x=Tt_broken_sum, y=Observed),colour="green",size=3)+
  #geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  #stat_smooth(method="nls",formula =  y~a*exp(-x*b),method.args=list(start=c(a=2,b=2)),se=F,color="red")+
  #stat_smooth(method="lm",formula =  y~exp(-x),se=F,color="blue")
 facet_grid(GrowthSeason.x~Rotation.x)+ggtitle("Iversen_8Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
#Iversen_91DefoliationLL
```{r,fig.height=6, fig.width=10}
obsLAI1<-ObsL%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  dplyr::filter(Variable=="LAI")
obsNode1<-ObsL%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  dplyr::filter(Variable=="NodeNumber")
obsLAI1%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd)")+ylab("Node Number ")+ggtitle("Iversen_91DefoliationLL")+
  geom_point(data=obsNode1, aes(x=Tt_broken_sum, y=Observed),colour="green",size=3)+
 facet_grid(GrowthSeason.x~Rotation.x)+
  #geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
 
```
##Iversen_9SowingDateSD1Waterirr
```{r,fig.height=4, fig.width=10}

obsLAI2<-ObsLF%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD1Waterirr")%>%
  dplyr::filter(Variable=="LAI")
obsNode2<-ObsLF%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD1Waterirr")%>%
  dplyr::filter(Variable=="NodeNumber")
 
obsLAI2%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd)")+ylab("LAI (m^2/m^2) ")+ggtitle("Iversen_9SowingDateSD1Waterirr")+
  geom_point(data=obsNode2, aes(x=Tt_broken_sum, y=Observed),colour="green",size=3)+
  geom_smooth(method = "glm",family = gaussian(link="log"), aes(colour = "Exponential"))+
 facet_grid(GrowthSeason.x~Rotation.x)+
  #geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="black")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
 
```
##Iversen_9SowingDateSD2Waterirr
```{r,fig.height=3, fig.width=10}

obsLAI3<-ObsLF%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD2Waterirr")%>%
  dplyr::filter(Variable=="LAI")
obsNode3<-ObsLF%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD2Waterirr")%>%
  dplyr::filter(Variable=="NodeNumber")
 
obsLAI3%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd)")+ylab("LAI (m^2/m^2) ")+ggtitle("Iversen_9SowingDateSD2Waterirr")+
  geom_point(data=obsNode3, aes(x=Tt_broken_sum, y=Observed),colour="green",size=3)+
 facet_grid(GrowthSeason.x~Rotation.x)+
  geom_smooth(method = "glm",family = gaussian(link="log"), aes(colour = "Exponential"))+
  #geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="black")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
 
```
##Iversen_9SowingDateSD3Waterirr
```{r,fig.height=3, fig.width=10}

obsLAI4<-ObsLF%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD3Waterirr")%>%
  dplyr::filter(Variable=="LAI")

obsNode4<-ObsLF%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD3Waterirr")%>%
  dplyr::filter(Variable=="NodeNumber")
 
obsLAI4
obsLAI4%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd)")+ylab("LAI (m^2/m^2) ")+ggtitle("Iversen_9SowingDateSD3Waterirr")+
  geom_smooth(method = "glm",family = gaussian(link="log"), aes(colour = "Exponential"))+ 
  geom_point(data=obsNode4, aes(x=Tt_broken_sum, y=Observed),colour="green",size=3)+
 facet_grid(GrowthSeason.x~Rotation.x)+
 #geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
 
```
##Iversen_9SowingDateSD4Waterirr
```{r,fig.height=3, fig.width=10}

obsLAI5<-ObsLF%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD4Waterirr")%>%
  dplyr::filter(Variable=="LAI")

obsNode5<-ObsLF%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD4Waterirr")%>%
  dplyr::filter(Variable=="NodeNumber")

obsLAI5%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd)")+ylab("LAI (m^2/m^2) ")+ggtitle("Iversen_9SowingDateSD4Waterirr")+
  geom_point(data=obsNode5, aes(x=Tt_broken_sum, y=Observed),colour="green",size=3)+
  facet_grid(GrowthSeason.x~Rotation.x)+
  #geom_smooth(method = "glm",family = gaussian(link="log"), aes(colour = "Exponential"))+  
  #geom_smooth(method = "lm", se = TRUE, linetype = 1, aes(colour = "lm"))+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
 
```
##Iverson12DefoliationFD5
```{r,fig.height=6, fig.width=10}

obsLAI6<-ObsLF%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Variable=="LAI")
obsNode6<-ObsLF%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Variable=="NodeNumber")

obsLAI6%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+
  theme_bw()+xlab("Thermal time(°Cd)")+ylab("LAI (m^2/m^2)")+ggtitle("Iversen_121DefoliationLLFDFD5")+
 facet_grid(GrowthSeason.x~Rotation.x)+
  geom_point(data=obsNode6, aes(x=Tt_broken_sum, y=Observed),colour="green",size=3)+
  #geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="black")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```

###LEAR
```{r}
LEAR<-ObsL%>%
  group_by(Name,GrowthSeason.x,Rotation.x,Tmean,Ppm,Collection,GrowthRotation)%>%
 do(mod = lm(Observed~Tt_broken_sum,data=.)) %>%
  mutate(LEAR = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)
  
LEAR%>%
  dplyr::filter(Collection!="2010_2012")%>%
  dplyr::filter(Name!="Iversen_121DefoliationLLFDFD2")%>%
  ggplot(aes(x=Ppm, y=LEAR, colour=factor(Name)))+geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey")+xlab("Photoperiod (h)")+ylab("LEAR (m^2/m^2/°Cd)")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
```
#load Rotation and Growth season
```{r,fig.height=6, fig.width=10}
phyll <- "D:\\R\\"
StartGrazing <- read.table(paste0(phyll, "ExperimentList.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(GrowthRotation= as.factor(paste0(GrowthSeason,Rotation)))
LEARPp<- merge(StartGrazing1,LEAR,by=c("Name","Collection","GrowthRotation"))


LEARPp%>%
  dplyr::filter(Collection!="2010_2012")%>%
  #dplyr::filter(Stage!="Seedling")%>%
  ggplot(aes(x=Ppm, y=LEAR,label=GrowthRotation,color=Name))+geom_text()+theme_bw()+xlab("Mean photoperiod(h) ")+ylab("LEAR (m^2/m^2/°Cd)")+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="red")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
  facet_grid(Trend~Stage)+
  #facet_wrap(~Stage,ncol = 2)+
  #geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())

  
```
```{r}
LEARPp1<-LEARPp%>%
dplyr::filter(Stage!="Seedling")

X<-LEARPp1$Ppm
Y<-LEARPp1$LEAR
Xsq<-X^2
Xcub<-X^3
plot(X,Y, pch=19)
model1<-lm(Y~X)
model2<-lm(Y~X+Xsq)
model3<-lm(Y~X+Xsq+Xcub)

anova(model1)
summary(model1)
anova(model2)
summary(model2)
anova(model3)
summary(model3)
abline(model1, col="red")
XV<-seq(min(X),max(X),0.01)
yv<-predict(model2,list(X=XV,Xsq=XV^2))
lines(XV,yv,col="blue")
  
```

####Sen
```{r,fig.height=6, fig.width=10}
ObsLSen<-ObsL.Raw%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))%>%
  dplyr::filter(Water.x=="irr")%>%
  dplyr::filter(Defoliation.x=="LL")%>%
  dplyr::filter(Variable=="Senescence"|Variable=="NodeNumber")%>%
  dplyr::filter(Tb==1)
ObsSen<-ObsLSen%>%
  dplyr::filter(Variable=="Senescence")%>%
  dplyr::select(Clock.Today,Name,Collection,GrowthSeason.x,Rotation.x,Variable,Observed,StdDEV,Tt_broken_sum,Ppm,Tmean,GrowthRotation)
ObsNode<-ObsLSen%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::select(Clock.Today,Name,Collection,GrowthSeason.x,Rotation.x,Variable,Observed,StdDEV,Tt_broken_sum,Ppm,Tmean,GrowthRotation)
ObsSen_Node<-merge(ObsSen,ObsNode,by=c("Clock.Today","Name","Collection","GrowthSeason.x","Rotation.x","Tt_broken_sum","Ppm","Tmean","GrowthRotation"))
ObsSen_Node%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  ggplot(aes(x=Observed.y, y=Observed.x,label=GrowthRotation))+theme_bw()+xlab("NodeNumber")+ylab("Senescence")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
   facet_grid(GrowthSeason.x~Rotation.x)+
  #facet_wrap(~Stage,ncol = 2)+
  geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())
  
  
```

```{r}
ObsSen_Node%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Tt_broken_sum>200)%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed.x,label=GrowthRotation))+theme_bw()+ylab("Senescence")+xlab("Thermal time")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
   facet_grid(GrowthSeason.x~Rotation.x)+
  #facet_wrap(~Stage,ncol = 2)+
  geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())

```
```{r}
ObsSN.rate<-ObsSen_Node%>%
  group_by(Name,GrowthSeason.x,Rotation.x,Collection,Tmean,Ppm,GrowthRotation) %>%
  do(mod = lm(Observed.x~Observed.y,data=.)) %>%
  mutate(slope = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)

phyll <- "D:\\R\\"
StartGrazing <- read.table(paste0(phyll, "ExperimentList.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(GrowthRotation= as.factor(paste0(GrowthSeason,Rotation)))
ObsSNPp<- merge(StartGrazing1,ObsSN.rate,by=c("Name","Collection","GrowthRotation"))
ObsSNPp%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL")%>%
  dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="13")%>%
  dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="31")%>%
  ggplot(aes(x=Ppm, y=slope,label=GrowthRotation,color=Name))+theme_bw()+xlab("Photoperiod")+ylab("Senescence rate")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
   #facet_grid(GrowthSeason.x~Rotation.x)+
  #facet_wrap(~Trend,ncol = 2)+
  #geom_point(size=2)+
  geom_text()+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())

```
```{r}
ObsST.rate<-ObsSen_Node%>%
  dplyr::filter(Tt_broken_sum>200)%>%
  group_by(Name,GrowthSeason.x,Rotation.x,Collection,Tmean,Ppm,GrowthRotation) %>%
  do(mod = lm(Tt_broken_sum~Observed.x,data=.)) %>%
  mutate(slope = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)

phyll <- "D:\\R\\"
StartGrazing <- read.table(paste0(phyll, "ExperimentList.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(GrowthRotation= as.factor(paste0(GrowthSeason,Rotation)))
ObsSTPp<- merge(StartGrazing1,ObsST.rate,by=c("Name","Collection","GrowthRotation"))
ObsSTPp%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL"|GrowthRotation!="16")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL"|GrowthRotation!="27")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL"|GrowthSeason.x!="1")%>%
  ggplot(aes(x=Ppm, y=slope,label=GrowthRotation,color=Name))+theme_bw()+xlab("Photoperiod")+ylab("Sen per node")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
   #facet_grid(GrowthSeason.x~Rotation.x)+
  facet_wrap(~Trend,ncol = 2)+
  #geom_point(size=2)+
  geom_text()+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())

```


```{r,fig.height=6, fig.width=10}
ObsSen_Node%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  ggplot(aes(x=Observed.y, y=Observed.x,label=GrowthRotation))+theme_bw()+xlab("NodeNumber")+ylab("Senescence")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
   facet_grid(GrowthSeason.x~Rotation.x)+
  #facet_wrap(~Stage,ncol = 2)+
  geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())
```


####Braching
```{r,fig.height=6, fig.width=10}
ObsLbranch<-ObsL.Raw%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))%>%
  dplyr::filter(Water.x=="irr")%>%
  dplyr::filter(Defoliation.x=="LL")%>%
  dplyr::filter(Variable=="Branch"|Variable=="NodeNumber")%>%
  dplyr::filter(Tb==1)
Obsbranch<-ObsLbranch%>%
  dplyr::filter(Variable=="Branch")%>%
  dplyr::select(Clock.Today,Name,Collection,GrowthSeason.x,Rotation.x,Variable,Observed,StdDEV,Tt_broken_sum,Ppm,Tmean,GrowthRotation)
ObsNode<-ObsLbranch%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::select(Clock.Today,Name,Collection,GrowthSeason.x,Rotation.x,Variable,Observed,StdDEV,Tt_broken_sum,Ppm,Tmean,GrowthRotation)
ObsBr_Node<-merge(Obsbranch,ObsNode,by=c("Clock.Today","Name","Collection","GrowthSeason.x","Rotation.x","Tt_broken_sum","Ppm","Tmean","GrowthRotation"))
ObsBr_Node%>%
  #dplyr::filter(Observed.y>4)%>%
  ggplot(aes(x=Observed.y, y=Observed.x,label=GrowthRotation))+geom_point()+theme_bw()+xlab("NodeNumber")+ylab("Branch")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
  facet_grid(GrowthSeason.x~Rotation.x)+
  #facet_wrap(~Stage,ncol = 2)+
  geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())
  
  
```
###Branching data prepare for interpolate with LAI
```{r,fig.height=6, fig.width=10}
ObsLBL<-ObsL.Raw%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))%>%
  dplyr::filter(Water.x=="irr")%>%
  dplyr::filter(Defoliation.x=="LL")%>%
  dplyr::filter(Variable=="Branch"|Variable=="LAI")%>%
  dplyr::filter(Tb==1)%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Clock.Today<"2016-07-01")%>%
  dplyr::filter(GrowthRotation!="14")
  
```
###Branching interpolate for each rotation
```{r}

# add function to "turn-off" rowise() in dplyr. FIXME: maybe there's a better/simpler solution?

UniExp <- unique(ObsLBL$ExpUnitCode)

InteBL.df<- data.frame()
  
for(i in 1:length(UniExp))
{
  
  ObsLBL.sub<-ObsLBL%>%
   filter(ExpUnitCode==UniExp[i])
  
 LB<- ObsLBL.sub%>%
  unique()%>%
  tidyr::spread(Variable,Observed)
 
 LB.data<-LB%>%
  mutate( Branch.y=approx(LB$Clock.Today, LB$Branch, xout =LB$Clock.Today, 
         method="linear", 
         rule = 2)$y)##interpolate function 
  

 InteBL.df <- rbind(InteBL.df, LB.data)

}

summary(InteBL.df)
InteBL.df
#write.csv(df.all,"D:/R/TtAll/df.all.csv", row.names = FALSE)

```
##Branch against LAI
```{r}
InteBL.df%>%
  dplyr::filter(GrowthRotation!="11")%>%
  ggplot(aes(x=Branch.y, y=LAI,label=GrowthRotation))+theme_bw()+ylab("LAI")+xlab("Branch")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
  #facet_grid(GrowthSeason.x~Rotation.x)+
  #facet_wrap(~Stage,ncol = 2)+
  geom_text()+
  #geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())
```

###Branching per node in Increase and decrease photoperiods

```{r}
ObsBr.rate<-ObsBr_Node%>%
   dplyr::filter(Observed.y>4)%>%
  group_by(Name,GrowthSeason.x,Rotation.x,Collection,Tmean,Ppm,GrowthRotation) %>%
  do(mod = lm(Observed.x~Observed.y,data=.)) %>%
  mutate(slope = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)

phyll <- "D:\\R\\"
StartGrazing <- read.table(paste0(phyll, "ExperimentList.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(GrowthRotation= as.factor(paste0(GrowthSeason,Rotation)))
ObsBrPp<- merge(StartGrazing1,ObsBr.rate,by=c("Name","Collection","GrowthRotation"))

ObsBrPp%>%
  dplyr::filter(GrowthRotation!="26")%>%
  dplyr::filter(GrowthRotation!="36")%>%
  # dplyr::filter(GrowthRotation!="24")%>%
  # dplyr::filter(GrowthRotation!="34")%>%
  ggplot(aes(x=Tmean, y=slope,label=GrowthRotation))+geom_text()+theme_bw()+ylab("Branch per node")+xlab("Mean temperature")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
  #facet_grid(GrowthSeason.x~Rotation.x)+
  facet_wrap(~Trend,ncol = 2)+
  #geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())


```
###shoot population number
```{r}
ObsSP<-ObsL.Raw %>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))%>%
  dplyr::filter(Water.x=="irr")%>%
  dplyr::filter(Defoliation.x=="LL")%>%
  dplyr::filter(FD.x=="FD5")%>%
  dplyr::filter(Tb==1)%>%
  dplyr::filter(Variable=="ShootPopulation"|Variable=="PlantPopulation")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  tidyr::spread(Variable,Observed)
ObsSP%>%
   ggplot(aes(x=PlantPopulation, y=ShootPopulation,label=GrowthRotation))+theme_bw()+ylab("Plant population")+xlab("Shoots population")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
  #facet_grid(GrowthSeason.x~Rotation.x)+
  #facet_wrap(~Trend,ncol = 2)+
  geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())



```
###Plant population 
```{r}
ObsSP<-ObsL.Raw %>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))%>%
  dplyr::filter(Water.x=="irr")%>%
  dplyr::filter(Defoliation.x=="LL")%>%
  dplyr::filter(FD.x=="FD5")%>%
  dplyr::filter(Tb==1)%>%
  dplyr::filter(Variable=="PlantPopulation")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")
ObsSP%>%
   ggplot(aes(x=Tt_broken_sum, y=Observed,label=GrowthRotation))+theme_bw()+ylab("Plant population")+xlab("Thermal time")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
  facet_grid(GrowthSeason.x~Rotation.x)+
  #facet_wrap(~Trend,ncol = 2)+
  geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())



```

###Branching against thermal time

```{r}
ObsBr_Node%>%
  dplyr::filter(Observed.y>4)%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed.x,label=GrowthRotation))+geom_point()+theme_bw()+ylab("Branch")+xlab("Thermal time")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
  facet_grid(GrowthSeason.x~Rotation.x)+
  #facet_wrap(~Stage,ncol = 2)+
  geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())
```

###branchchron aganist Photoperiod
```{r}
ObsBT.rate<-ObsBr_Node%>%
   dplyr::filter(Observed.y>4)%>%
  group_by(Name,GrowthSeason.x,Rotation.x,Collection,Tmean,Ppm,GrowthRotation) %>%
  do(mod = lm(Tt_broken_sum~Observed.x,data=.)) %>%
  mutate(slope = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)

phyll <- "D:\\R\\"
StartGrazing <- read.table(paste0(phyll, "ExperimentList.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(GrowthRotation= as.factor(paste0(GrowthSeason,Rotation)))
ObsBTPp<- merge(StartGrazing1,ObsBT.rate,by=c("Name","Collection","GrowthRotation"))


ObsBTPp%>%
  dplyr::filter(GrowthRotation!="26")%>%
  dplyr::filter(GrowthRotation!="36")%>%
  dplyr::filter(GrowthRotation!="24")%>%
  dplyr::filter(GrowthRotation!="34")%>%
  ggplot(aes(x=Ppm, y=slope,label=GrowthRotation))+geom_text()+theme_bw()+ylab("Branchchron")+xlab("photoperiod")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
  #facet_grid(GrowthSeason.x~Rotation.x)+
  facet_wrap(~Trend,ncol = 2)+
  #geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())
  
```
###Node number against branching

```{r}
ObsBN.rate<-ObsBr_Node%>%
  dplyr::filter(Observed.y>5)%>%
  group_by(Name,GrowthSeason.x,Rotation.x,Collection,Tmean,Ppm,GrowthRotation) %>%
  do(mod = lm(Observed.x~Observed.y,data=.)) %>%
  mutate(slope = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)
ObsBN.rate%>%
  ggplot(aes(x=Tmean, y=slope,label=GrowthRotation))+geom_text()+theme_bw()+xlab("NodeNumber")+ylab("Branch")+
  #geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
  #facet_grid(GrowthSeason.x~Rotation.x)+
  #facet_wrap(~Trend,ncol = 2)+
  #geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())
  
```

## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r, round(r2*100,1))

  return(out)

}
```

## Test stats functions used

```{r}
s <- c(4231.972,3935.604,3779.652,3627.687,3363.499,3230.566,2868.114,2868.827)
m <- c(4987.66,5636.09,4754.06,4114.53,4141.72,3704.06,5142.19,4762.03)

x <- gauchStats(s,m)

tempDf <- data.frame(statName=c("SB","NU","LC","r_MSD","R2"), statValue=x)
# kable(tempDf, digits= 2)
tempDf2 <- data.frame(Predicted=s, Observed=m)

x <- tempDf2 %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>% 
  t() 

df <- data.frame(stat = row.names(x),statvalue = x[,1])

df %>%
  kable(format = "markdown")
```
## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneValidation.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
summary(df)
head(df) # simulation results
```
# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"_Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)

# myDb %>%
#   dplyr::select(Name) %>%
#   unique()

```
## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,SWC,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  tidyr::gather("Variable","Predicted",LAI:NodeNumber) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)
summary(simD)


head(obsNode)
mergedf<-merge(ObsL,simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)
mergedf

```
## Node number
#Time series
## obs Vs Pre for each experiment
## 1997-2001
```{r,fig.height=4, fig.width=9}

obsLAI1<-ObsL%>%
  dplyr::filter(Collection=="1997_2001")%>%
  dplyr::filter(Variable=="LAI")%>%
  dplyr::filter(Name=="Iversen_8Waterirr")%>%
  dplyr::filter(Clock.Today>"1997-08-01")%>%
  dplyr::filter(Clock.Today<"2001-08-01")
  
  
   
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Clock.Today>"1997-08-01")%>%
   dplyr::filter(Clock.Today<"2001-08-01")%>%
   dplyr::filter(Variable=="LAI")%>%
   dplyr::filter(Name=="Iversen_8Waterirr")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~Name,ncol = 2)+
 geom_point(data=obsLAI1, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("LAI(m^2/m^2)")+
 theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
##2002-2004
```{r,  fig.height=4, fig.width=8}
obsLAI2<-ObsL%>% 
  dplyr::filter(Collection=="2002_2004")%>%
  dplyr::filter(Variable=="LAI")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")

simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2002-06-01")%>%
  dplyr::filter(Variable=="LAI")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
str(simD2)
simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 1)+
  geom_point(data=obsLAI2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("LAI(m^2/m^2)")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
  


```

```{r,  fig.height=8, fig.width=8}
obsLAI3<-ObsL%>%
  dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Variable=="LAI")
 obsNode3 

simD3<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2000-10-24 12:00:00")%>%
  dplyr::filter(Clock.Today<"2002-07-01 12:00:00")%>%
  dplyr::filter(Name!="Iversen_8Waterdry")%>%
  dplyr::filter(Name!="Iversen_8Waterirr")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="MooraDefoliation")%>%
  dplyr::filter(Name!="NekiaDefoliation")%>%
  dplyr::filter(Name!="QuairadingDefoliation")%>%
  dplyr::filter(Name!="RoseworthyWaterdry")%>%
  dplyr::filter(Name!="RoseworthyWaterirr")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD1Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD2Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD3Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD4Waterdry")%>%
  dplyr::filter(Variable=="LAI")
  str(simD3)
simD3%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 2)+
  geom_point(data=obsLAI3, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  facet_wrap(~Name,ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("LAI(m^2/m^2)")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
```
##2014-2018
```{r,  fig.height=4, fig.width=8}
obsLAI4<-ObsL%>% 
  dplyr::filter(Collection=="2014_2018")%>%
  dplyr::filter(Variable=="LAI")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD4<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="LAI")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 1)+
  geom_point(data=obsLAI4, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("LAI(m^2/m^2)")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
  


```


# Statistic and Graph
```{r,,fig.height=6, fig.width=10}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "LAI") %>% 
  dplyr::filter(Defoliation.x== "LL")%>%
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(Name))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("LAI")+
  facet_wrap(~Collection, ncol = 4)+
  theme(legend.title=element_blank())+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

## RMSE

```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "LAI") %>% 
   dplyr::filter(Water.x== "irr")%>%
  dplyr::filter(Defoliation.x== "LL")%>%
 #filter(Variable == "NodeNumber") %>%
  filter(Collection!="2010_2012")%>%
  mutate(Rotation= as.factor(Rotation.x))%>%
  mutate(GrowthSeason=as.factor(GrowthSeason.x))%>%
  group_by(Name) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```

