---
title: "R Notebook"
output: html_notebook
---
###Height analysis

```{r Load, warning=FALSE, fig.height=8, fig.width=8}
# install.packages("zoo")
#install.packages("polynom")
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)
library(lme4)
library(polynom)
```
## lode observed data
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsAll <- read.table(paste0(obsData, "ObsAll.txt"),
                   header = TRUE)
obsA1<- obsAll %>%
  dplyr::filter(Collection=="2000_2002")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
 mutate(Rotation2=as.factor(ifelse(Rotation=="1",paste0("S",Rotation),paste0("R",Rotation))))

obsA4<- obsAll %>%
  dplyr::filter(Collection=="2014_2018")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
  mutate(Rotation2=as.factor(ifelse(Rotation=="1",paste0("S",Rotation),paste0("R",Rotation))))
 

  obsA2<- obsAll %>%
  dplyr::filter(Collection=="1997_2001")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
  mutate(Rotation2=as.factor(paste0("R",Rotation)))
  

  obsA3<- obsAll %>%
  dplyr::filter(Collection=="2002_2004")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
  mutate(Rotation2=as.factor(paste0("R",Rotation)))
  
obsA<-rbind(obsA2,obsA3,obsA1,obsA4)
summary(obsA)
 obsA
```

#Load Tt and Join Observed data together
```{r}
upDir <- "D:/R/"
obsData <- "D:/R/TtAll/"

Tt<- read.table(paste0(obsData, "df.all.txt"),
               header = TRUE)
TtA <- Tt %>% mutate(Clock.Today=dmy(Clock.Today), ExpUnitCode=as.factor(ExpName))
TtA
ObsH <-merge(obsA,TtA,by=c("Clock.Today","ExpUnitCode")) %>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))%>%
  dplyr::filter(Water.x=="irr")%>%
  dplyr::filter(Defoliation.x=="LL")%>%
  dplyr::filter(Variable=="Height")%>%
  dplyr::filter(Tb==1)
  

summary(ObsH)
```
```{r}
mytheme1<-theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14,angle=90, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

mytheme3<-theme(
     legend.title = element_text(colour="black", size=14, face="bold"),
     legend.text = element_text(colour="black", size = 14,face="plain"),
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14),
    legend.position = "right", legend.box = "vertical")
```


####Height against Mean temperature 
```{r,fig.height=5, fig.width=8}
obsheight<-ObsH%>%
  dplyr::filter(Name=="Iversen_8Waterirr")

obsheight$Rotation2<- factor(obsheight$Rotation2, levels=c("R1", "R2", "R3", "R4", "R5","R6", "R7"))

obsheight%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Mean temperature (°C)")+ylab("Plant height (mm)")+ facet_grid(GrowthSeason2~Rotation2)+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+ 
  ggtitle("E1ILL(Iversen_8Waterirr)")+mytheme1+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")
#ggsave("D:/R/Pictures/Height/Iversen_8WaterirrHeight.png", width=8, height=6, dpi=500)

```
```{r,fig.height=5, fig.width=8}
obsheight<-ObsH%>%
  dplyr::filter(Name=="Iversen_8Waterirr")
obsheight$Rotation2<- factor(obsheight$Rotation2, levels=c("R1", "R2", "R3", "R4", "R5","R6", "R7"))
obsheight%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd)")+ylab("Plant height (mm)")+ facet_grid(GrowthSeason2~Rotation2)+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  ggtitle("E1ILL(Iversen_8Waterirr)")+mytheme1+
  scale_x_continuous(breaks = seq(0, 600, by =200), limits=c(0,500))+
  scale_y_continuous(breaks = seq(0, 550, by =200), limits=c(0,600))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")
#ggsave("D:/R/Pictures/Height/Iversen_8WaterirrHeight.png", width=8, height=6, dpi=500)

```


#Iversen_91DefoliationLL
```{r,fig.height=5, fig.width=8}
obsheight1<-ObsH%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
obsheight1$Rotation2<- factor(obsheight1$Rotation2, levels=c("R1", "R2", "R3", "R4", "R5","R6", "R7"))

obsheight1%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd)")+ylab("Plant height (mm)")+ggtitle("E3ILL(Iversen_91DefoliationLL)")+
 facet_grid(GrowthSeason2~Rotation2)+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  mytheme1+
  scale_x_continuous(breaks = seq(0, 600, by =200), limits=c(0,500))+
  scale_y_continuous(breaks = seq(0, 550, by =200), limits=c(0,600))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")

#ggsave("D:/R/Pictures/Height/Iversen_91DefoliationLL.png", width=8, height=6, dpi=500)
```
###mean temperature
```{r,fig.height=5, fig.width=8}
obsheight1<-ObsH%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
obsheight1%>%
  ggplot(aes(x=mean, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd)")+ylab("Plant height (mm)")+ggtitle("Iversen_91DefoliationLL")+
 facet_grid(GrowthSeason2~Rotation2)+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  mytheme1+
  # scale_x_continuous(breaks = seq(0, 600, by =200), limits=c(0,500))+
  # scale_y_continuous(breaks = seq(0, 550, by =200), limits=c(0,600))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")
#ggsave("D:/R/Pictures/Height/Iversen_91DefoliationLL.png", width=8, height=6, dpi=500)
```

##Iversen_9SowingDateSD1Waterirr
```{r,fig.height=4, fig.width=8}

obsheight3<-ObsH%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD1Waterirr")%>%
  mutate(Observed=Observed*10)
 obsheight3$Rotation2<- factor(obsheight3$Rotation2, levels=c("S1", "R2", "R3", "R4", "R5","R6", "R7"))
obsheight3%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd)")+ylab("Plant height (mm)")+ggtitle("E2ILLS1(Iversen_9SowingDateSD1Waterirr)")+
 facet_grid(GrowthSeason2~Rotation2)+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="black")+
 mytheme1+
  scale_x_continuous(breaks = seq(0, 800, by =300), limits=c(0,750))+
  scale_y_continuous(breaks = seq(0, 600, by =200), limits=c(0,700))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")
#ggsave("D:/R/Pictures/Height/Iversen_9SowingDateSD1Waterirr.png", width=8, height=5, dpi=500)
```
##Iversen_9SowingDateSD2Waterirr
```{r,fig.height=3, fig.width=10}

obsheight1<-ObsH%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD2Waterirr")%>%
  mutate(Observed=Observed*10)
obsheight1$Rotation2<- factor(obsheight1$Rotation2, levels=c("S1", "R2", "R3", "R4", "R5","R6", "R7"))
 
obsheight1%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd)")+ylab("Plant height (mm)")+ggtitle("E2ILLS2(Iversen_9SowingDateSD2Waterirr)")+
 facet_grid(GrowthSeason2~Rotation2)+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
  scale_x_continuous(breaks = seq(0, 800, by =200), limits=c(0,900))+
  scale_y_continuous(breaks = seq(0, 600, by =200), limits=c(0,700))+
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

#ggsave("D:/R/Pictures/Height/Iversen_9SowingDateSD2Waterirr.png", width=8, height=3, dpi=500)
```

##Iversen_9SowingDateSD3Waterirr
```{r,fig.height=3, fig.width=10}

obsheight1<-ObsH%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD3Waterirr")%>%
  mutate(Observed=Observed*10)
obsheight1$Rotation2<- factor(obsheight1$Rotation2, levels=c("S1", "R2", "R3", "R4", "R5","R6", "R7"))
 
obsheight1
obsheight1%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd)")+ylab("Plant height (mm)")+ggtitle("E2ILLS3(Iversen_9SowingDateSD3Waterirr)")+
 facet_grid(GrowthSeason2~Rotation2)+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
  scale_x_continuous(breaks = seq(0, 1000, by =200), limits=c(0,1100))+
  scale_y_continuous(breaks = seq(0, 600, by =200), limits=c(0,700))+
  #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

#ggsave("D:/R/Pictures/Height/Iversen_9SowingDateSD3Waterirr.png", width=8, height=3, dpi=500)
 
```
##Iversen_9SowingDateSD4Waterirr
```{r,fig.height=3, fig.width=10}

obsheight1<-ObsH%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD4Waterirr")%>%
  mutate(Observed=Observed*10)
obsheight1$Rotation2<- factor(obsheight1$Rotation2, levels=c("S1", "R2", "R3", "R4", "R5","R6", "R7"))
 
obsheight1
obsheight1%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd)")+ylab("Plant height (mm)")+ggtitle("E2ILLS4(Iversen_9SowingDateSD4Waterirr)")+
 facet_grid(GrowthSeason2~Rotation2)+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
  scale_x_continuous(breaks = seq(0, 1000, by =200), limits=c(0,1100))+
  scale_y_continuous(breaks = seq(0, 600, by =200), limits=c(0,600))+
  #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

#ggsave("D:/R/Pictures/Height/Iversen_9SowingDateSD4Waterirr.png", width=8, height=3, dpi=500)
 
```

##Iverson12DefoliationFD5
```{r,fig.height=5, fig.width=8}

obsheight1<-ObsH%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  mutate(Observed=Observed*10)
 obsheight1$Rotation2<- factor(obsheight1$Rotation2, levels=c("S1", "R2", "R3", "R4", "R5","R6", "R7"))

obsheight1%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd)")+ylab("Plant height (mm)")+ggtitle("E5ILLF5(Iversen_121DefoliationLLFDFD5)")+
 facet_grid(GrowthSeason2~Rotation2)+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
  scale_y_continuous(breaks = seq(0, 1000, by =600), limits=c(0,900))+
  scale_x_continuous(breaks = seq(0, 600, by =200), limits=c(0,500))+
   mytheme1
 # ggsave("D:/R/Pictures/Height/Iversen_121DefoliationLLFDFD5.png", width=8, height=6, dpi=500)
 
```

#### convert unit
###calculate for heightchron

```{r}
#detach(package:plyr)
obsH2<-ObsH%>%
  dplyr::filter(Collection!="1997_2001")%>%
  dplyr::filter(Collection!="2002_2004")%>%
  mutate(Observed=Observed*10)

obsH3<-ObsH%>%
  dplyr::filter(Collection!="2000_2002")%>%
  dplyr::filter(Collection!="2014_2018")
obsH3
obsHN<-rbind(obsH2,obsH3)
obsHN


obsSlope <- obsHN%>%
  group_by(Name,GrowthSeason.x,Rotation.x,Collection,Tmean,Ppm,GrowthRotation,ID,ExperimentID) %>%
  do(mod = lm(Tt_broken_sum~Observed,data=.)) %>%
  mutate(slope = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)
obsSlope

obsHanalysis<- obsHN%>%
  group_by(Name,GrowthSeason.x,Rotation.x,Collection,ID,ExperimentID) %>%
  do(mod = lm(Tt_broken_sum~Observed,data=.)) %>%
  mutate(slope = summary(mod)$coeff[2]) %>%
  mutate(R2 = summary(mod)$r.squared)%>%
  mutate(P=anova(mod)$'Pr(>F)'[1])%>%  
  mutate(intcp= summary(mod)$coeff[1])%>%
  dplyr::select(-mod)
obsHanalysis
write.csv(obsHanalysis,"D:/R/obsHanalysis.csv", row.names = FALSE)





```
##load Rotation and Growth season

```{r,fig.height=4, fig.width=10}
library(plyr)
phyll <- "D:\\R\\"
StartGrazing <- read.table(paste0(phyll, "ExperimentList.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(GrowthRotation= as.factor(paste0(GrowthSeason,Rotation)))
HchronPp<- merge(StartGrazing1,obsSlope,by=c("Name","Collection","GrowthRotation"))

HchronPp1<-HchronPp%>%
dplyr::filter(Name!="Iversen_8Waterirr"|GrowthRotation!="57")%>%
dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="36")%>%
 dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="14")%>%
 dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="37")%>%
 dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="12")%>%
 dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="41")%>%
 dplyr::filter(Name!="Iversen_8Waterirr"|GrowthRotation!="26")%>%
 dplyr::filter(Name!="Iversen_8Waterirr"|GrowthRotation!="32")%>%
 dplyr::filter(Name!="Iversen_91DefoliationLL"|GrowthRotation!="27")%>%
 dplyr::filter(Name!="Iversen_91DefoliationLL"|GrowthRotation!="17")%>%
 dplyr::filter(Name!="Iversen_91DefoliationLL"|GrowthRotation!="11")%>%
 #   # dplyr::filter(Name!="Iversen_91DefoliationLL"|GrowthRotation!="17")%>%
 dplyr::filter(Name!="Iversen_9SowingDateSD1Waterirr"|GrowthRotation!="14")%>%
 dplyr::filter(Name!="Iversen_9SowingDateSD1Waterirr"|GrowthRotation!="21")%>%
 #   # dplyr::filter(Name!="Iversen_9SowingDateSD1Waterirr"|GrowthRotation!="26")%>%
 dplyr::filter(Name!="Iversen_9SowingDateSD2Waterirr"|GrowthRotation!="13")
 ##dplyr::filter(Name!="Iversen_9SowingDateSD4Waterirr"|GrowthRotation!="13")%>%
 #dplyr::filter(Stage!="Seedling")

# my.formula <- slope ~ poly(Ppm, 2, raw = TRUE)
# m <- lm(my.formula, HchronPp1)
# my.eq <- as.character(signif(as.polynomial(coef(m)), 2))
# 
# 
# label.text <- paste(gsub("italic(y)=x", "~italic(x)", my.eq, fixed = TRUE),
#               paste("italic(R)^2",  
#                     format(summary(m)$r.squared, digits = 2), 
#                     sep = "~`=`~"),
#                     sep = "~~~~")



my.formula  <- function(HchronPp1){
  my.formula <- slope ~ poly(Ppm, 2, raw = TRUE)
  m <- lm(my.formula, HchronPp1)
  my.eq <- as.character(signif(as.polynomial(coef(m)), 2))
  label.text <- paste("y","'='",paste(gsub(y, "~italic(x)",my.eq, fixed = TRUE)),
              paste("italic(R)^2",format(summary(m)$r.squared, digits = 2), 
                    sep = "~`=`~"),
                    sep = "~~~~")
  as.character(as.expression(label.text));                 
}

my.eqs <- ddply(HchronPp1,.(Stage),my.formula)




b<-HchronPp1%>%
  ggplot(aes(x=Ppm, y=slope, colour=factor(ID),label=GrowthRotation))+geom_text()+theme_bw()+xlab("Mean photoperiod (h)")+ylab(bquote(bold('Heightchron ('*'°Cd'~'mm'^-1*')')))+
  geom_smooth(method = "lm", se = TRUE, formula=y ~ poly(x, 2, raw=TRUE), colour="darkgrey")+
  facet_wrap(~Stage,ncol = 2)+mytheme3+theme(legend.title = element_blank())

#b + annotate(geom = "text", x = 11.5, y = 2, label = label.text, 
             #family = "serif", hjust = 0, parse = TRUE, size = 4)m
b+geom_text(data = my.eqs, aes(x = 13.7, y = 2.5, label = V1), 
          color = 'black',  parse = TRUE, size=4)
detach(package:plyr)
#ggsave("D:/R/Pictures/Height/Heightchorn.png", width=8, height=4, dpi=500)
```
####base photoperiod

```{r,fig.height=4, fig.width=10}
library(plyr)
Pb<-HchronPp1%>%
   mutate(pb=1/slope)

lm_eqn <- function(Pb){
  m <- lm(pb ~ Ppm, Pb);
  eq <- substitute(italic(y) == Ppm + pb %.% italic(Ppm)*","~~italic(R)^2~"="~r2, 
                   list(Ppm = format(coef(m)[1], digits = 2), 
                         pb = format(coef(m)[2], digits = 2), 
                       r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}

eqns <- ddply(Pb,.(Stage),lm_eqn)

Pb%>%
  ggplot(aes(x=Ppm, y=pb, colour=factor(ID),label=GrowthRotation))+geom_text()+theme_bw()+xlab("Mean photoperiod (h)")+ylab("1/y")+
  geom_smooth(method = "lm", se = TRUE,  colour="darkgrey")+
  facet_wrap(~Stage,ncol = 2)+mytheme3+theme(legend.title = element_blank())+
  scale_x_continuous(breaks = seq(9, 18, by =3), limits=c(9,18))+
  geom_text(data = eqns, aes(x = 13.5, y = 2.5, label = V1), 
          color = 'black',  parse = TRUE, size=4.8)
detach(package:plyr)
#ggsave("D:/R/Pictures/Height/Heightchorny1.png", width=8, height=4, dpi=500)

```

```{r}
HchronPp
X<-HchronPp1$Ppm
Y<-HchronPp1$slope
Xsq<-X^2
Xcub<-X^3
plot(X,Y, pch=19)
model1<-lm(Y~X)
model2<-lm(Y~X+Xsq)
model3<-lm(Y~X+Xsq+Xcub)
mod_lm <-lm(Y~X*(X<14.2)+X*(X>=14.2),data=HchronPp)
anova(model1)
summary(model1)
anova(model2)
summary(model2)
anova(model3)
summary(model3)
abline(model1, col="red")
XV<-seq(min(X),max(X),0.01)
yv<-predict(model2,list(X=XV,Xsq=XV^2))
lines(XV,yv,col="blue")
  
  
```


### Fit a polynomial regression model
# ```{r}
# HchronPp1
# X<-HchronPp1$Pmean
# Y<-HchronPp1$slope
# Xsq<-X^2
# Xcub<-X^3
# plot(X,Y, pch=19)
# model1<-lm(Y~X)
# model2<-lm(Y~X+Xsq)
# model3<-lm(Y~X+Xsq+Xcub)
# mod_lm <-lm(Y~X*(X<14.2)+X*(X>=14.2),data=HchronPp1)
# anova(model1)
# summary(model1)
# anova(model2)
# summary(model2)
# anova(model3)
# summary(model3)
# abline(model1, col="red")
# XV<-seq(min(HchronPp1$Pmean),max(HchronPp1$Pmean),0.01)
# yv<-predict(model2,list(X=XV,Xsq=XV^2))
# lines(XV,yv,col="blue")
# title(xlab="Mean photoperiod (h) ",ylab="Heightchron (mm/cd )")




## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r, round(r2*100,1))

  return(out)

}
```

## Test stats functions used

```{r}
s <- c(4231.972,3935.604,3779.652,3627.687,3363.499,3230.566,2868.114,2868.827)
m <- c(4987.66,5636.09,4754.06,4114.53,4141.72,3704.06,5142.19,4762.03)

x <- gauchStats(s,m)

tempDf <- data.frame(statName=c("SB","NU","LC","r_MSD","R2"), statValue=x)
 kable(tempDf, digits= 4)
tempDf2 <- data.frame(Predicted=s, Observed=m)

x <- tempDf2 %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse =format(NSE(Predicted,Observed), digits=3),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>% 
  t() 

df <- data.frame(stat = row.names(x),statvalue = x[,1])

df %>%
  kable(format = "markdown",digits = 4)
#format(coef(m)[2], digits = 2)
```
## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneValidation.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
summary(df)
head(df) # simulation results
```
# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"_Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)

# myDb %>%
#   dplyr::select(Name) %>%
#   unique()

```
## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,SWC,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  tidyr::gather("Variable","Predicted",LAI:NodeNumber) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)
summary(simD)

head(ObsH)
mergedf<-merge(obsHN,simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)
mergedf

```
###mytheme for observed and predicted graphs
```{r}
mytheme2<-theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
```


## Node number
#Time series
## obs Vs Pre for each experiment
## 1997-2001
```{r,fig.height=4, fig.width=9}
obsheight1<-ObsH%>%dplyr::filter(Name=="Iversen_8Waterirr")
  
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Variable=="Height")%>%
   dplyr::filter(Name=="Iversen_8Waterirr")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~ID,ncol = 2)+
 geom_point(data=obsheight1, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Plant height (mm)")+
 mytheme2+
 annotate("text", x=ymd_hms("1999-10-24 12:00:00"), y=750, size = 5, label ="paste(R_RMSD == 37.6,'%')", parse=T)
   #geom_text(aes(x=ymd_hms("1999-10-24 12:00:00"), y=750, label="R_RMSD = 37.6%",size=5))
 
 #ggsave("D:/R/Pictures/Height/Iversen_8Waterirrheight1.png", width=8, height=4, dpi=500)
```
##2002-2004
```{r,  fig.height=4, fig.width=8}
obsheight2<-obsHN%>% 
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  dplyr::filter(Variable=="Height")

simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="Height")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
   dplyr::filter(Clock.Today>"2002-06-01")
str(simD2)
simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 1)+
  geom_point(data=obsheight2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Plant height (mm)")+
  mytheme2+
  annotate("text", x=ymd_hms("2003-07-24 12:00:00"), y=750, size = 5, label ="paste(R_RMSD == 27.6,'%')", parse=T)
 #geom_text(aes(x=ymd_hms("2003-07-24 12:00:00"), y=750, label="R_RMSD = 27.6%",size=5))
 #ggsave("D:/R/Pictures/Height/Iversen_91DefoliationLLheight1.png", width=8, height=4, dpi=500)

```
```{r,  fig.height=4, fig.width=8}
obsheight2<-obsHN%>% 
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Variable=="Height")

simD2a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="Height")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Clock.Today<"2015-01-06")


simD2b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="Height")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD2<-rbind(simD2a,simD2b)
  
   
str(simD2)
simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 1)+
  geom_point(data=obsheight2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Plant height (mm)")+
   mytheme2+
  annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=920, size = 5, label ="paste(R_RMSD == 40,'%')" , parse=T)
 #ggsave("D:/R/Pictures/Height/Iversen_121DefoliationLLFDFD5height1.png", width=8, height=4, dpi=500)
  
  


```
##2000-2002
```{r,  fig.height=8, fig.width=8}
obsheight3<-obsHN%>%
  dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Variable=="Height")

simD3A<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2000-10-24 12:00:00")%>%
  dplyr::filter(Clock.Today<"2002-07-01 12:00:00")%>%
  dplyr::filter(Name==c("Iversen_9SowingDateSD1Waterirr","Iversen_9SowingDateSD2Waterirr","Iversen_9SowingDateSD3Waterirr","Iversen_9SowingDateSD4Waterirr"))%>%
  dplyr::filter(Variable=="Height")
  

DF<-data.frame(Name=c("Iversen_9SowingDateSD1Waterirr","Iversen_9SowingDateSD2Waterirr","Iversen_9SowingDateSD3Waterirr","Iversen_9SowingDateSD4Waterirr"),ID= c("E2ILLS1","E2ILLS2","E2ILLS3","E2ILLS4"))
simD3<-merge(DF,simD3A, by=c("Name"))

p1<-simD3%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  geom_point(data=obsheight3, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  facet_wrap(~ID,ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Plant height (mm)")+
  mytheme2

dat_text <- data.frame(
  label = c("R_RMSE=28.2%","R_RMSE=33.2%","R_RMSE=48.6%", "R_RMSE=34.5%"),
  ID= c("E2ILLS1","E2ILLS2","E2ILLS3","E2ILLS4"),
  x= ymd_hms("2001-01-24 12:00:00", "2001-01-24 12:00:00","2001-01-24 12:00:00","2001-01-24 12:00:00"),
  y=c(750,750,750,750)) 

 p1 +geom_text(data=dat_text, mapping = aes(x=x,y=y, label = label),hjust   = -0.1,vjust   = -1,size=5)  
 
#ggsave("D:/R/Pictures/Height/Iversen_9SowingDateSDWaterheight1.png", width=8, height=8, dpi=500)
  
```


# Statistic and Graph
```{r,fig.height=6, fig.width=8}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "Height") %>% 
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Plant height")+
  facet_wrap(~ID, ncol = 4)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  mytheme2
  
  #ggsave("D:/R/Pictures/Height/predicted.png", width=8, height=6, dpi=500)
```
```{r}
mergedf2<-mergedf%>%
   dplyr::filter(Variable== "Height") %>% 
  dplyr::filter(ID==c("E3ILL","E5ILLF5"))
summary(mergedf1)
str(mergedf1)
m <- lm(Predicted ~ Observed, data = mergedf2)
mp <- predict(m, interval = 'conf')
d2 <- cbind(mergedf2, mp)

p1<-d2 %>%
    
  ggplot(aes(x=Observed, y= Predicted,color=ID))+
geom_point(size=2,colour="blue")+theme_bw()+ geom_smooth(method = 'lm', se = FALSE, color="black") +
    geom_line(aes(y = upr), color = 'black', linetype = 3,size=1) +
    geom_line(aes(y = lwr), color = 'black', linetype = 3,size=1)+
  #geom_smooth(method = "lm", se = TRUE, linetype = 3, colour="black") +
  geom_abline(intercept = 0, slope = 1,size=1,color="purple") +
  coord_fixed(ratio = 1)+
  ggtitle("Height (mm)")+
  #facet_wrap(~ID, ncol = 4)+
  theme(legend.title=element_blank(),legend.position = "blank")+
  xlab("Observed")+ylab("Predicted")+
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   ggsave("D:/R/Pictures/Poster/Height.png", width=8, height=4, dpi=500)
```
```












## 2002-2004

```{r,  fig.height=8, fig.width=10}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Collection=="2002_2004")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Plant height")+
  facet_grid(GrowthSeason.x~Rotation.x)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```


## 2000-2002

```{r}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Collection=="2000_2002")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Height")+
  facet_grid(GrowthSeason.x~Rotation.x)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```




```{r, fig.width=8, fig.height=8, warning=FALSE}
mergedf %>%
    dplyr::filter(Collection=="1997_2001")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw() +
   geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1) +
  ggtitle("Plant height")  +
  facet_grid(GrowthSeason.x~Rotation.x)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```


## RMSE

```{r}
str(mergedf)

mergedf %>%
  group_by(ID) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),2),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

# NAR = format(coef(m)[2], digits = 2)

# %>%
#   group_by(Variable,Name) %>%
#   summarise_each(funs(mean))
  
```
#####Height ag





