---
title: "R Notebook"
output: html_notebook
---

### partitioning to leaf and stem

```{r Load, warning=FALSE, fig.height=8, fig.width=8}
# install.packages("zoo")
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)
library(lme4)
library(reshape2)
```
###load experiment data
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsAll <- read.table(paste0(obsData, "ObsAll.txt"),
                   header = TRUE)
obsleaf<- obsAll %>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason,Rotation)))%>%
  dplyr::filter(Water=="irr")%>%
  dplyr::filter(Defoliation=="LL")%>%
  dplyr::filter(FD=="FD5")%>%
  dplyr::filter(Variable=="shootbiomass"|Variable=="LeafWt")
summary(obsleaf)
obsleaf
```

###load experiment data of stem weight
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsAll <- read.table(paste0(obsData, "ObsAll.txt"),
                   header = TRUE)
obsShoot<- obsAll %>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason,Rotation)))%>%
  dplyr::filter(Water=="irr")%>%
  dplyr::filter(Defoliation=="LL")%>%
  dplyr::filter(FD=="FD5")%>%
  dplyr::filter(Variable=="shootbiomass")
summary(obsShoot)
obsShoot
```
###load experiment data of leaf and stem ratio
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsAll <- read.table(paste0(obsData, "ObsAll.txt"),
                   header = TRUE)
obsLSR<- obsAll %>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason,Rotation)))%>%
  dplyr::filter(Water=="irr")%>%
  dplyr::filter(Defoliation=="LL")%>%
  dplyr::filter(FD=="FD5")%>%
  dplyr::filter(Variable=="LeafWt"|Variable=="StemWt")
summary(obsLSR)
obsLSR
```
###mytheme for observed and predicted graphs
```{r}
mytheme2<-theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
```

####Leaf and stem rotaio
```{r}
obsLSRL<-obsLSR%>%
  dplyr::filter(Variable=="LeafWt")%>%
  mutate(LeafWt=Observed)%>%
  mutate(StdDEVL=StdDEV)
obsLSRS<-obsLSR%>%
  dplyr::filter(Variable=="StemWt")%>%
  mutate(StemWt=Observed)%>%
  mutate(StdDEVs=StdDEV)%>%
  dplyr::select(Clock.Today,Name,StemWt,StdDEVs)
LSR<-merge(obsLSRL,obsLSRS,by=c("Clock.Today","Name"))%>%
  mutate(LSR=LeafWt/StemWt)
Shoot<-obsShoot%>%
  mutate(Shootbiomass=Observed*0.001)%>%
  mutate(StdDEVsh=StdDEV)%>%
  dplyr::select(Clock.Today,Name,Shootbiomass,StdDEVsh)

SLS<-merge(LSR,Shoot,by=c("Clock.Today","Name"))%>%
  mutate(Shootbiomass=Shootbiomass)%>%
  dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="14")%>%
  dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="26")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL"|GrowthRotation!="31")

SLS%>%
   ggplot(aes(x=Shootbiomass, y=LSR,label=GrowthRotation,colour=Name))+geom_text()+theme_bw()+xlab("Shootbiomass")+ylab("LSR")+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
 #facet_grid(GrowthSeason~Rotation)+
  ggtitle("Iversen_8Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 #theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(panel.border=element_rect(colour="black",size=0.5, fill = NA),
       axis.line = element_line(colour = "black", size = 0.5),
        panel.background = element_rect(fill = "white", size = 0.5),
        legend.position="none",
        panel.grid.minor.x=element_blank(), panel.grid.major.x=element_blank(),
        panel.grid.minor.y=element_blank(), panel.grid.major.y=element_blank(),
        axis.title.x = element_text(face = "bold", colour = "Black", size = 12),
        axis.title.y = element_text(face = "bold", colour = "black", size = 12),
        axis.text = element_text(face = "bold", vjust = 1, size = 8),
        axis.text.x  = element_text(angle=0, vjust=0.5, size = 11),
        axis.text.y  = element_text(angle=0, vjust=0.5, size = 11),
        strip.text.x = element_text(size=10, face="bold", colour = "black"),
        strip.background = element_rect(colour="red", fill="#CCCCFF"))
```
###leaf parititioning rate
```{r}
LeafP<-SLS%>%
  mutate(Shootbiomass1=Shootbiomass*1000)%>%
  mutate(Pleaf=LeafWt/Shootbiomass1)%>%
  dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="13")

StemP<-SLS%>%
  mutate(Shootbiomass1=Shootbiomass*1000)%>%
  mutate(Pstem=StemWt/Shootbiomass1)%>%
  dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="13")
  

LeafP%>%
   ggplot(aes(x=Shootbiomass1, y=LeafWt,label=GrowthRotation,colour=Name))+geom_text()+theme_bw()+xlab("Shootbiomass")+ylab("LeafWt")+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
 #facet_grid(GrowthSeason~Rotation)+
  ggtitle("Iversen_8Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

LeafP%>%
   ggplot(aes(x=Shootbiomass, y=Pleaf,label=GrowthRotation,colour=Name))+geom_text()+theme_bw()+xlab("Shootbiomass")+ylab("Pleaf")+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
 #facet_grid(GrowthSeason~Rotation)+
  ggtitle("Iversen_8Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

StemP%>%
   ggplot(aes(x=Shootbiomass1, y=StemWt,label=GrowthRotation,colour=ID))+geom_text()+theme_bw()+xlab("Shootbiomass")+ylab("StemWt")+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
 #facet_grid(GrowthSeason~Rotation)+
  #ggtitle("Iversen_8Waterirr")+
  mytheme3
  
  
  
```
###Fit a power function
```{r}
StemP1<-StemP%>%
  mutate(StemWt1=StemWt*0.1)%>%
  mutate(Shootbiomass2=Shootbiomass1*0.1)

m <- nls(StemWt1~ I(b*Shootbiomass2^power),data=StemP1,start = list(power=1.2321379,b=0.1452028),trace = T)

 summary(m)$coefficients
# Make predictions
predictions <- m %>% predict(StemP1)
residules<- resid(m)
plot(residules ~ StemP1$Shootbiomass2)
##Plot model
plot(StemP1$StemWt1 ~ StemP1$Shootbiomass2)
lines(StemP1$Shootbiomass2, fitted(m), lty = 1, col = "black", lwd = 0.1)
```

```{r}
StemP1<-StemP%>%
  mutate(StemWt1=StemWt*0.1)%>%
  mutate(Shootbiomass2=Shootbiomass1*0.1)

m <- nls(StemWt1~ I(b*Shootbiomass2^power),data=StemP1,start = list(power=1.2321379,b=0.1452028),trace = T)

x=StemP1$Shootbiomass2
y=StemP1$StemWt1

test <- function(x) {0.1452028*x^1.2321379}
stat_function(fun = test)
# 
# #mdl1 <- lm(y ~ x, data = Leaf_Node1)
# #mdl2 <- lm(y ~ x + I(x^2), data = Leaf_Node1)
# #mdl3 <- lm(y ~ x + I(x^2) + I(x^3), data = Leaf_Node1)
# mdl4 <- nls(StemWt1~ I(b*Shootbiomass2^power),data=StemP1,start = list(power=1.2321379,b=0.1452028),trace = T)
# #mdl5<-lm(y ~ poly(x, 2, raw=TRUE),data = Leaf_Node1 )
# summary(mdl4)
# 
# prd <- data.frame(x = seq(0,500, by = 5.65))
# 
# result <- prd
# #result$mdl1 <- predict(mdl1, newdata = prd)
# #result$mdl2 <- predict(mdl2, newdata = prd)
# #result$mdl3 <- predict(mdl3, newdata = prd)
# result$mdl4 <- predict(mdl4, newdata = prd)
# #result$mdl5 <- predict(mdl5, newdata = prd)
# 
# result <-  melt(result, id.vars = "x", variable.name = "model",
#                 value.name = "fitted")
StemP1%>%
ggplot(aes(x = Shootbiomass2, y = StemWt1,colour=ID)) + geom_point(size = 2)+
  theme_bw() +stat_function(fun = test,color="black",size=1)+xlab(bquote(bold('Shoot DM ('*g~m^-2*')')))+ylab(bquote(bold('Stem DM ('*g~m^-2*')')))+
  annotate("text", y=300, x=200, size = 5, label ="paste(y == 0.14*x^1.23, ~~R^2==0.93)", parse=T)+
  theme(legend.title=element_blank())+mytheme3+theme(legend.title = element_blank())
ggsave("D:/R/Pictures/SL/SS.png", width=8, height=4, dpi=500)
``` 

```{r}
m <- nls(LeafWt~ I(Shootbiomass1^power),data=StemP,start = list(power = 0.8949526),trace = T)

 summary(m)$coefficients
# Make predictions
predictions <- m %>% predict(LeafP)
residules<- resid(m)
plot(residules ~ LeafP$Shootbiomass1)
##Plot model
plot(LeafP$LeafWt ~ LeafP$Shootbiomass1)
lines(LeafP$Shootbiomass1, fitted(m), lty = 2, col = "red", lwd = 0.5)
```
###Fit a power function
```{r}
m <- nls(LeafWt~ I(Shootbiomass1^power),data=LeafP,start = list(power = 1),trace = T)

summary(m)
 summary(m)$coefficients
```

```{r}
obsroot<-obsAll %>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason,Rotation)))%>%
  dplyr::filter(Water=="irr")%>%
  dplyr::filter(Defoliation=="LL")%>%
  dplyr::filter(FD=="FD5")%>%
  dplyr::filter(Variable=="RootWt")%>%
  mutate(RootWt=Observed)%>%
  mutate(StdDEVR=StdDEV)%>%
  dplyr::select(Clock.Today,Name,RootWt,StdDEVR)%>%
  mutate(RootWt1=RootWt*0.001)

ObsL.DM<-merge(obsroot,LeafP,by=c("Clock.Today","Name"))


phyll <- "D:\\R\\"
StartGrazing <- read.table(paste0(phyll, "ExperimentList.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(GrowthRotation= as.factor(paste0(GrowthSeason,Rotation)))
PartionPp<- merge(StartGrazing1,ObsL.DM,by=c("Name","Collection","GrowthRotation"))%>%
  mutate(TotalDM=RootWt+Shootbiomass1)

PartionPp%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
   ggplot(aes(x=TotalDM, y=Shootbiomass1,label=GrowthRotation,colour=Name))+geom_text()+theme_bw()+xlab("Shootbiomass")+ylab("rootWt")+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
 facet_grid(GrowthSeason.x~Rotation.x)+
  ggtitle("Iversen_8Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))


```
###Leaf wt and specific leaf
```{r}

obsLw<- obsAll %>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason,Rotation)))%>%
  dplyr::filter(Water=="irr")%>%
  dplyr::filter(Defoliation=="LL")%>%
  dplyr::filter(FD=="FD5")%>%
  dplyr::filter(Variable=="LAI"|Variable=="LeafWt")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL"|Name=="Iversen_121DefoliationLLFDFD5")
summary(obsLw)

```
```{r}
obsLw1<-obsLw%>%
  dplyr::filter(ExpUnitCode!="Iversen_121DefoliationLLFDFD5Gs_1Rt_1")%>%
  dplyr::filter(ExpUnitCode!="Iversen_121DefoliationLLFDFD5Gs_1Rt_3")%>%
  dplyr::filter(ExpUnitCode!="Iversen_121DefoliationLLFDFD5Gs_2Rt_5")%>%
 dplyr::filter(ExpUnitCode!="Iversen_121DefoliationLLFDFD5Gs_3Rt_4")%>%
  dplyr::filter(ExpUnitCode!="Iversen_121DefoliationLLFDFD5Gs_1Rt_4")%>%
  dplyr::filter(ExpUnitCode!="Iversen_121DefoliationLLFDFD5Gs_4Rt_3")
  
  
UniExp <- unique(obsLw1$ExpUnitCode)

LW.df <- data.frame()
  
for(i in 1:length(UniExp))
{
  
  ObsLW<-obsLw1%>%
   filter(ExpUnitCode==UniExp[i])
  
 LW<-ObsLW%>%
  unique()%>%
  tidyr::spread(Variable,Observed)
 
 LW.data<-LW%>%
  mutate( LAI.y=approx(LW$Clock.Today, LW$LAI, xout =LW$Clock.Today, 
         method="linear", 
         rule = 2)$y)##interpolate function 
  

 LW.df <- rbind(LW.df, LW.data)

}

summary(LW.df)
LW.df
```
```{r}
LW.df1<-LW.df%>%
  mutate(LeafWt=LeafWt*0.1)%>%
  dplyr::filter(Rotation!="1")
LW.df1%>%
  ggplot(aes(y=LAI.y, x=LeafWt,label=GrowthRotation,colour=ID))+geom_text()+theme_bw()+ylab("LAI (m^2/m^2) ")+xlab("Leaf biomass (g/m^2)")+xlab(bquote(bold('Leaf DM ('*g~m^-2*')')))+ylab(bquote(bold('LAI ('*m^2~m^-2*')')))+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+mytheme3+theme(legend.title = element_blank())+
  annotate("text", x=80, y=7, size = 5, label ="paste(y == 2.33+28.06*x,~~R^2==0.86)", parse=T)
  
x=LW.df1$LAI.y
y=LW.df1$LeafWt
M<-lm(y~x)
summary(M)
ggsave("D:/R/Pictures/SL/SLA.png", width=8, height=4, dpi=500)
  
```
```{r}
LW.df2<-LW.df%>%
  mutate(LeafWt=LeafWt*0.1)%>%
  dplyr::filter(Rotation=="1")
LW.df2%>%
  ggplot(aes(x=LAI.y, y=LeafWt,label=GrowthRotation,colour=Name))+geom_text()+theme_bw()+xlab("LAI")+ylab("LeafWt")+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  ggtitle("Iversen_8Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

x=LW.df2$LAI.y
y=LW.df2$LeafWt
M<-lm(y~x)
summary(M)
  
```


###Specific leaf area against time

```{r}
SLA <- LW.df%>%
  mutate(LeafWt=LeafWt*0.1)%>%
  mutate(SLA=LeafWt/LAI.y)
SLA%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  dplyr::filter(Rotation!="1")%>%
  ggplot(aes(x=Clock.Today, y=SLA,label=GrowthRotation,colour=Name))+geom_text()+theme_bw()+xlab("Clock.Today")+ylab("SLA (g/m^2)")+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  ggtitle("Iversen_8Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```


```{r}
SLA%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  ggplot(aes(x=Clock.Today, y=SLA,label=GrowthRotation,colour=Name))+geom_text()+theme_bw()+xlab("Photoperiod (h)")+ylab("SLA (g/m^2)")+
  geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  ggtitle("Iversen_8Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```

###load experiment data of leaf and stem ratio
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsAll <- read.table(paste0(obsData, "ObsAll.txt"),
                   header = TRUE)
obsLB<- obsAll %>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason,Rotation)))%>%
  dplyr::filter(Water=="irr")%>%
  dplyr::filter(Defoliation=="LL")%>%
  dplyr::filter(FD=="FD5")%>%
  dplyr::filter(Variable=="LeafWt")
summary(obsLB)
obsLB
```


###Leafwt 
## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r, round(r2*100,1))

  return(out)

}
```

## Test stats functions used

```{r}
s <- c(4231.972,3935.604,3779.652,3627.687,3363.499,3230.566,2868.114,2868.827)
m <- c(4987.66,5636.09,4754.06,4114.53,4141.72,3704.06,5142.19,4762.03)

x <- gauchStats(s,m)

tempDf <- data.frame(statName=c("SB","NU","LC","r_MSD","R2"), statValue=x)
# kable(tempDf, digits= 2)
tempDf2 <- data.frame(Predicted=s, Observed=m)

x <- tempDf2 %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>% 
  t() 

df <- data.frame(stat = row.names(x),statvalue = x[,1])

df %>%
  kable(format = "markdown")
```
## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneValidation.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
summary(df)
head(df) # simulation results
```
# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"_Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)

# myDb %>%
#   dplyr::select(Name) %>%
#   unique()

```
## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,SWC,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  tidyr::gather("Variable","Predicted",LAI:NodeNumber) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)
summary(simD)



mergedf<-merge(obsLB,simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)
mergedf

```
## Node number
#Time series
## obs Vs Pre for each experiment
## 1997-2001
```{r,fig.height=4, fig.width=9}

obsLB1<-obsLB%>%
  dplyr::filter(Collection=="1997_2001")%>%
  dplyr::filter(Variable=="LeafWt")%>%
  dplyr::filter(Name=="Iversen_8Waterirr")%>%
  dplyr::filter(Clock.Today>"1997-08-01")%>%
  dplyr::filter(Clock.Today<"2001-08-01")
  
  
   
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Clock.Today>"1997-08-01")%>%
   dplyr::filter(Clock.Today<"2001-08-01")%>%
   dplyr::filter(Variable=="LeafWt")%>%
   dplyr::filter(Name=="Iversen_8Waterirr")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~Name,ncol = 2)+
 geom_point(data=obsLB1, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Leaf (kg DM/ha)")+
 theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
##2002-2004
```{r,  fig.height=4, fig.width=8}
obsLB2<-obsLB%>% 
  dplyr::filter(Collection=="2002_2004")%>%
  dplyr::filter(Variable=="LeafWt")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")

simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2002-06-01")%>%
  dplyr::filter(Variable=="LeafWt")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
str(simD2)
simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 1)+
  geom_point(data=obsLB2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Leaf DM ('*kg~ha^-1*')')))+
  mytheme3+
  annotate("text", x=ymd_hms("2003-07-24 12:00:00"), y=2500, size = 5, label ="paste(R_RMSD == 33.7,'%')", parse=T)
 #geom_text(aes(x=ymd_hms("2003-07-24 12:00:00"), y=750, label="R_RMSD = 33.7%",size=5))
 ggsave("D:/R/Pictures/SL/Iversen_91DefoliationLLleaf1.png", width=8, height=4, dpi=500)
  
  
  


```

```{r,  fig.height=8, fig.width=8}
obsLB3<-obsLB%>%
  dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Variable=="LeafWt")


simD3<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2000-10-24 12:00:00")%>%
  dplyr::filter(Clock.Today<"2002-07-01 12:00:00")%>%
  dplyr::filter(Name!="Iversen_8Waterdry")%>%
  dplyr::filter(Name!="Iversen_8Waterirr")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="MooraDefoliation")%>%
  dplyr::filter(Name!="NekiaDefoliation")%>%
  dplyr::filter(Name!="QuairadingDefoliation")%>%
  dplyr::filter(Name!="RoseworthyWaterdry")%>%
  dplyr::filter(Name!="RoseworthyWaterirr")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD1Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD2Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD3Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD4Waterdry")%>%
  dplyr::filter(Variable=="LeafWt")
  str(simD3)
simD3%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 2)+
  geom_point(data=obsLB3, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  facet_wrap(~Name,ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Leaf(kg DM/ha)")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
```
##2014-2018
```{r,  fig.height=4, fig.width=8}
obsLB4<-obsLB%>%
  dplyr::filter(Collection=="2014_2018")%>%
  dplyr::filter(Variable=="LeafWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD4a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="LeafWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Clock.Today<"2015-01-06")


simD4b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="LeafWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Clock.Today>"2015-01-30")

simD4<-rbind(simD4a,simD4b)
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 1)+
  geom_point(data=obsLB4, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Leaf DM ('*kg~ha^-1*')')))+
  mytheme3+theme(legend.title = element_blank())+
  annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=2700, size = 5, label ="paste(R_RMSD == 60.3,'%')", parse=T)
 #geom_text(aes(x=ymd_hms("2003-07-24 12:00:00"), y=750, label="R_RMSD = 33.7%",size=5))
 ggsave("D:/R/Pictures/SL/Iversen_121DefoliationLLFDFD5leaf1.png", width=8, height=4, dpi=500)
  
  


```


# Statistic and Graph
```{r,,fig.height=4, fig.width=8}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "LeafWt") %>% 
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(Name))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Leaf")+
  facet_wrap(~ID, ncol = 4)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  scale_x_continuous(breaks = seq(0, 2000, by =1000), limits=c(0,2000))+
  #scale_x_continuous(breaks = seq(0, 600, by =200), limits=c(0,500))+
 mytheme3
ggsave("D:/R/Pictures/SL/predictleaf1.png", width=8, height=4, dpi=500)
```

## RMSE

```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "LeafWt") %>% 
 #filter(Variable == "NodeNumber") %>%
  filter(Collection!="2010_2012")%>%
  group_by(ID) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```


###load experiment data of stem
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsAll <- read.table(paste0(obsData, "ObsAll.txt"),
                   header = TRUE)
obsST<- obsAll %>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason,Rotation)))%>%
  dplyr::filter(Water=="irr")%>%
  dplyr::filter(Defoliation=="LL")%>%
  dplyr::filter(FD=="FD5")%>%
  dplyr::filter(Variable=="StemWt")
summary(obsST)
obsST
```


###Leafwt 
## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r, round(r2*100,1))

  return(out)

}
```

## Test stats functions used

```{r}
s <- c(4231.972,3935.604,3779.652,3627.687,3363.499,3230.566,2868.114,2868.827)
m <- c(4987.66,5636.09,4754.06,4114.53,4141.72,3704.06,5142.19,4762.03)

x <- gauchStats(s,m)

tempDf <- data.frame(statName=c("SB","NU","LC","r_MSD","R2"), statValue=x)
# kable(tempDf, digits= 2)
tempDf2 <- data.frame(Predicted=s, Observed=m)

x <- tempDf2 %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>% 
  t() 

df <- data.frame(stat = row.names(x),statvalue = x[,1])

df %>%
  kable(format = "markdown")
```
## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneValidation.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
summary(df)
head(df) # simulation results
```
# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"_Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)

# myDb %>%
#   dplyr::select(Name) %>%
#   unique()

```
## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,SWC,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  tidyr::gather("Variable","Predicted",LAI:NodeNumber) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)
summary(simD)



mergedf<-merge(obsST,simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)
mergedf

```
## Node number
#Time series
## obs Vs Pre for each experiment
## 1997-2001
```{r,fig.height=4, fig.width=9}

obsST1<-obsST%>%
  dplyr::filter(Collection=="1997_2001")%>%
  dplyr::filter(Variable=="StemWt")%>%
  dplyr::filter(Name=="Iversen_8Waterirr")%>%
  dplyr::filter(Clock.Today>"1997-08-01")%>%
  dplyr::filter(Clock.Today<"2001-08-01")
  
  
   
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Clock.Today>"1997-08-01")%>%
   dplyr::filter(Clock.Today<"2001-08-01")%>%
   dplyr::filter(Variable=="StemWt")%>%
   dplyr::filter(Name=="Iversen_8Waterirr")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~Name,ncol = 2)+
 geom_point(data=obsST1, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Stem (kg DM/ha)")+
 theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
##2002-2004
```{r,  fig.height=4, fig.width=8}
obsST2<-obsST%>%
  dplyr::filter(Collection=="2002_2004")%>%
  dplyr::filter(Variable=="StemWt")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")

simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2002-06-01")%>%
  dplyr::filter(Variable=="StemWt")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
str(simD2)
simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 1)+
  geom_point(data=obsST2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Stem DM ('*kg~ha^-1*')')))+
  mytheme3+
  annotate("text", x=ymd_hms("2003-07-24 12:00:00"), y=4000, size = 5, label ="paste(R_RMSD == 31.5,'%')", parse=T)
 #geom_text(aes(x=ymd_hms("2003-07-24 12:00:00"), y=750, label="R_RMSD = 27.6%",size=5))
 ggsave("D:/R/Pictures/SL/Iversen_91DefoliationLLstem1.png", width=8, height=4, dpi=500)

  
  


```

```{r,  fig.height=8, fig.width=8}
obsST3<-obsST%>%
  dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Variable=="StemWt")


simD3<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2000-10-24 12:00:00")%>%
  dplyr::filter(Clock.Today<"2002-07-01 12:00:00")%>%
  dplyr::filter(Name!="Iversen_8Waterdry")%>%
  dplyr::filter(Name!="Iversen_8Waterirr")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="MooraDefoliation")%>%
  dplyr::filter(Name!="NekiaDefoliation")%>%
  dplyr::filter(Name!="QuairadingDefoliation")%>%
  dplyr::filter(Name!="RoseworthyWaterdry")%>%
  dplyr::filter(Name!="RoseworthyWaterirr")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD1Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD2Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD3Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD4Waterdry")%>%
  dplyr::filter(Variable=="StemWt")
  str(simD3)
simD3%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 2)+
  geom_point(data=obsST3, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  facet_wrap(~Name,ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Stem (kg DM/ha)")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
```
##2014-2018
```{r,  fig.height=4, fig.width=8}
obsST4<-obsST%>%
  dplyr::filter(Collection=="2014_2018")%>%
  dplyr::filter(Variable=="StemWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD5a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="StemWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Clock.Today<"2015-01-06")


simD5b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="StemWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Clock.Today>"2015-01-30")

simD5<-rbind(simD5a,simD5b)
simD5%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 1)+
  geom_point(data=obsLB4, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+
  ylab(bquote(bold('Stem DM ('*kg~ha^-1*')')))+
  mytheme2+
  annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=6000, size = 5, label ="paste(R_RMSD == 92.3,'%')", parse=T)
 #geom_text(aes(x=ymd_hms("20016-07-24 12:00:00"), y=750, label="R_RMSD = 27.6%",size=5))
 ggsave("D:/R/Pictures/SL/Iversen_121DefoliationLLFDFD5stem1.png", width=8, height=4, dpi=500)

```


# Statistic and Graph
```{r,,fig.height=4, fig.width=8}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "StemWt") %>% 
  ggplot(aes(x=Observed, y= Predicted, colour= factor(Name))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Stem")+
  facet_wrap(~Name, ncol = 4)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+mytheme3
  ggsave("D:/R/Pictures/SL/predicted.png", width=8, height=4, dpi=500)
```

## RMSE

```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "StemWt") %>% 
 #filter(Variable == "NodeNumber") %>%
  filter(Collection!="2010_2012")%>%
  group_by(ID) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```





