---
title: "R Notebook"
output: html_notebook
---
###NodeNumber analysis

```{r Load, warning=FALSE, fig.height=8, fig.width=8}
# install.packages("zoo")
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)
```
# ### load obs data
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsAll <- read.table(paste0(obsData, "ObsAll.txt"),
                   header = TRUE)
obsA<- obsAll %>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))
  
summary(obsA)
obsA
```
```{r}
upDir <- "D:/R/"
obsData <- "D:/R/TtAll/"

Tt<- read.table(paste0(obsData, "df.all.txt"),
               header = TRUE)
TtA <- Tt %>% mutate(Clock.Today=dmy(Clock.Today), ExpUnitCode=as.factor(ExpName))
TtA
ObsH <-merge(obsA,TtA,by=c("Clock.Today","ExpUnitCode")) %>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))%>%
  dplyr::filter(Water.x=="irr")%>%
  dplyr::filter(Defoliation.x=="LL")%>%
  dplyr::filter(Variable=="NodeNumber")
  

summary(ObsH)
```

```{r,fig.height=6, fig.width=8}
obsNode<-ObsH%>%
  dplyr::filter(Tb==1)
 
obsNode
# phyll <- "D:\\R\\Data statistic\\"
# StartGrazing <- read.table(paste0(phyll, "obsTphy.txt"), 
#                       header = TRUE)
# StartGrazing1<-StartGrazing %>%
#   mutate(StartDate = dmy(StartDate))%>%
#   mutate(MidDate = dmy(MidDate))%>%
#   mutate(FinishDate= dmy(FinishDate))%>%
#   mutate(Rotation=as.factor(Rotation))
# 
# StartGrazing1
# 
# obsf<- merge(obsNode,StartGrazing1,by=c("Name","Collection","GrowthSeason","Rotation","GrowthRotation"))
# obsf
# obsef<-obsf%>%
#   mutate(BudV=dmy(BudV))%>%
#   mutate(Flowering=dmy(Flowering))%>%
#   mutate(Ture=ifelse(Clock.Today<=BudV,"Yes","No"))
# 
# obsef
#  
# obsef1<-obsef %>%
#       mutate(Ture = ifelse(is.na(Ture),"A",Ture))
#   
obsNodeF<-obsNode%>%
  #dplyr::filter(Ture!="No")%>%
  dplyr::filter(Name=="Iversen_8Waterirr")%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd) ")+ylab("Node number"   )+ggtitle("Iversen_8Waterirr")  +
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason.x~Rotation.x)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```

```{r,fig.height=4, fig.width=8}
obsNode1<-obsNode%>%
  #dplyr::filter(Ture!="No")%>%
  dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD1Waterirr")
obsNode1%>%
  ggplot(aes(x=Tt_beta_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd) ")+ylab("Node number")+ggtitle("Iversen_9SowingDateSD1Waterirr")+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason.x~Rotation.x)+theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
```
```{r,fig.height=3, fig.width=10}
obsNode2<-obsNode%>%
  #dplyr::filter(Ture!="No")%>%
  dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD2Waterirr")
obsNode2%>%
  ggplot(aes(x=Tt_beta_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd)")+ylab("Node number")+ggtitle("Iversen_9SowingDateSD2Waterirr")+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason.x~Rotation.x)+theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
```

```{r,fig.height=3, fig.width=10}
obsNode1<-obsNode%>%
  #dplyr::filter(Ture!="No")%>%
  dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD3Waterirr")
obsNode1%>%
  ggplot(aes(x=Tt_beta_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd)")+ylab("Node number")+ggtitle("Iversen_9SowingDateSD3Waterirr")+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason.x~Rotation.x)+theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
```
```{r,fig.height=3, fig.width=10}
obsNode1<-obsNode%>%
  #dplyr::filter(Ture!="No")%>%
  dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD4Waterirr")
obsNode1%>%
  ggplot(aes(x=Tt_beta_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd)")+ylab("Node number")+ggtitle("Iversen_9SowingDateSD4Waterirr")+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason.x~Rotation.x)+theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
```


```{r,fig.height=4, fig.width=8}
obsNode%>%
  #dplyr::filter(Ture!="No")%>%  
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  ggplot(aes(x=Tt_beta_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd)")+ylab("Node number")+ggtitle("Iversen_91DefoliationLL")+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason.x~Rotation.x)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

```{r,fig.height=5, fig.width=8}
obsNodeLL<-obsNode%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")
obsNodeLL%>%
  ggplot(aes(x=Tt_beta_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd)")+ylab("Node number")+ggtitle("Iverson_121DefoliationLLFDFD5")+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason.x~Rotation.x)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```

###R squared and phyllo calculation for each rotation
##TTWES1
##Tb evaluation 
```{r}
#obsef1%>%
 # dplyr::filter(Ture!="No")
 # statWE1<-ObsH%>%
 # filter(Variable == "NodeNumber") %>%
 #  filter(Water=="irr")%>%
 #  filter(Defoliation=="LL")%>%
 #  mutate(GrowthSeason=factor(GrowthSeason))%>%
 #  group_by(GrowthSeason,Collection) %>%

uniTb <- unique(ObsH$Tb)

PhyBeta.all <- data.frame()
 
for(i in 1:length(uniTb)){
  
  ObsH1 <- ObsH %>%
  filter(Tb==uniTb[i])
  
   ObsH.sub <- ObsH1 %>%
  group_by(Name,GrowthSeason.x,Rotation.x,Collection,Tmean,Ppm,Tb) %>%
    do(mod.beta = lm(Tt_beta_sum~Observed,data=.))%>%
  mutate(R2WE = summary(mod.beta)$r.squared)%>%
  mutate(PhylloWE = summary(mod.beta)$coeff[2])%>%
  dplyr::select(-mod.beta)

  PhyBeta.all <- rbind(PhyBeta.all, ObsH.sub)
}
  
PhyBeta.all
write.csv(PhyBeta.all,"D:/R/PhyllochronData/PhyBeta.all.csv", row.names = FALSE)

```
```{r}
uniTb <- unique(ObsH$Tb)

Phybroken.all <- data.frame()
 
for(i in 1:length(uniTb)){
  
  ObsH1 <- ObsH %>%
  filter(Tb==uniTb[i])
  
   ObsH.sub <- ObsH1 %>%
  group_by(Name,GrowthSeason.x,Rotation.x,Collection,Tmean,Ppm,Tb) %>%
    do(mod.broken = lm(Tt_broken_sum~Observed,data=.))%>%
    #do(mod.fick = lm(Tt_fick_sum~Observed,data=.))%>%
  mutate(R2Br = summary(mod.broken)$r.squared)%>%
  mutate(PhylloBr = summary(mod.broken)$coeff[2])%>%
  mutate(P=anova(mod.broken)$'Pr(>F)'[1])%>% 
  mutate(intcp= summary(mod.broken)$coeff[1])%>%  
  dplyr::select(-mod.broken)

  Phybroken.all <- rbind(Phybroken.all, ObsH.sub)
}
  
Phybroken.all
write.csv(Phybroken.all,"D:/R/PhyllochronData/Phybroken.all.csv", row.names = FALSE)
```

```{r}
uniTb <- unique(ObsH$Tb)

Phyfick.all <- data.frame()
 
for(i in 1:length(uniTb)){
  
  ObsH1 <- ObsH %>%
  filter(Tb==uniTb[i])
  
   ObsH.sub <- ObsH1 %>%
  group_by(Name,GrowthSeason.x,Rotation.x,Collection,Tmean,Ppm,Tb) %>%
    do(mod.fick = lm(Tt_fick_sum~Observed,data=.))%>%
  mutate(R2fi = summary(mod.fick)$r.squared)%>%
  mutate(Phyllofick = summary(mod.fick)$coeff[2])%>%
  dplyr::select(-mod.fick)

  Phyfick.all <- rbind(Phyfick.all, ObsH.sub)
}
  
Phyfick.all
write.csv(Phyfick.all,"D:/R/PhyllochronData/Phyfick.all.csv", row.names = FALSE)
```


<!-- ##TTWES2 -->
<!-- ```{r} -->
<!-- #obsef1%>% -->
<!--  # dplyr::filter(Ture!="No") -->
<!-- statWE2<-obsNode%>% -->
<!--  filter(Variable == "NodeNumber") %>% -->
<!--   filter(Water=="irr")%>% -->
<!--   filter(Defoliation=="LL")%>% -->
<!--   mutate(GrowthSeason=factor(GrowthSeason))%>% -->
<!--   group_by(GrowthSeason,Collection) %>% -->
<!--   group_by(Name,GrowthSeason,Rotation,Collection,Tmean,Pmean) %>% -->
<!--   do(mod = lm(TTWES2~Observed,data=.)) %>% -->
<!--   mutate(R2WE2 = summary(mod)$r.squared) %>% -->
<!--   mutate(PhylloWE2 = summary(mod)$coeff[2]) %>% -->
<!--   dplyr::select(-mod) -->

<!--   WE2R2<-statWE2%>% -->
<!--   group_by(Collection)%>% -->
<!--   mutate(meanR2WE2=mean(R2WE2)) -->
<!--   WE2R2 -->
<!--   write.csv(WE2R2,"D:/R/Phyllo/WE2R2.csv", row.names = FALSE) -->

<!-- ``` -->


### Combine the Phyllo data together
```{r,fig.height=5, fig.width=10,warning=FALSE}
multmerge = function(mypath){
filenames=list.files(path=mypath, full.names=TRUE)
datalist = lapply(filenames, function(x){read.csv(file=x,header=T)})
Reduce(function(x,y) {merge(x,y)}, datalist)}

mergephy=multmerge("D:/R/PhyllochronData")
mergephy

```

```{r}

mergeP<-mergephy%>%
   dplyr::select(Name,GrowthSeason.x,Rotation.x,Collection,Tmean, Ppm,Tb, PhylloWE,PhylloBr,Phyllofick) %>%
  tidyr::gather("Variable","Phyllo",PhylloWE:Phyllofick)%>%
  mutate(PhylloTb=as.factor(paste0(Variable,Tb)))%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))
unique(mergeP)

mergeP$Names[mergeP$Name=="Iversen_8Waterirr" ] <-"I8irr"
mergeP$Names[mergeP$Name=="Iversen_91DefoliationLL"] <-"I9LL"
mergeP$Names[mergeP$Name=="Iversen_9SowingDateSD1Waterirr"]<-"I9SD1irr"
mergeP$Names[mergeP$Name=="Iversen_9SowingDateSD2Waterirr"]<-"I9SD2irr"
mergeP$Names[mergeP$Name=="Iversen_9SowingDateSD3Waterirr"]<-"I9SD3irr"
mergeP$Names[mergeP$Name=="Iversen_9SowingDateSD4Waterirr"]<-"I9SD4irr"
mergeP$Names[mergeP$Name=="Iversen_121DefoliationLLFDFD5"]<-"I12DF5"
mergeP

```
##Regression coefficient
```{r}
mergeP%>%
 ggplot(aes(x=Tmean, y=Phyllo, colour=factor(Names)))+geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey")+xlab("Mean air temperature (°C)")+ylab("Phyllochron (°Cd/Leaf)")+
  facet_wrap(~PhylloTb,ncol = 2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
```

```{r}

uniPhy <- unique(mergeP$PhylloTb)
Slope.df<-data.frame()

for(i in 1:length(uniPhy) ){
   mergeP.sub <- mergeP %>%
     filter(PhylloTb==uniPhy[i])%>%
   group_by(PhylloTb) %>%
    do(modPhy = lm(Tmean~Phyllo,data=.))%>%
  mutate(R2 = summary(modPhy)$r.squared)%>%
  mutate(slope = summary(modPhy)$coeff[2])%>%
  mutate(P=anova(modPhy)$'Pr(>F)'[1])%>%  
  dplyr::select(-modPhy)
     
   Slope.df <- rbind(Slope.df,mergeP.sub)
  
}
 Slope.df

```


##CV coeffecient of variation
```{r,fig.height=4, fig.width=10}
mergeP

mergePcv<-mergeP%>%group_by(Collection, Variable)%>%
 mutate(meanPhyllo=mean(Phyllo))%>%
  mutate(SDPhyllo=sd(Phyllo))%>%
  mutate(CVPhyllo=SDPhyllo/meanPhyllo)
mergePcv
mergePcv1<-mergePcv%>%group_by(Variable)%>%
  mutate(CVmean=mean(CVPhyllo))

mergePcv%>%
  ggplot(aes(x=PhylloTb,y=CVPhyllo,color=factor(Collection)))+geom_point(size=2)+theme_bw()
  
mergePcv1%>%
  ggplot(aes(x=PhylloTb,y=CVmean))+geom_point(size=2)+theme_bw()
mergePcv1

```

###x-intercept method

```{r}

LAR2<-ObsH%>%  
  group_by(Name,GrowthSeason.x,Rotation.x,Collection,Tmean,Ppm,GrowthRotation) %>%
  do(mod = lm(Observed~Interval,data=.)) %>%
  mutate(slope = summary(mod)$coeff[2]) %>%
   mutate(R2 = summary(mod)$r.squared)%>%
  mutate(P=anova(mod)$'Pr(>F)'[1])%>%  
  mutate(intcp= summary(mod)$coeff[1])%>%
  dplyr::select(-mod)
LAR.ana<- ObsH%>%  
  group_by(Collection) %>%
  do(mod = lm(Observed~Interval,data=.)) %>%
  mutate(slope = summary(mod)$coeff[2]) %>%
   mutate(R2 = summary(mod)$r.squared)%>%
  mutate(P=anova(mod)$'Pr(>F)'[1])%>%  
  mutate(intcp= summary(mod)$coeff[1])%>%
  dplyr::select(-mod)

LAR2%>%
  dplyr::filter(Rotation.x!="6"|Collection!="1997_2001")%>%
  #dplyr::filter(GrowthRotation!="11"|Collection!="2000_2002")%>%
 dplyr::filter(Collection!="2010_2012")
 mutate(Name=factor(Name))%>%
 ggplot(aes(x=Tmean, y=slope,label=GrowthRotation))+geom_text()+theme_bw()+xlab("Mean air temperature (°C)")+ylab("Node appearance rate (leaves/day)")+scale_x_continuous(limits=c(0,20))+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
 facet_wrap(~Collection)+
 theme(legend.title=element_blank())+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") 

```

```{r}
LAR2
  #dplyr::filter(Rotation!="6"|Collection!="1997_2001")
LAR2.lm=lm(slope~Tmean,data=LAR2)
summary(LAR2.lm)
predict(LAR2.lm, LAR2, interval="predict")
```


```{r}

# LARs<-LAR1%>%
#   dplyr::filter(Collection=="2014_2018")
# 
# LAR.lm = lm(Observed ~ TTS2, data=LARs) 
# LAR.res = resid(LAR.lm)
# 
# 
# plot(LARs$Clock.Today, LAR.res, ylab="Residuals", xlab="Date") 
# abline(0, 0) 

```


#load Rotation and Growth season
```{r,fig.height=6, fig.width=10}
phyll <- "D:\\R\\"
StartGrazing <- read.table(paste0(phyll, "ExperimentList.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(GrowthRotation= as.factor(paste0(GrowthSeason,Rotation)))
PhyPp<- merge(StartGrazing1,mergeP,by=c("Name","Collection","GrowthRotation"))

PhyPp
mergeP

PhyPp%>%
  #dplyr::filter(Rotation!="1")%>%
  #dplyr::filter(Rotation!="7")%>%
  #dplyr::filter(Name!="Iversen_8Waterirr"|GrowthSeason!="3")%>%
  #dplyr::filter(Stage!="Seedling")%>%
  dplyr::filter(PhylloTb=="PhylloBr1")%>%
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Ppm, y=Phyllo,label=GrowthRotation,color=Name))+geom_text()+theme_bw()+xlab("Mean photoperiod(h) ")+ylab("Phyllochron (°Cd/primary leaves)")+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey")+
  facet_grid(Trend~Stage)+
  #facet_wrap(~Stage,ncol = 2)+
  #geom_point(size=2)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+
  theme(legend.title=element_blank())
```

```{r}
PhyPpD<-PhyPp%>%
  dplyr::filter(Stage=="Regrowth")%>%
  dplyr::filter(Trend=="Dec")
mod<-lm(PhyPpD$Phyllo~PhyPpD$Ppm)
summary(mod)

PhyPpI<-PhyPp%>%
  dplyr::filter(Stage=="Regrowth")%>%
  dplyr::filter(Trend!="Dec")
mod<-lm(PhyPpI$Phyllo~PhyPpI$Ppm)
summary(mod)
```




## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r, round(r2*100,1))

  return(out)

}
```

## Test stats functions used

```{r}
s <- c(4231.972,3935.604,3779.652,3627.687,3363.499,3230.566,2868.114,2868.827)
m <- c(4987.66,5636.09,4754.06,4114.53,4141.72,3704.06,5142.19,4762.03)

x <- gauchStats(s,m)

tempDf <- data.frame(statName=c("SB","NU","LC","r_MSD","R2"), statValue=x)
# kable(tempDf, digits= 2)
tempDf2 <- data.frame(Predicted=s, Observed=m)

x <- tempDf2 %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>% 
  t() 

df <- data.frame(stat = row.names(x),statvalue = x[,1])

df %>%
  kable(format = "markdown")
```
## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneValidation.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
summary(df)
head(df) # simulation results
```
# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"_Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)

# myDb %>%
#   dplyr::select(Name) %>%
#   unique()

```
## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,SWC,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  tidyr::gather("Variable","Predicted",LAI:NodeNumber) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)
summary(simD)


head(obsNode)
mergedf<-merge(obsA,simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)
mergedf

```


## Node number
#Time series
## obs Vs Pre for each experiment
## 1997-2001
```{r,fig.height=4, fig.width=9}

obsNode1<-obsA%>%
  dplyr::filter(Collection=="1997_2001")%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_8Waterirr")%>%
  dplyr::filter(Clock.Today>"1997-08-01")%>%
  dplyr::filter(Clock.Today<"2001-08-01")
  
  
   
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Clock.Today>"1997-08-01")%>%
   dplyr::filter(Clock.Today<"2001-08-01")%>%
   dplyr::filter(Variable=="NodeNumber")%>%
   dplyr::filter(Name=="Iversen_8Waterirr")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~Name,ncol = 2)+
 geom_point(data=obsNode1, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
 theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```


##2002-2004
```{r,  fig.height=4, fig.width=8}
obsNode2<-obsNode%>% 
  dplyr::filter(Collection=="2002_2004")%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")

simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2002-06-01")%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
str(simD2)
simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 1)+
  geom_point(data=obsNode2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
  


```
##2000-2002
```{r,  fig.height=8, fig.width=8}
obsNode3<-obsNode%>%
  dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Variable=="NodeNumber")
 obsNode3 

simD3<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2000-10-24 12:00:00")%>%
  dplyr::filter(Clock.Today<"2002-07-01 12:00:00")%>%
  dplyr::filter(Name!="Iversen_8Waterdry")%>%
  dplyr::filter(Name!="Iversen_8Waterirr")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="MooraDefoliation")%>%
  dplyr::filter(Name!="NekiaDefoliation")%>%
  dplyr::filter(Name!="QuairadingDefoliation")%>%
  dplyr::filter(Name!="RoseworthyWaterdry")%>%
  dplyr::filter(Name!="RoseworthyWaterirr")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD1Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD2Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD3Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD4Waterdry")%>%
  dplyr::filter(Variable=="NodeNumber")
  str(simD3)
simD3%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 2)+
  geom_point(data=obsNode3, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  facet_wrap(~Name,ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
```
##2014-2018
```{r,  fig.height=4, fig.width=8}
obsNode4<-obsNode%>% 
  dplyr::filter(Collection=="2014_2018")%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD4<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Clock.Today>"2015-01-06")%>%
  dplyr::filter(Clock.Today<"2015-01-29")
  
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 1)+
  geom_point(data=obsNode4, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
  


```

# Statistic and Graph
```{r,fig.height=6, fig.width=10}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
   dplyr::filter(Water== "irr")%>%
  dplyr::filter(Defoliation== "LL")%>%
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(Name))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_wrap(~Collection, ncol = 4)+
  theme(legend.title=element_blank())+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```


## 2002-2004

```{r}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Collection=="2002_2004")%>%
  dplyr::filter(Variable== "NodeNumber") %>% 
   dplyr::filter(Water== "irr")%>%
  dplyr::filter(Defoliation== "LL")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_grid(GrowthSeason~Rotation)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```
```{r}
mergedf %>%
    dplyr::filter(Collection=="2014_2018")%>%
  dplyr::filter(Variable== "NodeNumber") %>% 
   dplyr::filter(Water== "irr")%>%
  dplyr::filter(Defoliation== "LL")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_grid(GrowthSeason~Rotation)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```



## 2000-2002

```{r}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Variable== "NodeNumber") %>% 
   dplyr::filter(Water== "irr")%>%
  dplyr::filter(Defoliation== "LL")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_grid(GrowthSeason~Rotation)+
  theme(legend.title=element_blank())+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```




```{r}
mergedf %>%
    dplyr::filter(Collection=="1997_2001")%>%
  dplyr::filter(Variable== "NodeNumber") %>% 
   dplyr::filter(Water== "irr")%>%
  dplyr::filter(Defoliation== "LL")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw() +
   geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1) +
  ggtitle("Node Number")  +
  facet_grid(GrowthSeason~Rotation)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

```{r, warning=FALSE}
mergedf %>%
    dplyr::filter(Collection=="1997_2001")%>%
  dplyr::filter(Variable== "NodeNumber") %>% 
   dplyr::filter(Water== "irr")%>%
  dplyr::filter(Defoliation== "LL")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw() +
   geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1) +
  ggtitle("Node Number")  +
  # facet_grid(.~Rotation) + # Rotation
  facet_wrap(~GrowthSeason, ncol = 4)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

## RMSE

```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "NodeNumber") %>% 
   dplyr::filter(Water== "irr")%>%
  dplyr::filter(Defoliation== "LL")%>%
 #filter(Variable == "NodeNumber") %>%
 #filter(Collection=="2010-2012")%>%
  mutate(Rotation= as.factor(Rotation))%>%
  mutate(GrowthSeason=as.factor(GrowthSeason))%>%
  group_by(Name) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```



