---
title: "R Notebook"
output: html_notebook
---
###Height analysis

```{r Load, warning=FALSE, fig.height=8, fig.width=8}
# install.packages("zoo")
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)
```
## lode observed data
```{r, echo=FALSE}
obsTt <- "D:\\R\\TmeanRotation\\"
obsH <- read.table(paste0(obsTt, "obsTt.txt"), 
                      header = TRUE)
obsH1<-obsH%>%
  mutate(Rotation = factor(Rotation))%>%
  mutate(Clock.Today = dmy(Clock.Today))
obsH1$Clock.Today1 <-as.POSIXct(paste(obsH1$Clock.Today,obsH1$Time),format="%Y-%m-%d %H:%M:%S")
obsH1
```

```{r}
obsNode<-obsH1%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Water=="irr")%>%
  dplyr::filter(Defoliation=="LL")
 
obsNode%>%
  dplyr::filter(Name=="Iversen_8Waterirr")%>%
  ggplot(aes(x=TTS2, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time ")+ylab("Node number")+
 facet_grid(GrowthSeason~Rotation)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
```{r}
obsNode%>%
  dplyr::filter(Collection=="2000_2002")%>%
  ggplot(aes(x=TTS2, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time ")+ylab("Node number")+
 facet_grid(GrowthSeason~Rotation)+theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
```
```{r}
obsNode%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  ggplot(aes(x=TTS2, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time ")+ylab("Node number")+
 facet_grid(GrowthSeason~Rotation)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```


```{r}

Phyllochron <- obsNode%>%
  mutate(GrowthSeason=factor(GrowthSeason))%>%
  group_by(Name,GrowthSeason,Rotation,Collection,Tmean,Pmean) %>%
  do(mod = lm(TTS2~Observed,data=.)) %>%
  mutate(Phyllo = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)

Phyllochron

```
##load Rotation and Growth season
```{r}
phyll <- "D:\\R\\Data statistic\\"
StartGrazing <- read.table(paste0(phyll, "obsTphy.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(Clock.Today = dmy(Clock.Today))%>%
  mutate(MidDate = dmy(MidDate))%>%
  mutate(FinishDate= dmy(FinishDate))
PhyPp<- merge(StartGrazing1,Phyllochron,by=c("Name","GrowthSeason","Rotation","Collection"))

PhyPp%>%
  #dplyr::filter(GrowthRotation!="11")%>%
  ggplot(aes(x=Pmean, y=Phyllo), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Mean photoperiod ")+ylab("Phyllochron")+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey")+
  facet_wrap(~Stage)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

  
```

## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r, round(r2*100,1))

  return(out)

}
```

## Test stats functions used

```{r}
s <- c(4231.972,3935.604,3779.652,3627.687,3363.499,3230.566,2868.114,2868.827)
m <- c(4987.66,5636.09,4754.06,4114.53,4141.72,3704.06,5142.19,4762.03)

x <- gauchStats(s,m)

tempDf <- data.frame(statName=c("SB","NU","LC","r_MSD","R2"), statValue=x)
# kable(tempDf, digits= 2)
tempDf2 <- data.frame(Predicted=s, Observed=m)

x <- tempDf2 %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>% 
  t() 

df <- data.frame(stat = row.names(x),statvalue = x[,1])

df %>%
  kable(format = "markdown")
```
## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneValidation.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
summary(df)
head(df) # simulation results
```
# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"_Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)

# myDb %>%
#   dplyr::select(Name) %>%
#   unique()

```
## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,SWC,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  tidyr::gather("Variable","Predicted",LAI:NodeNumber) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)
summary(simD)


head(obsNode)
mergedf<-merge(obsNode,simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)
mergedf

```


## Node number
#Time series
## obs Vs Pre for each experiment
## 1997-2001
```{r,fig.height=4, fig.width=9}

obsNode1<-obsNode%>%dplyr::filter(Collection=="1997_2001")
  
 
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Variable=="NodeNumber")%>%
   dplyr::filter(Name=="Iversen_8Waterirr")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~Name,ncol = 2)+
 geom_point(data=obsNode1, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
 theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```


##2002-2004
```{r,  fig.height=4, fig.width=8}
obsNode2<-obsNode%>% dplyr::filter(Name=="Iversen_91DefoliationLL")

simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
str(simD2)
simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 1)+
  geom_point(data=obsNode2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
  


```
##2000-2002
```{r,  fig.height=8, fig.width=8}
obsNode3<-obsNode%>%
  dplyr::filter(Collection=="2000_2002")
 obsNode3 

simD3<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2000-10-24 12:00:00")%>%
  dplyr::filter(Clock.Today<"2002-07-01 12:00:00")%>%
  dplyr::filter(Name!="Iversen_8Waterdry")%>%
  dplyr::filter(Name!="Iversen_8Waterirr")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="MooraDefoliation")%>%
  dplyr::filter(Name!="NekiaDefoliation")%>%
  dplyr::filter(Name!="QuairadingDefoliation")%>%
  dplyr::filter(Name!="RoseworthyWaterdry")%>%
  dplyr::filter(Name!="RoseworthyWaterirr")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD1Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD2Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD3Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD4Waterdry")%>%
  dplyr::filter(Variable=="NodeNumber")
  str(simD3)
simD3%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 2)+
  geom_point(data=obsNode3, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  facet_wrap(~Name,ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  
```


# Statistic and Graph
```{r,  fig.height=6, fig.width=8}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_wrap(~Collection, ncol = 3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```


## 2002-2004

```{r,  fig.height=8, fig.width=10}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Collection=="2002_2004")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_grid(GrowthSeason~Rotation)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```


## 2000-2002

```{r,  fig.height=8, fig.width=10}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Collection=="2000_2002")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_grid(GrowthSeason~Rotation)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```




```{r, fig.width=8, fig.height=8, warning=FALSE}
mergedf %>%
    dplyr::filter(Collection=="1997_2001")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw() +
   geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1) +
  ggtitle("Node Number")  +
  facet_wrap(~Rotation, ncol = 4)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

```{r, warning=FALSE}
mergedf %>%
    dplyr::filter(Collection=="1997_2001")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw() +
   geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1) +
  ggtitle("Node Number")  +
  # facet_grid(.~Rotation) + # Rotation
  facet_wrap(~GrowthSeason, ncol = 4)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

## RMSE

```{r}
str(mergedf)

mergedf %>%
 #filter(Variable == "NodeNumber") %>%
 #filter(Collection=="2010-2012")%>%
  mutate(Rotation= as.factor(Rotation))%>%
  mutate(GrowthSeason=as.factor(GrowthSeason))%>%
  group_by(Name) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

# %>%
#   group_by(Variable,Name) %>%
#   summarise_each(funs(mean))
  
```

```{r}
mergedf %>%
  mutate(Rotation= as.factor(Rotation))%>%
  mutate(GrowthSeason=as.factor(GrowthSeason))%>%
  group_by(GrowthRotation,Collection,Name) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

```

