---
title: "R Notebook"
output: html_notebook
---
###PAR analysis and LAI

```{r Load, warning=FALSE, fig.height=8, fig.width=8}
# install.packages("zoo")
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)
library(lme4)
library(reshape2)
```

## lode observed data
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsAll <- read.table(paste0(obsData, "ObsAll1.txt"),
                   header = TRUE)
obsA<- obsAll %>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))
  
summary(obsA)
obsA
```

#Load Tt and Join Observed data together
##Select LAI variable
```{r}
upDir <- "D:/R/"
obsData <- "D:/R/TtAll/"

Tt<- read.table(paste0(obsData, "df.all.txt"),
               header = TRUE)
TtA <- Tt %>% mutate(Clock.Today=dmy(Clock.Today), ExpUnitCode=as.factor(ExpName))
TtA
ObsL.Raw <-merge(obsA,TtA,by=c("Clock.Today","ExpUnitCode"))
ObsPAR<-ObsL.Raw%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))%>%
  dplyr::filter(Water.x=="irr")%>%
  dplyr::filter(Defoliation.x=="LL")%>%
  dplyr::filter(FD.x=="FD5")%>%
  dplyr::filter(Variable=="LAI"|Variable=="Fraction")%>%
  dplyr::filter(Tbb==1)
  
summary(ObsPAR)
ObsPAR
```
##my theme
```{r}
mytheme3<-theme(
     #legend.title = element_text(), 
     legend.text = element_text(colour="black", size = 12,face="plain"),
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
```

###LAI and PAR
```{r,fig.height=4, fig.width=8}
ObsLP<-ObsPAR%>%
  unique()%>%
  dplyr::filter(Collection!="2010_2012")%>%
  dplyr::select(Clock.Today,ExpUnitCode,Name,Collection,GrowthSeason.x,Rotation.x,StartDate,MidDate,FinishDate,Interval,Variable,VariableUnits,Time,Observed,StdDEV,GrowthRotation,ID,ExperimentID)

ObsLAI <- ObsLP%>%
  dplyr::filter(Variable=="LAI")
ObsP <- ObsLP%>%
  dplyr::filter(Variable=="Fraction")
  
ObsPL<-merge(ObsLAI,ObsP,by=c("Clock.Today","ExpUnitCode","Name","Collection","GrowthSeason.x","Rotation.x","StartDate","MidDate","FinishDate","Interval","Time","GrowthRotation","ID","ExperimentID"))

phyll <- "D:\\R\\"
StartGrazing <- read.table(paste0(phyll, "ExperimentList.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(GrowthRotation= as.factor(paste0(GrowthSeason,Rotation)))
ObsPL1<- merge(StartGrazing1,ObsPL,by=c("Name","Collection","GrowthRotation"))%>%
 dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthSeason.x!="2")%>%
  dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="13")%>%
  dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="33")%>%
  dplyr::filter(ID!="E3ILL"|GrowthRotation!="14")

test1 <- function(x) {1-exp(-0.81*x)}
stat_function(fun = test1)
 
ObsPL1%>%
  dplyr::filter(Stage=="Regrowth")%>%
  ggplot(aes(x=Observed.x,y=Observed.y,shape=ID,label=GrowthRotation))+theme_bw()+ylab("Franctional radiation interception")+xlab(bquote(bold('LAI ('*m^2~m^-2*')')))+
  geom_point(size=2)+theme(legend.title = element_blank())+
  #geom_vline(xintercept = 3.45, linetype="dotted", color = "black", size=1.2)+
   geom_segment(aes(x = 3.6, y = 0, xend = 3.6, yend = 0.95))+
  #geom_segment(aes(x = 0, y = 0.95, xend = 3.45, yend = 0.95))+
  geom_segment(aes(x = 4.25, y = 0.2, xend = 3.6, yend = 0),
                  arrow = arrow(length = unit(0.5, "cm")))+
  #facet_wrap(~Stage,ncol = 2)+
  stat_function(fun = test1,color="black",size=1)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))+mytheme3+
 annotate("text", x=1.4, y=1, size = 5, label ="paste(y == 1-exp(-0.81*x),~~R^2==0.96 )", parse=T)+
annotate("text", x=4.5, y=0.25, size = 5, label ="paste(LAIcrit==3.6)", parse=T)
  #ggsave("D:/R/Pictures/PAR/Regrowth.png", width=8, height=5  , dpi=500) 
```
###seedling crop
```{r,fig.height=5, fig.width=10}
test1 <- function(x) {1-exp(-0.71*x)}
stat_function(fun = test1)
 
ObsPL1%>%
   dplyr::filter(Stage=="Seedling")%>%
  ggplot(aes(x=Observed.x,y=Observed.y,color=ID,label=GrowthRotation))+theme_bw()+ylab("Franctional radiation interception")+xlab(bquote(bold('LAI ('*m^2~m^-2*')')))+
  geom_point(size=2)+
  facet_wrap(~Stage,ncol = 2)+
  stat_function(fun = test1,color="black",size=1)+mytheme3+theme(legend.title = element_blank())+
 annotate("text", x=1.5, y=1, size = 5, label ="paste(y == 1-exp(-0.76*x),~~R^2==0.90 )", parse=T)
  ggsave("D:/R/Pictures/PAR/Seedling.png", width=8, height=5  , dpi=500) 
```


#### Extinction_coef evaluation
```{r,fig.height=5, fig.width=10}
library(plyr)
Exc.K<-ObsPL1%>%
  mutate(Fra=1-Observed.y)%>%
  mutate(lnFI=log(Fra))

lm_eqn3 <- function(Exc.K){
  m <- lm(lnFI~Observed.x, Exc.K);
  eq <- substitute(italic(y) == Observed.x + lnFI %.% italic(Observed.x)*","~~italic(R)^2~"="~r2, 
                   list(Observed.x = format(coef(m)[1], digits = 2), 
                       lnFI = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}


eqs2 <- ddply(Exc.K,.(Stage),lm_eqn3)


Exc.K%>%
  ggplot(aes(x=Observed.x,y=lnFI,color=Name,label=GrowthRotation,shape=Stage))+geom_text()+theme_bw()+ylab("ln(I/IO)")+xlab(bquote(bold('LAI ('*m^2~m^-2*')')))+
  #geom_point(size=2)+
   geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
  facet_wrap(~Stage,ncol = 2)+
  mytheme3+
  geom_text(data = eqs2, aes(y =0, x = 3.5, label = V1), 
          color = 'black',  parse = TRUE)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
  detach(package:plyr)
```

```{r}
Exc.KS<-Exc.K%>%
  dplyr::filter(Stage=="Seedling")
Exc.KR<-Exc.K%>%
  dplyr::filter(Stage=="Regrowth")

##seedling analysis
x1=Exc.KS$Observed.x
y1=Exc.KS$lnFI
mod1<-lm(y1~x1)
summary(mod1)
m.e.s<-nls(Observed.y~1-I(exp(1)^(a*Observed.x)), data=Exc.KS,start=list(a=1), trace=T)
summary(m.e.s)$coefficients
plot(m.e.s)

#R2=1-RSS/TSS

RSS.P<-sum(residuals(m.e.s)^2)
TSS<-sum((Exc.KS$Observed.y-mean(Exc.KS$Observed.y))^2)
R2<-1-(RSS.P/TSS)

##regrowth analysis
x2=Exc.KR$Observed.x
y2=Exc.KR$lnFI
mod2<-lm(y2~x2)
summary(mod2)
m.e.r<-nls(Observed.y~1-I(exp(1)^(a*Observed.x)), data=Exc.KR,start=list(a=1), trace=T)
summary(m.e.r)$coefficients
plot(m.e.r)

RSS.P<-sum(residuals(m.e.r)^2)
TSS<-sum((Exc.KR$Observed.y-mean(Exc.KR$Observed.y))^2)
R2<-1-(RSS.P/TSS)


##seedling and regrowth analysis
x3=Exc.K$Observed.x
y3=Exc.K$lnFI
mod3<-lm(y3~x3)
summary(mod3)

Exc.K

x4=Exc.K$Observed.x
y4=Exc.K$Observed.y
m.e<-nls(y4~1-I(exp(1)^(a*x4)), data=Exc.K,start=list(a=1), trace=T)
summary(m.e)$coefficients
plot(m.e)
plot(y4~x4)

RSS.P<-sum(residuals(m.e)^2)
TSS<-sum((Exc.K$Observed.y-mean(Exc.K$Observed.y))^2)
R2<-1-(RSS.P/TSS)



```


####analysis
```{r}
ObsPLR<-ObsPL1%>%
  # dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="13")%>%
  # dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthSeason.x!="2")%>%
  # dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  dplyr::filter(Stage!="Seedling")
x=ObsPLR$Observed.x
y=ObsPLR$Observed.y

# mdl1 <- lm(y ~ x, data = ObsPLR)
# mdl2 <- lm(y ~ x + I(x^2), data = ObsPLR)
# mdl3 <- lm(y ~ x + I(x^2) + I(x^3), data = ObsPLR)
# mdl4 <- lm(y ~ I(x^2), data = ObsPLR)
# mdl5<-lm(y ~ poly(x, 2, raw=TRUE),data = ObsPLR )
mdl6<-lm(y~exp(-x),data = ObsPLR) 

# summary(mdl1)
# summary(mdl2)
# summary(mdl3)
# summary(mdl4)
# summary(mdl5)
summary(mdl6)


prd <- data.frame(x = seq(0.1, 7, by = 0.1))

result <- prd
# result$mdl1 <- predict(mdl1, newdata = prd)
# result$mdl2 <- predict(mdl2, newdata = prd)
# result$mdl3 <- predict(mdl3, newdata = prd)
# result$mdl4 <- predict(mdl4, newdata = prd)
# result$mdl5 <- predict(mdl5, newdata = prd)
result$mdl6 <- predict(mdl6, newdata = prd)
#df<-data.frame(x=c(0,1,2,3,4,5,6,7),y=c(0,0.55,0.80,0.91,0.96,0.98,0.99,0.99))
#df1<-data.frame(x=c(0,1,2,3,4,5,6,7),y=c(0,0.57,0.817,0.92,0.966,0.985,0.99,0.997))

result <-  melt(result, id.vars = "x", variable.name = "model",
                value.name = "fitted")
ggplot(result, aes(x = x, y = fitted)) +
  theme_bw() +
  facet_wrap(~Stage,ncol=2)+
  geom_point(data = ObsPLR, aes(x = x, y = y)) +ylab("Franctional radiation interception")+xlab("LAI")+
  #geom_line(data = df,aes(x=x,y=y),color="red",size=1)+
  #geom_line(data = df1,aes(x=x,y=y),color="blue",size=1)+
  geom_line(aes(colour = model), size = 1)+
  theme(legend.title=element_blank(),legend.position = "blank")+
  theme(axis.title.x=element_text(face="bold",colour= "black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```
```{r}
ObsPLR<-ObsPL1%>%
  # dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthRotation!="13")%>%
  # dplyr::filter(Name!="Iversen_121DefoliationLLFDFD5"|GrowthSeason.x!="2")%>%
  # dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  dplyr::filter(Stage=="Seedling")
x=ObsPLR$Observed.x
y=ObsPLR$Observed.y

# mdl1 <- lm(y ~ x, data = ObsPLR)
# mdl2 <- lm(y ~ x + I(x^2), data = ObsPLR)
# mdl3 <- lm(y ~ x + I(x^2) + I(x^3), data = ObsPLR)
# mdl4 <- lm(y ~ I(x^2), data = ObsPLR)
# mdl5<-lm(y ~ poly(x, 2, raw=TRUE),data = ObsPLR )
mdl6<-lm(y~exp(-x),data = ObsPLR) 

# summary(mdl1)
# summary(mdl2)
# summary(mdl3)
# summary(mdl4)
# summary(mdl5)
summary(mdl6)


prd <- data.frame(x = seq(0.1, 5, by = 0.1))

result <- prd
# result$mdl1 <- predict(mdl1, newdata = prd)
# result$mdl2 <- predict(mdl2, newdata = prd)
# result$mdl3 <- predict(mdl3, newdata = prd)
# result$mdl4 <- predict(mdl4, newdata = prd)
# result$mdl5 <- predict(mdl5, newdata = prd)
result$mdl6 <- predict(mdl6, newdata = prd)

result <-  melt(result, id.vars = "x", variable.name = "model",
                value.name = "fitted")
ggplot(result, aes(x = x, y = fitted)) +
  theme_bw() +
  facet_wrap(~Stage,ncol=2)+
  geom_point(data = ObsPLR, aes(x = x, y = y)) +ylab("Franctional radiation interception")+xlab("LAI")+
  geom_line(aes(colour = model), size = 1)+
  theme(legend.title=element_blank(),legend.position = "blank")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```
###PAR and acculmated PARi
##PAR
###dataframe format


```{r}
TtA1<-TtA%>%
  dplyr::filter(Tbb==1)%>%
  dplyr::select(year,day,rain,maxt,mint,mean,radn,wind,vp,Pp,Tbb,TTbroken,TTfick,TTbeta,GrowthSeason,Rotation, Clock.Today,ExpUnitCode,Tt_beta_sum,Tt_fick_sum,Tt_broken_sum,Ppm,Tmean)
  
obsA1<-obsA%>%
  dplyr::filter(Variable=="LAI")%>%
  dplyr::select(Clock.Today, Name, Collection,Water,Defoliation,SowingDate,FD, Experiment,Variable,VariableUnits,Observed,StdDEV,ExpUnitCode,StartDate,MidDate,FinishDate,ExperimentID,TreatmentID,ID)

ObsLAI.Raw <-merge(obsA1,TtA1,by=c("ExpUnitCode"))%>%
  #mutate(fPAR=as.factor(ifelse(Clock.Today.x==Clock.Today.y,Observed,"NA")))%>%
 # mutate(fPAR=as.factor(ifelse(Clock.Today.y==StartDate,0.1,paste0(fPAR))))%>%
  #mutate(StdDEV1=as.factor(ifelse(Clock.Today.x==Clock.Today.y,StdDEV,"NA")))%>%
  dplyr::select(-Clock.Today.x,-Observed,-StdDEV)%>%
  unique()
#write.csv(ObsPAR.Raw,"D:/R/ObsPAR.Raw.csv", row.names = FALSE)
write.csv(ObsLAI.Raw,"D:/R/ObsLAI.Raw.csv", row.names = FALSE)
```
###fPAR interpolate for each rotation

```{r}
upDir <- "D:/R/"
obsData <- "D:/R/"

ObsPAR.Raw1<- read.table(paste0(obsData, "ObsPAR.Raw.txt"),
               header = TRUE)%>%
  unique()

UniExp <- unique(ObsPAR.Raw1$ExpUnitCode)

fPAR.df <- data.frame()
  
for(i in 1:length(UniExp))
{
  
  ObsfPAR<-ObsPAR.Raw1%>%
   filter(ExpUnitCode==UniExp[i])%>%
  mutate(Clock.Today=dmy(Clock.Today.y))
  
 
 fPAR.data<-ObsfPAR%>%
  mutate(fPAR1=approx(Clock.Today, fPAR, xout =Clock.Today, 
         method="linear", 
         rule = 2)$y)##interpolate function 
  

 fPAR.df<- rbind( fPAR.df, fPAR.data)

}

summary(fPAR.df)
fPAR.df
write.csv(fPAR.df,"D:/R/fPAR.df.csv", row.names = FALSE)
```
###calculate PARi for every day
```{r}
# PARi<-fPAR.df%>%
#   #dplyr::select(-fPAR)%>%
#   unique()%>%
#   mutate(PARi=radn*fPAR1)

```
###Accumlated PAR for every rotation
```{r}

UniExp <- unique(fPAR.df$ExpUnitCode)

PARi.df <- data.frame()
  
for(i in 1:length(UniExp))
{
  
  ObsPARi<-fPAR.df%>%
    
   filter(ExpUnitCode==UniExp[i])%>%
     mutate(PARi=radn*fPAR1)%>% 
   dplyr::select(-fPAR,-StdDEV1)%>%
    unique()
  
 
 PARi.data<-ObsPARi%>%
  mutate( PARi.sum = cumsum(PARi))##accmulated function
  

 PARi.df<- rbind( PARi.df, PARi.data)

}

summary(PARi.df)
PARi.df
write.csv(PARi.df,"D:/R/PARi.df.csv", row.names = FALSE)
```
###calculated RUE value
####Join yield and PARi table together
```{r}
PARi.df1<-PARi.df%>%
  mutate(Clock.Today=dmy(Clock.Today.y))%>%
  dplyr::select(ExpUnitCode,Name,Clock.Today,fPAR1,PARi,PARi.sum,GrowthSeason,Rotation)

obsTDM<-ObsL.Raw%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))%>%
  dplyr::filter(Water.x=="irr")%>%
  dplyr::filter(Defoliation.x=="LL")%>%
  dplyr::filter(FD.x=="FD5")%>%
  dplyr::filter(Tbb==1)%>%
  dplyr::filter(Variable=="shootbiomass"|Variable=="RootWt")

  
RUE.RAW<-merge(obsTDM,PARi.df1,by=c("Clock.Today","Name","ExpUnitCode"))
```

###check the intepolate function
```{r,fig.height=5, fig.width=8}
PARi.df2<-PARi.df1%>%
  dplyr::filter(Name=="Iversen_8Waterirr")
  
PARi.df2%>%
  ggplot(aes(x=Clock.Today, y=fPAR1))+geom_point(size=2)+theme_bw()+xlab("Date")+ylab("Fractional intercepted radiation")+
  #geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
 facet_grid(GrowthSeason~Rotation)+ggtitle("Iversen_8Waterirr")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
```{r,fig.height=5, fig.width=8}
PARi.df3<-PARi.df1%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
  
PARi.df3%>%
  ggplot(aes(x=Clock.Today, y=fPAR1))+geom_point(size=2)+theme_bw()+xlab("Date")+ylab("Fractional intercepted radiation")+
  #geom_smooth(method = "lm", se = TRUE,linetype=1 , colour="black")+
 facet_grid(GrowthSeason~Rotation)+ggtitle("Iversen_91DefoliationLL")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
