---
title: "R Notebook"
output: html_notebook
---
```{r}
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)

```
# ### load obs data
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsADF <- read.table(paste0(obsData, "Defoliation.txt"),
                   header = TRUE)
obsAD<- obsADF %>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(FD=="FD5")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today))%>%
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
 mutate(Rotation2=as.factor(paste0("R",Rotation)))%>%
   dplyr::filter(Variable=="NodeNumber")
 obsAD
```
```{r}
upDir <- "D:/R/"
obsData <- "D:/R/TtAll/"

Tt<- read.table(paste0(obsData, "df.all1.txt"),
               header = TRUE)
TtA <- Tt %>% mutate(Clock.Today=dmy(Clock.Today), ExpUnitCode=as.factor(ExpName))%>%
  dplyr::filter(Tb==1)

TtA1<-TtA%>%
  dplyr::filter(ExpUnitCode=="Iversen_92DefoliationLSGs_1Rt_8")

obsD <-merge(obsAD,TtA,by=c("Clock.Today","ExpUnitCode")) %>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))%>%
  dplyr::filter(Variable=="NodeNumber")
  summary(obsD)
  obsD
  
```

```{r}
mytheme1<-theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14,angle=90, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

mytheme3<-theme(
     legend.title = element_text(colour="black", size=14, face="bold"),
     legend.text = element_text(colour="black", size = 14,face="plain"),
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14),
    legend.position = "right", legend.box = "vertical")
```
###LS
```{r,fig.height=6, fig.width=8}
  obsN0<-obsD%>%
  dplyr::filter(ID=="E3ILS")
  obsN0$Rotation2<- factor(obsN0$Rotation2,
                          levels=c("R1", "R2", "R3", "R4","R5","R6","R7","R8","R9","R10"))
  obsN0%>%  
  ggplot(aes(x=Tt_broken_sum, y=Observed))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd) ")+ylab("Node number")+ggtitle(paste0("E1ILS","(Iversen_91DefoliationLS)"))  +
  scale_x_continuous(breaks = seq(0, 550, by =200), limits=c(0,450))+
  scale_y_continuous(breaks = seq(0, 18, by =6), limits=c(0,16))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason2~Rotation2)+mytheme1
#ggsave("D:/R/Pictures/C5/Node/Iversen_91DefoliationLSnode.png", width=8, height=6, dpi=500)

```
###SL
```{r,fig.height=6, fig.width=8}
  obsN1<-obsD%>%
  dplyr::filter(ID=="E3ISL")
  obsN1$Rotation2<- factor(obsN1$Rotation2, levels=c("R1", "R2", "R3", "R4", "R5","R6", "R7","R8","R9","R10"))
  obsN1%>%  
  ggplot(aes(x=Tt_broken_sum, y=Observed))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd) ")+ylab("Node number")+ggtitle(paste0("E1ILS","(Iversen_91DefoliationSL)"))  +
  scale_x_continuous(breaks = seq(0, 550, by =200), limits=c(0,450))+
  scale_y_continuous(breaks = seq(0, 18, by =6), limits=c(0,16))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason2~Rotation2)+mytheme1
#ggsave("D:/R/Pictures/C5/Node/Iversen_91DefoliationSLnode.png", width=8, height=6, dpi=500)

```
###SS
```{r,fig.height=6, fig.width=8}
  obsN2<-obsD%>%
  dplyr::filter(ID=="E3ISS")
  obsN2$Rotation2<- factor(obsN2$Rotation2, levels=c("R1", "R2", "R3", "R4", "R5","R6", "R7","R8","R9","R10"))
  obsN2%>%  
  ggplot(aes(x=Tt_broken_sum, y=Observed))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd) ")+ylab("Node number")+ggtitle(paste0("E3ISS","(Iversen_91DefoliationSS)"))  +
  scale_x_continuous(breaks = seq(0, 500, by =200), limits=c(0,500))+
  scale_y_continuous(breaks = seq(0, 18, by =6), limits=c(0,16))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason2~Rotation2)+mytheme1
#ggsave("D:/R/Pictures/C5/Node/Iversen_91DefoliationSSnode.png", width=8, height=6, dpi=500)

```

###SS
```{r,fig.height=6, fig.width=8}
  obsN3<-obsD%>%
  dplyr::filter(ID=="E5ISSF5")
  obsN3$Rotation2<- factor(obsN3$Rotation2, levels=c("R1", "R2", "R3", "R4", "R5","R6", "R7","R8","R9","R10"))
  obsN3%>%  
  ggplot(aes(x=Tt_broken_sum, y=Observed))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd) ")+ylab("Node number")+ggtitle(paste0("E5ISSF5","(Iversen_121DefoliationSSFDFD5)"))  +
  scale_x_continuous(breaks = seq(0, 550, by =200), limits=c(0,500))+
  scale_y_continuous(breaks = seq(0, 18, by =6), limits=c(0,16))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason2~Rotation2)+mytheme1
#ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationSSFD5node.png", width=8, height=6, dpi=500)

```
###phyllochron

```{r}
 phyllochron <- obsD%>%
  dplyr::filter(Defoliation.x!="HH")%>%
  mutate(GrowthSeason=as.factor(GrowthSeason.x),Rotation=as.factor(Rotation.x))%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason,Rotation)))%>%
  group_by(Name,GrowthSeason,Rotation,Tmean,Ppm,Tb,ID,GrowthRotation) %>%
    do(mod = lm(Tt_broken_sum~Observed,data=.))%>%
  mutate(PhyollchronSS= summary(mod)$coeff[2])%>%
  dplyr::select(-mod)
  
```

#load Rotation and Growth season
```{r,fig.height=4, fig.width=8}
library(plyr)
phyll <- "D:\\R\\"
StartGrazing <- read.table(paste0(phyll, "ExperimentList.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(GrowthRotation= as.factor(paste0(GrowthSeason,Rotation)))
PhyPp1<- merge(StartGrazing1,phyllochron, by=c("Name","GrowthRotation"))%>% filter(GrowthRotation!="29")%>%
  dplyr::filter(ID!="E5ISSF5"|GrowthRotation!="41")%>%
  dplyr::filter(ID!="E5ISSF5"|GrowthRotation!="42")

lm_eqn1 <- function( PhyPp1){
  m <- lm(PhyollchronSS~Ppm ,PhyPp1);
  eq <- substitute(italic(y) == Ppm +PhyollchronSS %.% italic(Ppm)*","~~italic(R)^2~"="~r2, 
                   list(Ppm = format(coef(m)[1], digits = 2), 
                        PhyollchronSS= format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}


eqs <- ddply(PhyPp1,.(Trend,Stage),lm_eqn1)
#df2 <- data.frame(eq = unclass(eqns), Collection = as.numeric(names(eqns)))
#ylab(bquote(bold('LEAR ('*m^2~m^-2~'°Cd'^-1*')')))

PhyPp1%>%
  filter(GrowthRotation!="29")%>%
  dplyr::filter(ID!="E5ISSF5"|GrowthRotation!="41")%>%
  dplyr::filter(ID!="E5ISSF5"|GrowthRotation!="42")%>%
  ggplot(aes(x=Ppm, y=PhyollchronSS,colour=factor(ID),label=GrowthRotation))+geom_text()+
  theme_bw()+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Mean photoperiod (h)")+ylab(bquote(bold('Phyllochron ('*'°Cd'~'main node'^-1*')')))+
  geom_text(data = eqs, aes(x =13.5, y = 81, label = V1), 
          color = 'black',  parse = TRUE, size=5)+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey")+
  facet_wrap(~Trend, ncol = 2)+
   scale_y_continuous(breaks = seq(0, 70, by =20), limits=c(0,81))+
  mytheme3+theme(legend.title = element_blank())
 #ggsave("D:/R/Pictures/C5/Node/phyllo.png", width=8, height=4, dpi=500)
   detach(package:plyr)
```

```{r,fig.height=4, fig.width=6}
phyllochron%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason,Rotation)))%>%
  filter(GrowthRotation!="29")%>%
  ggplot(aes(x=Ppm, y=PhyollchronSS,colour=factor(ID),label=GrowthRotation))+geom_text()+
  #geom_point(size=2)+
  theme_bw()+xlab("Photoperiod")+ylab("Phyllochron")+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 mytheme3+
   theme(legend.title=element_blank(),legend.position = "blank")
 
```


###HH
```{r,fig.height=6, fig.width=8}
  obsN4<-obsD%>%
  dplyr::filter(ID=="E5IHHF5")
  obsN4$Rotation2<- factor(obsN4$Rotation2, levels=c("R1", "R2", "R3", "R4", "R5","R6", "R7","R8","R9","R10"))
  obsN4%>%  
  ggplot(aes(x=Tt_broken_sum, y=Observed))+geom_point(size=2)+theme_bw()+xlab("Thermal time (°Cd) ")+ylab("Node number")+ggtitle(paste0("E5IHHF5","(Iversen_121DefoliationHHFDFD5)"))  +
  scale_x_continuous(breaks = seq(0, 1000, by =400), limits=c(0,1000))+
  scale_y_continuous(breaks = seq(0, 20, by =6), limits=c(0,25))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason2~Rotation2)+mytheme1
#ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationHHFD5node11.png", width=8, height=6, dpi=500)

```

###Join with the flowering data

```{r}
upDir <- "D:/R/"
obsData <- "D:/R/"

flowering <- read.table(paste0(obsData, "Flowering.txt"),
                   header = TRUE)
flower <- flowering%>%
  mutate(StartDate=dmy(StartDate),BVDate=dmy(BVDate),FloDate=dmy(FloDate))
  

mergeHH<-merge(obsN4,flower,by=c("Name","ID","StartDate"))%>%
   mutate(Dev=ifelse(Clock.Today<=BVDate,"Veg","Repro"))
   

```
###Nodenumber and Phyllochron
```{r,fig.height=6, fig.width=10}
mergeHH_Veg<-mergeHH%>%
  dplyr::filter(Dev=="Veg")%>%
  dplyr::filter(Variable=="NodeNumber")
mergeHH_Veg%>%  
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd)")+ylab("Node number")+ggtitle(paste0("E5IHHF5","(Iversen_121DefoliationHHFD5)"))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason.x~Rotation.x)+
  scale_x_continuous(breaks = seq(0, 1000, by =400), limits=c(0,1000))+
  scale_y_continuous(breaks = seq(0, 20, by =6), limits=c(0,25))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason2~Rotation2)+mytheme1
#ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationHHFD5node.png", width=8, height=6, dpi=500)
  
```

```{r}
 mergeHH_V <- mergeHH_Veg %>%
  mutate(GrowthSeason=as.factor(GrowthSeason.x),Rotation=as.factor(Rotation.x))%>%
  group_by(Name,GrowthSeason,Rotation,Tmean,Ppm,Tb) %>%
    do(mod = lm(Tt_broken_sum~Observed,data=.))%>%
  mutate(Veg = summary(mod)$coeff[2])%>%
  dplyr::select(-mod)
```


```{r,fig.height=6, fig.width=10}
mergeHH_Repro<-mergeHH%>%
  dplyr::filter(Dev=="Repro")%>%
  dplyr::filter(Variable=="NodeNumber")
mergeHH_Repro%>%
  ggplot(aes(x=Tt_broken_sum, y=Observed), colour=factor(Name))+geom_point(size=2)+theme_bw()+xlab("Thermal time(°Cd)")+ylab("Node number")+ggtitle(paste0("E5IHHF5","(Iversen_121DefoliationHHFD5)"))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason2~Rotation2)+
  scale_x_continuous(breaks = seq(0, 1000, by =400), limits=c(0,900))+
  scale_y_continuous(breaks = seq(10, 26, by =6), limits=c(10,25))+
 mytheme3+
   theme(legend.title=element_blank(),legend.position = "blank")
#ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationHHFD5node12.png", width=8, height=6, dpi=500)
```

```{r}
 mergeHH_R <- mergeHH_Repro %>%
  mutate(GrowthSeason=as.factor(GrowthSeason.x),Rotation=as.factor(Rotation.x))%>%
  #dplyr::filter(GrowthSeason!="2"|Rotation!="1") %>%
  group_by(Name,GrowthSeason,Rotation,Tmean,Ppm,Tb) %>%
    do(mod = lm(Tt_broken_sum~Observed,data=.))%>%
  mutate(Reg= summary(mod)$coeff[2])%>%
  dplyr::select(-mod)
  
mergePhy<-merge(mergeHH_V, mergeHH_R,by=c("Name","GrowthSeason","Rotation","Tmean","Ppm","Tb"))%>%
  dplyr::select(Name,GrowthSeason,Rotation,Tmean, Ppm,Tb, Veg,Reg) %>%
  tidyr::gather("Variable","Phyllo",Veg:Reg)
  
```

```{r,fig.height=4, fig.width=6}
mergePhy$Variable<-factor(mergePhy$Variable, levels = c("Veg","Reg"))


mergePhy%>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason,Rotation)))%>%
  filter(GrowthRotation!="21")%>%
  filter(GrowthRotation!="33")%>%
  ggplot(aes(x=Ppm, y=Phyllo,colour=factor(Name),label=GrowthRotation))+geom_text()+
  #geom_point(size=2)+
  theme_bw()+xlab("Photoperiod (h)")+ylab(bquote(bold('Phyllochron ('*'°Cd'~'main node'^-1*')')))+ggtitle("E5IHHF5(Iverson_121DefoliationHHFDFD5)")+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_wrap(~Variable,ncol = 2)+mytheme3+
   theme(legend.title=element_blank(),legend.position = "blank")

#ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationHHFD5phyllochron.png", width=8, height=4, dpi=500)
```


## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r, round(r2*100,1))

  return(out)

}
```

## Test stats functions used

```{r}
s <- c(4231.972,3935.604,3779.652,3627.687,3363.499,3230.566,2868.114,2868.827)
m <- c(4987.66,5636.09,4754.06,4114.53,4141.72,3704.06,5142.19,4762.03)

x <- gauchStats(s,m)

tempDf <- data.frame(statName=c("SB","NU","LC","r_MSD","R2"), statValue=x)
# kable(tempDf, digits= 2)
tempDf2 <- data.frame(Predicted=s, Observed=m)

x <- tempDf2 %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>% 
  t() 

df <- data.frame(stat = row.names(x),statvalue = x[,1])

df %>%
  kable(format = "markdown")
```
## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneValidation.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
summary(df)
head(df) # simulation results
```
# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"_Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)

# myDb %>%
#   dplyr::select(Name) %>%
#   unique()

```
## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,SWC,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  tidyr::gather("Variable","Predicted",LAI:NodeNumber) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)
summary(simD)



mergedf<-merge(obsD,simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)
mergedf

```

## Node number
#Time series
## obs Vs Pre for each experiment
## 2002-2004
```{r,fig.height=4, fig.width=8}

obsDNode1<-obsD%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLS")
  
   
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Variable=="NodeNumber")%>%
   dplyr::filter(Clock.Today>"2002-06-01")%>%
   dplyr::filter(Name=="Iversen_91DefoliationLS")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~ID,ncol = 2)+
 geom_point(data=obsDNode1, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))+
  annotate("text", x=ymd_hms("2003-07-24 12:00:00"), y=17, size = 5, label ="paste(R_RMSD == 20.9,'%')", parse=T)
 #ggsave("D:/R/Pictures/C5/Node/Iversen_91DefoliationLSnodenumber1.png", width=8, height=4, dpi=500)

```
## SL
```{r,fig.height=4, fig.width=8}

obsDNode1<-obsD%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_91DefoliationSL")
  
   
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Variable=="NodeNumber")%>%
   dplyr::filter(Clock.Today>"2002-06-01")%>%
   dplyr::filter(Name=="Iversen_91DefoliationSL")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~ID,ncol = 2)+
 geom_point(data=obsDNode1, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))+
  annotate("text", x=ymd_hms("2003-07-24 12:00:00"), y=15, size = 5, label ="paste(R_RMSD == 20.8,'%')", parse=T)
 #ggsave("D:/R/Pictures/C5/Node/Iversen_91DefoliationSL1.png", width=8, height=4, dpi=500)

```

## SS
```{r,fig.height=4, fig.width=8}

obsDNode1<-obsD%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_91DefoliationSS")
  
   
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Variable=="NodeNumber")%>%
   dplyr::filter(Clock.Today>"2002-06-01")%>%
   dplyr::filter(Name=="Iversen_91DefoliationSS")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~ID,ncol = 2)+
 geom_point(data=obsDNode1, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))+
  annotate("text", x=ymd_hms("2003-07-24 12:00:00"), y=13, size = 5, label ="paste(R_RMSD == 30.5,'%')", parse=T)
 #ggsave("D:/R/Pictures/C5/Node/Iversen_91DefoliationSS1.png", width=8, height=4, dpi=500)

```
##2014-2018
```{r,  fig.height=4, fig.width=8}
obsD4<-obsD%>% 
  dplyr::filter(Collection=="2014_2018")%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD5")

simD4a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD5")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD4b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD5")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD4<-rbind(simD4a,simD4b)
  
  
str(simD4)
simD4%>%
  dplyr::filter(Clock.Today>"2015-01-31")%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 1)+
  geom_point(data=obsD4, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))+
   annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=12, size = 5, label ="paste(R_RMSD == 41.6,'%')", parse=T)
  # ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationLLFDFD5nodenumber1.png", width=8, height=4, dpi=500)
  
  


```
##2014-2018
```{r,  fig.height=4, fig.width=8}
obsD4<-obsD%>% 
  dplyr::filter(Collection=="2014_2018")%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD5")

simD4a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD5")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD4b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD5")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD4<-rbind(simD4a,simD4b)
  
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 1)+
  geom_point(data=obsD4, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))+
   annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=25, size = 5, label ="paste(R_RMSD == 39.7,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationHHFDFD5nodenumber1.png", width=8, height=4, dpi=500)
  
  


```

# Statistic and Graph
```{r,fig.height=6, fig.width=8}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
  ggplot(aes(x=Observed, y= Predicted, colour= factor(Name))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_wrap(~ID, ncol = 3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))


   #ggsave("D:/R/Pictures/C5/Node/nodenumber1.png", width=8, height=6, dpi=500)
```

## RMSE

```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "NodeNumber") %>% 
  group_by(ID) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),2),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```






