---
title: "Yield for Defoliation treatments"
output: html_notebook
---
```{r}
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)

```
# ### load obs data
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsSRF <- read.table(paste0(obsData, "Defoliation.txt"),
                   header = TRUE)
obsSRR<- obsSRF %>%
  dplyr::filter(FD=="FD5")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today))%>%
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
 mutate(Rotation2=as.factor(paste0("R",Rotation)))%>%
   dplyr::filter(Variable==c("RootWt"))

obsSRS<- obsSRF %>%
  dplyr::filter(FD=="FD5")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today))%>%
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
 mutate(Rotation2=as.factor(paste0("R",Rotation)))%>%
   dplyr::filter(Variable==c("shootbiomass"))


 obsSR<-rbind(obsSRR,obsSRS)
```

```{r}
upDir <- "D:/R/"
obsData <- "D:/R/TtAll/"

Tt<- read.table(paste0(obsData, "df.all1.txt"),
               header = TRUE)
TtA <- Tt %>% mutate(Clock.Today=dmy(Clock.Today), ExpUnitCode=as.factor(ExpName))%>%
  dplyr::filter(Tb==1)

obsSRD <-merge(obsSR,TtA,by=c("Clock.Today","ExpUnitCode")) %>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))

  summary(obsSRD)
  obsSRD
  
```

```{r}
mytheme1<-theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14,angle=90, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

mytheme3<-theme(
     legend.title = element_text(colour="black", size=14, face="bold"),
     legend.text = element_text(colour="black", size = 14,face="plain"),
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14),
    legend.position = "right", legend.box = "vertical")
```

```{r,fig.height=6, fig.width=8}
obsSRD$Variable<- factor(obsSRD$Variable, levels=c("shootbiomass","RootWt"))
obsSRD%>%
  dplyr::filter(ID=="E3ILS")%>%
 ggplot(aes(x=Clock.Today,y=Observed,colour=ID))+theme_bw()+
 facet_wrap(~Variable,ncol = 1)+
 geom_point(size=2)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("RootWt (kg/ha)")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
```

```{r,fig.height=6, fig.width=8}
obsSRD%>%
  dplyr::filter(ID=="E3ILS")%>%
 ggplot(aes(x=Tt_broken_sum,y=Observed,colour=ID))+theme_bw()+
 facet_grid(GrowthSeason2~Rotation2)+
 geom_point(size=2)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("RootWt (kg/ha)")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
```


```{r,fig.height=6, fig.width=8}
obsSRD%>%
  dplyr::filter(ID=="E3ISS")%>%
 ggplot(aes(x=Tt_broken_sum,y=Observed,colour=ID))+theme_bw()+
 facet_grid(GrowthSeason2~Rotation2)+
 geom_point(size=2)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("RootWt (kg/ha)")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
```

```{r,fig.height=6, fig.width=8}
obsSRD%>%
  dplyr::filter(ID=="E3ISL")%>%
 ggplot(aes(x=Tt_broken_sum,y=Observed,colour=ID))+theme_bw()+
 facet_grid(GrowthSeason2~Rotation2)+
 geom_point(size=2)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("RootWt (kg/ha)")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
```
```{r}
obsSRD%>%
  dplyr::filter(ID=="E5ISSF5")%>%
 ggplot(aes(x=Tt_broken_sum,y=Observed,colour=ID))+theme_bw()+
 facet_grid(GrowthSeason2~Rotation2)+
 geom_point(size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("RootWt (kg/ha)")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))


```
```{r}
obsSRD%>%
  dplyr::filter(ID=="E5IHHF5")%>%
 ggplot(aes(x=Tt_broken_sum,y=Observed,colour=ID))+theme_bw()+
 facet_grid(GrowthSeason2~Rotation2)+
 geom_point(size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("RootWt (kg/ha)")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))


```


```{r}
obsSRD%>%
  dplyr::filter(Collection=="2014_2018")%>%
 ggplot(aes(x=Clock.Today,y=Observed,colour=ID))+theme_bw()+
 facet_wrap(~ID,ncol = 2)+
 geom_point(size=2)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("RootWt (kg/ha)")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))


```

## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r, round(r2*100,1))

  return(out)

}
```

## Test stats functions used

```{r}
s <- c(4231.972,3935.604,3779.652,3627.687,3363.499,3230.566,2868.114,2868.827)
m <- c(4987.66,5636.09,4754.06,4114.53,4141.72,3704.06,5142.19,4762.03)


x <- gauchStats(s,m)

tempDf <- data.frame(statName=c("SB","NU","LC","r_MSD","R2"), statValue=x)
# kable(tempDf, digits= 2)
tempDf2 <- data.frame(Predicted=s, Observed=m)

x <- tempDf2 %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>% 
  t() 

df <- data.frame(stat = row.names(x),statvalue = x[,1])

df %>%
  kable(format = "markdown")
```

## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneValidation.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
summary(df)
head(df) # simulation results
```

# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"_Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)

# myDb %>%
#   dplyr::select(Name) %>%
#   unique()

```

## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,SWC,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  tidyr::gather("Variable","Predicted",LAI:NodeNumber) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)
summary(simD)



mergedf<-merge( obsSRD,simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)
mergedf

```

## Node number
#Time series
## obs Vs Pre for each experiment
## 2002-2004
```{r,fig.height=6, fig.width=8}
obsRoot<- obsSRD%>%
  dplyr::filter(Name=="Iversen_91DefoliationLS")

obsRoot$Variable<- factor(obsRoot$Variable, levels=c("shootbiomass","RootWt"))  
   
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
   dplyr::filter(Clock.Today>"2002-06-01")%>%
   dplyr::filter(Name=="Iversen_91DefoliationLS")
  simD1$Variable<- factor( simD1$Variable, levels=c("shootbiomass","RootWt"))  
   
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_grid(Variable~ID)+ggtitle(paste0("E3ILS","(Iversen_91DefoliationLS)"))+
 geom_point(data=obsRoot, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Biomass (kg/ha)")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
  #annotate("text", x=ymd_hms("2003-07-24 12:00:00"), y=17, size = 5, label ="paste(R_RMSD == 20.9,'%')", parse=T)
 #ggsave("D:/R/Pictures/C5/Node/Iversen_91DefoliationLSnodenumber1.png", width=8, height=4, dpi=500)
  #ggsave("D:/R/Pictures/C5/Yield//Iversen_91DefoliationLSyield.png", width=8, height=8, dpi=500)
```
```{r,fig.height=4, fig.width=8}

# obsShoot<- obsSRD%>%
#   dplyr::filter(Variable=="shootbiomass")%>%
#   dplyr::filter(Name=="Iversen_91DefoliationLS")
#   
#  simD1<-simD%>%
#    mutate(Clock.Today = ymd_hms(Clock.Today))%>%
#    dplyr::filter(Variable=="shootbiomass")%>%
#    dplyr::filter(Clock.Today>"2002-06-01")%>%
#    dplyr::filter(Name=="Iversen_91DefoliationLS")
#  str(simD1)
#  simD1%>%
#  ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
#  facet_wrap(~ID,ncol = 2)+
#  geom_point(data=obsShoot, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
#  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("RootWt (kg/ha)")+
#     #remove grid lines 
#   theme(
#      panel.spacing=unit(.01, "lines"),
#      panel.border = element_rect(colour = "black",size=1), 
#      panel.grid.major = element_blank(),
#      panel.grid.minor = element_blank(),
#      axis.line = element_line(colour = "black",size = 1),
#      axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
#      axis.text.y = element_text(face = "plain", color = "black", size = 14),
#      axis.title.x=element_text(face="bold",colour="black",size = 14),
#      axis.title.y=element_text(face="bold",colour="black",size = 14),
#      strip.background = element_rect(colour = "black", fill = "white",size=1),
#      strip.text.x = element_text(size=14, angle=0, face = "plain"), 
#      strip.text.y = element_text(size=14, face="plain"),
#      legend.title = element_text(colour="black", size=14, face="bold"),
#      axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
  #annotate("text", x=ymd_hms("2003-07-24 12:00:00"), y=17, size = 5, label ="paste(R_RMSD == 20.9,'%')", parse=T)
 #ggsave("D:/R/Pictures/C5/Node/Iversen_91DefoliationLSnodenumber1.png", width=8, height=4, dpi=500)

```
## SL
```{r,fig.height=4, fig.width=8}

obsRoot1<- obsSRD%>%
  dplyr::filter(Name=="Iversen_91DefoliationSL")
  
   
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
   dplyr::filter(Clock.Today>"2002-06-01")%>%
   dplyr::filter(Name=="Iversen_91DefoliationSL")
 str(simD1)
  simD1$Variable<- factor(simD1$Variable, levels=c("shootbiomass","RootWt"))  
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_grid(Variable~ID)+ggtitle(paste0("E3ISL","(Iversen_91DefoliationSL)"))+
 geom_point(data=obsRoot1, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Biomass (kg/ha)")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
  #annotate("text", x=ymd_hms("2003-07-24 12:00:00"), y=15, size = 5, label ="paste(R_RMSD == 20.8,'%')", parse=T)
 #ggsave("D:/R/Pictures/C5/Node/Iversen_91DefoliationSL1.png", width=8, height=4, dpi=500)
ggsave("D:/R/Pictures/C5/Yield/Iversen_91DefoliationSLyield.png", width=8, height=8, dpi=500)
```
## SS
```{r,fig.height=4, fig.width=8}

obsRoot2<- obsSRD%>%
  dplyr::filter(Name=="Iversen_91DefoliationSS")
  
   
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
   dplyr::filter(Clock.Today>"2002-06-01")%>%
   dplyr::filter(Name=="Iversen_91DefoliationSS")
 str(simD1)
 simD1$Variable<- factor(simD1$Variable, levels=c("shootbiomass","RootWt"))
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_grid(Variable~ID)+ggtitle(paste0("E3ISS","(Iversen_91DefoliationSS)"))+
 geom_point(data=obsRoot2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Biomass (kg/ha)")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
 # annotate("text", x=ymd_hms("2003-07-24 12:00:00"), y=13, size = 5, label ="paste(R_RMSD == 30.5,'%')", parse=T)
 #ggsave("D:/R/Pictures/C5/Node/Iversen_91DefoliationSS1.png", width=8, height=4, dpi=500)
ggsave("D:/R/Pictures/C5/Yield/Iversen_91DefoliationSSyield.png", width=8, height=8, dpi=500)
```

##2014-2018
```{r,  fig.height=4, fig.width=8}
obsRoot3<- obsSRD%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD5")

simD4a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD5")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD4b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD5")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD4<-rbind(simD4a,simD4b)
simD4$Variable<- factor(simD4$Variable, levels=c("shootbiomass","RootWt"))  
  
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(Variable~ID)+ggtitle(paste0("E5ISSFD5","(Iversen_121DefoliationSSFDFD5)"))+
  geom_point(data=obsRoot3, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Biomass (kg/ha)")+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=18, size = 5, label ="paste(R_RMSD == 64.5,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationLLFDFD5nodenumber1.png", width=8, height=4, dpi=500)
ggsave("D:/R/Pictures/C5/Yield/Iversen_121DefoliationSSFDFD5yield.png", width=8, height=8, dpi=500)
```

##2014-2018
```{r,  fig.height=4, fig.width=8}
obsRoot4<- obsSRD%>%
  #dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD5")

simD4a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD5")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD4b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD5")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD4<-rbind(simD4a,simD4b)
simD4$Variable<- factor(simD4$Variable, levels=c("shootbiomass","RootWt"))  
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(Variable~ID)+ggtitle(paste0("E5IHHFD5","(Iversen_121DefoliationHHFDFD5)"))+
  geom_point(data=obsRoot4, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Biomass (kg/ha)")+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=25, size = 5, label ="paste(R_RMSD == 39.7,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationHHFDFD5nodenumber1.png", width=8, height=4, dpi=500)
ggsave("D:/R/Pictures/C5/Yield/Iversen_121DefoliationHHFDFD5yield.png", width=8, height=8, dpi=500)
```
# Statistic and Graph
```{r,fig.height=6, fig.width=8}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(Name))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  #ggtitle("Node Number")+
  facet_wrap(~ID, ncol = 3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))


   #ggsave("D:/R/Pictures/C5/Node/nodenumber1.png", width=8, height=6, dpi=500)
```
## RMSE

```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "shootbiomass") %>% 
  group_by(ID) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),2),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```
####RUE calculation.
```{r}
PAR <- "D:\\R\\"
PARiD.df <- read.table(paste0(PAR, "PARiD.df.txt"), 
                      header = TRUE)


PARiD.df1<-PARiD.df%>%
  mutate(Clock.Today=dmy(Clock.Today.y))%>%
  dplyr::select(ExpUnitCode,Name,Clock.Today,fPAR1,PARi,PARi.sum)

obsDSRR<-obsSRD%>%
  filter(Variable=="RootWt")%>%
  mutate(RootWt=Observed)
obsDSRS<-obsSRD%>%
   filter(Variable=="shootbiomass")%>%
  dplyr::select(Name,Clock.Today,Observed)%>%
  mutate(shootbiomass=Observed)%>%
  mutate(Clock.Today=ymd(Clock.Today))%>%
  mutate(Name=factor(Name))
 
All<-merge(obsDSRR,obsDSRS,by=c("Clock.Today","Name"))%>%
  mutate(Biomass=RootWt+shootbiomass)
 
RUE.RAW<-merge(All,PARiD.df1,by=c("Clock.Today","Name","ExpUnitCode"))
  

phyll <- "D:\\R\\"
StartGrazing <- read.table(paste0(phyll, "ExperimentList.txt"),                       
                           header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(GrowthRotation= as.factor(paste0(GrowthSeason,Rotation)))
 RUE.RAW1<- merge(StartGrazing1,RUE.RAW,by=c("Name","GrowthRotation"))

##RUE Total
RUETotal <-RUE.RAW1%>%
  group_by(Name,GrowthSeason,Rotation,GrowthRotation,Tmean,Ppm,Stage,Trend,ID,ExperimentID) %>%
  do(mod = lm(Biomass~PARi.sum,data=.)) %>%
  mutate(RUEt = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)%>%
  mutate(RUEt1=RUEt*0.1)
##RUE Shoot
RUEshoot<-merge(obsSB,PARi.df1,by=c("Clock.Today","Name","ExpUnitCode"))
RUEshootp<-merge(RUEshoot,StartGrazing1,by=c("Name","GrowthRotation"))
RUEshoots<-RUEshootp%>%
  group_by(Name,GrowthSeason,Rotation,GrowthRotation,Tmean,Ppm,Stage,Trend,ID,ExperimentID) %>%
  do(mod = lm(Shootbiomass~PARi.sum,data=.)) %>%
  mutate(RUEs = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)%>%
  mutate(RUEs1=RUEs*0.1)

```

####plot RUE with diffferent defoliation
```{r}
RUETotal%>%
  mutate()
```

```{r}
 RUE.RAW1%>%
  filter(ID=="E3ISL")%>%
  ggplot(aes(x=PARi.sum,y=Biomass))+geom_point(size=2)+theme_bw()+xlab("Accumlated PARi (J/m^2) ")+ylab(bquote(bold('LAI ('*m^2~m^-2*')')))+ggtitle(paste0("E5IHHF5","(Iversen_91DefoliationLS)"))  +
  # scale_x_continuous(breaks = seq(0, 550, by =200), limits=c(0,500))+
  # scale_y_continuous(breaks = seq(0, 8, by =3), limits=c(0,8))+
 geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="blue")+
 facet_grid(GrowthSeason2~Rotation2)+mytheme1
```






























