---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)

```
# ### load obs data
###filter out FD5 and seedling crop 
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsFD <- read.table(paste0(obsData, "FallDtreatment.txt"),
                   header = TRUE)
obsFDR<- obsFD  %>%
  #dplyr::filter(FD=="FD5")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today))%>%
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
 mutate(Rotation2=as.factor(paste0("R",Rotation)))%>%
   dplyr::filter(Variable==c("RootWt"))

obsFDS<- obsFD  %>%
  #dplyr::filter(FD=="FD5")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today))%>%
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
 mutate(Rotation2=as.factor(paste0("R",Rotation)))%>%
   dplyr::filter(Variable==c("shootbiomass"))

 obsFDSR<-rbind(obsFDR,obsFDS)
```
###Tt then combine yield
```{r}
upDir <- "D:/R/"
obsData <- "D:/R/TtAll/"

Tt<- read.table(paste0(obsData, "df.all.txt"),
               header = TRUE)
TtA <- Tt %>% mutate(Clock.Today=dmy(Clock.Today), ExpUnitCode=as.factor(ExpName))%>%
  dplyr::filter(Tbb==1)

obsFDSRT <-merge(obsFDSR,TtA,by=c("Clock.Today","ExpUnitCode")) %>%
  mutate(GrowthRotation=as.factor(paste0(GrowthSeason.x,Rotation.x)))

  summary(obsFDSRT)
  obsFDSRT
  
```
###My theme
```{r}
mytheme1<-theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14,angle=90, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

mytheme3<-theme(
     legend.title = element_text(colour="black", size=14, face="bold"),
     legend.text = element_text(colour="black", size = 14,face="plain"),
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14),
    legend.position = "right", legend.box = "vertical")
```
###LL
##FD2
```{r,fig.height=5, fig.width=8}
obsFDSRT$Variable<- factor(obsFDSRT$Variable, levels=c("shootbiomass","RootWt"))

obsFDSRTLL2<-obsFDSRT%>%
  dplyr::filter(ID=="E5ILLF2")%>%
  dplyr::filter(ExperimentID=="E5")%>%
  dplyr::filter(Defoliation.x=="LL")
obsFDSRTLL2%>%
 ggplot(aes(x=Clock.Today,y=Observed,color=Variable))+geom_line(size=1)+theme_bw()+
  geom_point(aes(x=Clock.Today,y=Observed))+geom_point(size=3)+
 facet_grid(Variable~ID)+
 geom_point(size=2)+theme(legend.title=element_blank(),legend.position = "blank")+
 theme(legend.title=element_blank())+xlab("Date")+ylab("Biomass (kg/ha)")+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

ggsave("D:/R/Pictures/c6/Yield/E5ILLFD2SR.png", width=8, height=6, dpi=500)
```
###LL
##FD5
```{r,fig.height=5, fig.width=8}
obsFDSRT$Variable<- factor(obsFDSRT$Variable, levels=c("shootbiomass","RootWt"))

obsFDSRTLL5<-obsFDSRT%>%
  dplyr::filter(ID=="E5ILLF5")%>%
  dplyr::filter(ExperimentID=="E5")%>%
  dplyr::filter(Defoliation.x=="LL")
obsFDSRTLL5%>%
 ggplot(aes(x=Clock.Today,y=Observed,color=Variable))+geom_line(size=1)+theme_bw()+
  geom_point(aes(x=Clock.Today,y=Observed))+geom_point(size=3)+
 facet_grid(Variable~ID)+
 geom_point(size=2)+theme(legend.title=element_blank(),legend.position = "blank")+
 theme(legend.title=element_blank())+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

ggsave("D:/R/Pictures/c6/Yield/E5ILLFD5SR.png", width=8, height=6, dpi=500)
```
###LL
##FD10
```{r,fig.height=5, fig.width=8}
obsFDSRT$Variable<- factor(obsFDSRT$Variable, levels=c("shootbiomass","RootWt"))

obsFDSRTLL10<-obsFDSRT%>%
  #dplyr::filter(ID=="E5ILLF10")%>%
  dplyr::filter(ExperimentID=="E5")%>%
  dplyr::filter(Defoliation.x=="LL")
obsFDSRTLL10%>%
 ggplot(aes(x=Clock.Today,y=Observed,color=ID))+geom_line(size=1)+theme_bw()+
  geom_point(aes(x=Clock.Today,y=Observed))+geom_point(size=3)+
facet_wrap(~Variable,ncol = 1)+
 geom_point(size=2)+
 theme(legend.title=element_blank())+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

ggsave("D:/R/Pictures/c6/Yield/E5ILLFD10SR.png", width=8, height=6, dpi=500)
```


###HH
##FD2
```{r,fig.height=5, fig.width=8}
obsFDSRT$Variable<- factor(obsFDSRT$Variable, levels=c("shootbiomass","RootWt"))

obsFDSRTHHF2<-obsFDSRT%>%
  #dplyr::filter(ID=="E5IHHF2")%>%
  dplyr::filter(ExperimentID=="E5")%>%
  dplyr::filter(Defoliation.y=="HH")
obsFDSRTHHF2%>%
 ggplot(aes(x=Clock.Today,y=Observed,color=ID))+geom_line(size=1)+theme_bw()+
  geom_point(aes(x=Clock.Today,y=Observed))+geom_point(size=3)+
  facet_wrap(~Variable,ncol = 1)+
 geom_point(size=2)+
 theme(legend.title=element_blank())+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

ggsave("D:/R/Pictures/c6/Yield/E5IHHFD2SR.png", width=8, height=6, dpi=500)
```
###HH
##FD5
```{r,fig.height=5, fig.width=8}
obsFDSRT$Variable<- factor(obsFDSRT$Variable, levels=c("shootbiomass","RootWt"))

obsFDSRTHHF5<-obsFDSRT%>%
  dplyr::filter(ID=="E5IHHF5")%>%
  dplyr::filter(ExperimentID=="E5")%>%
  dplyr::filter(Defoliation.y=="HH")
obsFDSRTHHF5%>%
 ggplot(aes(x=Clock.Today,y=Observed,color=Variable))+geom_line(size=1)+theme_bw()+
  geom_point(aes(x=Clock.Today,y=Observed))+geom_point(size=3)+
  facet_grid(Variable~ID)+
 geom_point(size=2)+theme(legend.title=element_blank(),legend.position = "blank")+
 theme(legend.title=element_blank())+xlab("Date")+ylab("Biomass (kg/ha)")+
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

ggsave("D:/R/Pictures/c6/Yield/E5IHHFD5SR.png", width=8, height=6, dpi=500)
```
###HH
##FD10
```{r,fig.height=5, fig.width=8}
obsFDSRT$Variable<- factor(obsFDSRT$Variable, levels=c("shootbiomass","RootWt"))

obsFDSRTHHF10<-obsFDSRT%>%
  dplyr::filter(ID=="E5IHHF10")%>%
  dplyr::filter(ExperimentID=="E5")%>%
  dplyr::filter(Defoliation.y=="HH")
obsFDSRTHHF10%>%
 ggplot(aes(x=Clock.Today,y=Observed,color=Variable))+geom_line(size=1)+theme_bw()+
  geom_point(aes(x=Clock.Today,y=Observed))+geom_point(size=3)+
  facet_grid(Variable~ID)+
 geom_point(size=2)+
 geom_point(size=2)+theme(legend.title=element_blank(),legend.position = "blank")+
 theme(legend.title=element_blank())+xlab("Date")+ylab("Biomass (kg/ha)")+
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

ggsave("D:/R/Pictures/c6/Yield/E5IHHFD10SR.png", width=8, height=6, dpi=500)
```


###SS
##FD2
```{r,fig.height=5, fig.width=8}
obsFDSRT$Variable<- factor(obsFDSRT$Variable, levels=c("shootbiomass","RootWt"))

obsFDSRTSS2<-obsFDSRT%>%
  dplyr::filter(ExperimentID=="E5")%>%
  dplyr::filter(Defoliation.x=="SS")
obsFDSRTSS2%>%
ggplot(aes(x=Clock.Today,y=Observed,color=ID))+geom_line(size=1)+theme_bw()+
  geom_point(aes(x=Clock.Today,y=Observed))+geom_point(size=3)+
 facet_wrap(~Variable,ncol = 1)+
 geom_point(size=2)+
 theme(legend.title=element_blank())+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+
    #remove grid lines 
  theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

ggsave("D:/R/Pictures/c6/Yield/E5ISSFD2SR.png", width=8, height=5, dpi=500)
```



## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r, round(r2*100,1))

  return(out)

}
```

## Test stats functions used

```{r}
s <- c(4231.972,3935.604,3779.652,3627.687,3363.499,3230.566,2868.114,2868.827)
m <- c(4987.66,5636.09,4754.06,4114.53,4141.72,3704.06,5142.19,4762.03)


x <- gauchStats(s,m)

tempDf <- data.frame(statName=c("SB","NU","LC","r_MSD","R2"), statValue=x)
# kable(tempDf, digits= 2)
tempDf2 <- data.frame(Predicted=s, Observed=m)

x <- tempDf2 %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>% 
  t() 

df <- data.frame(stat = row.names(x),statvalue = x[,1])

df %>%
  kable(format = "markdown")
```
## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneChapter6.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
summary(df)
head(df) # simulation results
```
# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"_Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)

# myDb %>%
#   dplyr::select(Name) %>%
#   unique()

```
## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  tidyr::gather("Variable","Predicted",LAI:NodeNumber) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)
summary(simD)



mergedf<-merge(obsFDSR, simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)
mergedf

```
##2014-2018
##HH
##F5
```{r,  fig.height=4, fig.width=8}
obsFDHH<-  obsFDSR%>%
  #dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD5")

simD4a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD5")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD4b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD5")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD4<-rbind(simD4a,simD4b)
simD4$Variable<- factor(simD4$Variable, levels=c("shootbiomass","RootWt"))  
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(Variable~ID)+
  geom_point(data=obsFDHH, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+
  scale_y_continuous(breaks = seq(0, 12000, by =4000), limits=c(0,12000))+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
  
ggsave("D:/R/Pictures/C6/Yield/Iversen_121DefoliationHHFDFD5yield.png", width=8, height=6, dpi=500)
```
##HH
##F2
```{r,  fig.height=4, fig.width=8}
obsFDHH2<-  obsFDSR%>%
  #dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD2")

simD1a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD2")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD1b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD2")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD1<-rbind(simD1a,simD1b)
simD1$Variable<- factor(simD1$Variable, levels=c("shootbiomass","RootWt"))  
str(simD1)
simD1%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(Variable~ID)+
  geom_point(data=obsFDHH2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+scale_y_continuous(breaks = seq(0, 10000, by =3000), limits=c(0,10000))+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=25, size = 5, label ="paste(R_RMSD == 39.7,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationHHFDFD5nodenumber1.png", width=8, height=4, dpi=500)
ggsave("D:/R/Pictures/C6/Yield/Iversen_121DefoliationHHFDFD2yield.png", width=8, height=6, dpi=500)
```

##HH
##F10
```{r,  fig.height=4, fig.width=8}
obsFDHH<-  obsFDSR%>%
  #dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD10")

simD2a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD10")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD2b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationHHFDFD10")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD2<-rbind(simD2a,simD2b)
simD2$Variable<- factor(simD1$Variable, levels=c("shootbiomass","RootWt"))  
str(simD2)
simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(Variable~ID)+
  geom_point(data=obsFDHH, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+scale_y_continuous(breaks = seq(0, 11000, by =4000), limits=c(0,11000))+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=25, size = 5, label ="paste(R_RMSD == 39.7,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationHHFDFD5nodenumber1.png", width=8, height=4, dpi=500)
ggsave("D:/R/Pictures/C6/Yield/Iversen_121DefoliationHHFDFD10yield.png", width=8, height=6, dpi=500)
```

##LL
##F10
```{r,  fig.height=4, fig.width=8}
obsFDLL10<-  obsFDSR%>%
  #dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD10")

simD3a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD10")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD3b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD10")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD3<-rbind(simD3a,simD3b)
simD3$Variable<- factor(simD3$Variable, levels=c("shootbiomass","RootWt"))  
str(simD3)
simD3%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(Variable~ID)+
  geom_point(data=obsFDLL10, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=25, size = 5, label ="paste(R_RMSD == 39.7,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationHHFDFD5nodenumber1.png", width=8, height=4, dpi=500)
ggsave("D:/R/Pictures/C6/Yield/Iversen_121DefoliationLLFDFD10yield.png", width=8, height=6, dpi=500)
```
##LL
##F2
```{r,  fig.height=4, fig.width=8}
obsFDLL2<-  obsFDSR%>%
  #dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD2")

simD4a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD2")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD4b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD2")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD4<-rbind(simD4a,simD4b)
simD4$Variable<- factor(simD4$Variable, levels=c("shootbiomass","RootWt"))  
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(Variable~ID)+
  geom_point(data=obsFDLL2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=25, size = 5, label ="paste(R_RMSD == 39.7,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationHHFDFD5nodenumber1.png", width=8, height=4, dpi=500)
ggsave("D:/R/Pictures/C6/Yield/Iversen_121DefoliationLLFDFD2yield.png", width=8, height=6, dpi=500)
```
##LL
##F5
```{r,  fig.height=4, fig.width=8}
obsFDLL5<-  obsFDSR%>%
  #dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD4a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD4b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD4<-rbind(simD4a,simD4b)
simD4$Variable<- factor(simD4$Variable, levels=c("shootbiomass","RootWt"))  
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(Variable~ID)+
  geom_point(data=obsFDLL5, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   
ggsave("D:/R/Pictures/C6/Yield/Iversen_121DefoliationLLFDFD5yield.png", width=8, height=6, dpi=500)
```

##SS
##F10
```{r,  fig.height=4, fig.width=8}
obsFDSS10<-  obsFDSR%>%
  #dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD10")

simD4a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD10")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD4b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD10")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD4<-rbind(simD4a,simD4b)
simD4$Variable<- factor(simD4$Variable, levels=c("shootbiomass","RootWt"))  
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(Variable~ID)+
  geom_point(data=obsFDSS10, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=25, size = 5, label ="paste(R_RMSD == 39.7,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationHHFDFD5nodenumber1.png", width=8, height=4, dpi=500)
ggsave("D:/R/Pictures/C6/Yield/Iversen_121DefoliationSSFDFD10yield.png", width=8, height=6, dpi=500)
```
##SS
##F5
```{r,  fig.height=4, fig.width=8}
obsFDSS5<-  obsFDSR%>%
  #dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD5")

simD4a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD5")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD4b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD5")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD4<-rbind(simD4a,simD4b)
simD4$Variable<- factor(simD4$Variable, levels=c("shootbiomass","RootWt"))  
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(Variable~ID)+
  geom_point(data=obsFDSS5, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   
ggsave("D:/R/Pictures/C6/Yield/Iversen_121DefoliationSSFDFD5yield.png", width=8, height=6, dpi=500)
```

##SS
##F2
```{r,  fig.height=4, fig.width=8}
obsFDSS2<-  obsFDSR%>%
  #dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD2")

simD5a<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD2")%>%
  dplyr::filter(Clock.Today<"2015-01-06")

simD5b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt"|Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationSSFDFD2")%>%
  dplyr::filter(Clock.Today>"2015-01-30")
simD5<-rbind(simD5a,simD5b)
simD5$Variable<- factor(simD5$Variable, levels=c("shootbiomass","RootWt"))  
str(simD5)
simD5%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(Variable~ID)+ggtitle(paste0("E5ISSFD2","(Iversen_121DefoliationSSFDFD2)"))+
  geom_point(data=obsFDSS2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Biomass ('*kg~ha^-1*')')))+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=25, size = 5, label ="paste(R_RMSD == 39.7,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationHHFDFD5nodenumber1.png", width=8, height=4, dpi=500)
ggsave("D:/R/Pictures/C6/Yield/Iversen_121DefoliationSSFDFD2yield.png", width=8, height=6, dpi=500)
```
##Shootbiomass
```{r,,fig.height=6, fig.width=8}

mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "shootbiomass") %>% 
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(ID))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("shoot biomass")+mytheme3+
  facet_wrap(~ID, ncol = 3)+theme(legend.title=element_blank(),legend.position = "blank")+
  xlab("Observed")+ylab("Predicted")+
  scale_x_continuous(breaks = seq(0, 12000, by =6000), limits=c(0,12000))+
  scale_y_continuous(breaks = seq(0, 12000, by =4000), limits=c(0,12000))+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
ggsave("D:/R/Pictures/C6/Yield/shoot2.png", width=8, height=6, dpi=500)
```
## RMSE
###shoot
```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "shootbiomass") %>% 
  filter(Collection!="2010_2012")%>%
  group_by(ID) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```
##root biomass
```{r,,fig.height=6, fig.width=8}

mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "RootWt") %>% 
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(ID))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Root biomass")+mytheme3+
  facet_wrap(~ID, ncol = 3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  scale_y_continuous(breaks = seq(0, 8000, by =4000), limits=c(0,8000))+
  scale_x_continuous(breaks = seq(3000, 8000, by =5000), limits=c(0,8000))+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
ggsave("D:/R/Pictures/C6/Yield/Root2.png", width=8, height=6, dpi=500)
```
## RMSE
###root
```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "RootWt") %>% 
  filter(Collection!="2010_2012")%>%
  group_by(ID) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```







