---
title: "R Notebook"
output: html_notebook
---
###Yield analysis

```{r Load, warning=FALSE, fig.height=8, fig.width=8}
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)
library(tidyverse)
```
## lode observed data
```{r}
upDir <- "D:/R/CombinedData/"
obsData <- "D:/R/CombinedData/"

obsAll <- read.table(paste0(obsData, "ObsAll1.txt"),
                   header = TRUE)
obsA1<- obsAll %>%
  dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Water!="dry")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
 mutate(Rotation2=as.factor(ifelse(Rotation=="1",paste0("S",Rotation),paste0("R",Rotation))))

obsA4<- obsAll %>%
  dplyr::filter(Collection=="2014_2018")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
  mutate(Rotation2=as.factor(ifelse(Rotation=="1",paste0("S",Rotation),paste0("R",Rotation))))
 

  obsA2<- obsAll %>%
  dplyr::filter(Collection=="1997_2001")%>%
  dplyr::filter(Water!="dry")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
  mutate(Rotation2=as.factor(paste0("R",Rotation)))
  

  obsA3<- obsAll %>%
  dplyr::filter(Collection=="2002_2004")%>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate),Clock.Today=dmy(Clock.Today)) %>%
  #mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason1=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation1=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Name,GrowthSeason1,Rotation1))) %>%
  mutate(Clock.Today1 = as.POSIXct(paste(Clock.Today,Time),format="%Y-%m-%d %H:%M:%S"))%>%
  mutate(GrowthSeason2=as.factor(paste0("Y",GrowthSeason,"(",Period,")"))) %>%
  mutate(Rotation2=as.factor(paste0("R",Rotation)))
  
obsA<-rbind(obsA2,obsA3,obsA1,obsA4)
summary(obsA)
 obsA
```
###My theme
```{r}
mytheme1<-theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14,angle=90, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))

mytheme3<-theme(
     legend.title = element_text(colour="black", size=14, face="bold"),
     legend.text = element_text(colour="black", size = 14,face="plain"),
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14),
    legend.position = "right", legend.box = "vertical")
```

## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r, round(r2*100,1))

  return(out)

}
```

## Test stats functions used

```{r}
s <- c(4231.972,3935.604,3779.652,3627.687,3363.499,3230.566,2868.114,2868.827)
m <- c(4987.66,5636.09,4754.06,4114.53,4141.72,3704.06,5142.19,4762.03)


x <- gauchStats(s,m)

tempDf <- data.frame(statName=c("SB","NU","LC","r_MSD","R2"), statValue=x)
# kable(tempDf, digits= 2)
tempDf2 <- data.frame(Predicted=s, Observed=m)

x <- tempDf2 %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>% 
  t() 

df <- data.frame(stat = row.names(x),statvalue = x[,1])

df %>%
  kable(format = "markdown")
```
## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneChapter4.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
head(df) # simulation results
```
# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"_Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))
head(myDb)

```
## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
myDb1 <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  mutate(TotalDM=shootbiomass+RootWt)

simD <- myDb1 %>%
  dplyr::select(Name,Clock.Today,LAI,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber,TotalDM) %>%
  tidyr::gather("Variable","Predicted",LAI:TotalDM) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)
summary(simD)
  
mergedf<-merge(obsA,simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)
mergedf

```

###LAI
###chapter4
## 1997-2001
```{r,fig.height=4, fig.width=8}

obsLAI1<-obsA%>%
  dplyr::filter(Collection=="1997_2001")%>%
  dplyr::filter(Variable=="LAI")%>%
  dplyr::filter(Name=="Iversen_8Waterirr")%>%
  dplyr::filter(Clock.Today>"1996-08-01")%>%
  dplyr::filter(Clock.Today<"2000-08-01")
   
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Clock.Today>"1996-08-01")%>%
   dplyr::filter(Clock.Today<"2001-08-01")%>%
   dplyr::filter(Variable=="LAI")%>%
   dplyr::filter(Name=="Iversen_8Waterirr")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~ID,ncol = 2)+
   mytheme3+
 #annotate("text", x=ymd_hms("1999-10-24 12:00:00"), y=8, size = 5, label ="paste(R_RMSD == 52.5,'%')", parse=T)+
   #geom_text(aes(x=ymd_hms("1999-10-24 12:00:00"), y=750, label="R_RMSD = 37.6%",size=5))
 geom_point(data=obsLAI1, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('LAI ('*m^2~m^-2*')')))
 
 #ggsave("D:/R/Pictures/LAI/Iversen_8WaterirrLAI1.png", width=8, height=4, dpi=500)

```
##2002-2004
```{r,  fig.height=4, fig.width=8}
obsLAI2<-obsA%>% 
  dplyr::filter(Collection=="2002_2004")%>%
  dplyr::filter(Variable=="LAI")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")

simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2002-06-01")%>%
  dplyr::filter(Variable=="LAI")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
str(simD2)

simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 1)+
  geom_point(data=obsLAI2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('LAI ('*m^2~m^-2*')')))+
   mytheme3
 #annotate("text", x=ymd_hms("2003-07-24 12:00:00"), y=8, size = 5, label ="paste(R_RMSD == 43.2,'%')", parse=T)
#ggsave("D:/R/Pictures/LAI/Iversen_91DefoliationLLLAI1.png", width=8, height=4, dpi=500)
```
###2000-2002
```{r,  fig.height=8, fig.width=8}
obsLAI3<-obsA%>%
  dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Variable=="LAI")
 

simD3b<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2000-10-24 12:00:00")%>%
  dplyr::filter(Clock.Today<"2002-07-01 12:00:00")%>%
  dplyr::filter(Name==c("Iversen_9SowingDateSD1Waterirr","Iversen_9SowingDateSD2Waterirr","Iversen_9SowingDateSD3Waterirr","Iversen_9SowingDateSD4Waterirr"))%>%
  dplyr::filter(Variable=="LAI")
DF<-data.frame(Name=c("Iversen_9SowingDateSD1Waterirr","Iversen_9SowingDateSD2Waterirr","Iversen_9SowingDateSD3Waterirr","Iversen_9SowingDateSD4Waterirr"),ID= c("E2ILLS1","E2ILLS2","E2ILLS3","E2ILLS4"))
simD3<-merge(DF,simD3b, by=c("Name"))
 
simD3%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 2)+
  geom_point(data=obsLAI3, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('LAI ('*m^2~m^-2*')')))+
  mytheme3
  
```

##2014-2018
```{r,  fig.height=4, fig.width=8}
obsLAI4<-obsA%>%
  dplyr::filter(Collection=="2014_2018")%>%
  dplyr::filter(Variable=="LAI")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD4<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="LAI")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 1)+
  geom_point(data=obsLAI4, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('LAI ('*m^2~m^-2*')')))+
  mytheme3

```
# Statistic and Graph
##LAI
```{r,,fig.height=4, fig.width=10}

mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "LAI") %>% 
  dplyr::filter(Stage== "Regrowth") %>% 
  dplyr::filter(FD== "FD5")%>%
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(ID))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("LAI")+mytheme3+
  facet_wrap(~Collection, ncol = 4)+
  theme(legend.title=element_blank())+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```
# Statistic and Graph
##LAI
```{r,,fig.height=6, fig.width=10}

mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
  dplyr::filter(Stage== "Regrowth") %>% 
    dplyr::filter(Variable== "LAI") %>% 
  dplyr::filter(FD== "FD5")%>%
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(ID))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("LAI")+mytheme3+
  facet_wrap(~Month, ncol = 4)+
  theme(legend.title=element_blank())+
  xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```
## RMSE
###Lai
```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "LAI") %>% 
  dplyr::filter(FD== "FD5")%>%
  # dplyr::filter(Defoliation.x== "LL")%>%
 #filter(Variable == "NodeNumber") %>%
  filter(Collection!="2010_2012")%>%
  #mutate(Rotation= as.factor(Rotation.x))%>%
  #mutate(GrowthSeason=as.factor(GrowthSeason.x))%>%
  group_by(Name) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```

####Shootbiomass
## 1997-2001
```{r,fig.height=4, fig.width=9}

obsYield1<-obsA%>%
  dplyr::filter(Collection=="1997_2001")%>%
  dplyr::filter(Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_8Waterirr")%>%
  dplyr::filter(Clock.Today>"1997-08-01")%>%
  dplyr::filter(Clock.Today<"2001-08-01")
  
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Clock.Today>"1997-08-01")%>%
   dplyr::filter(Clock.Today<"2001-08-01")%>%
   dplyr::filter(Variable=="shootbiomass")%>%
   dplyr::filter(Name=="Iversen_8Waterirr")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~ID,ncol = 2)+
 geom_point(data=obsYield1, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Shoot DM ('*kg~ha^-1*')')))+
 mytheme3
 #annotate("text", x=ymd_hms("1999-10-24 12:00:00"), y=6500, size = 5, label ="paste(R_RMSD == 55.1,'%')", parse=T)

 #ggsave("D:/R/Pictures/shoot/Iversen_8Waterirrshootbiomass.png", width=8, height=4, dpi=500)
```
##2002-2004
```{r,  fig.height=4, fig.width=8}
obsYield2<-obsA%>% 
  dplyr::filter(Collection=="2002_2004")%>%
  dplyr::filter(Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")

simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2002-06-01")%>%
  dplyr::filter(Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
str(simD2)
simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 1)+
  geom_point(data=obsYield2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Shoot DM ('*kg~ha^-1*')')))+
 mytheme3
 #  annotate("text", x=ymd_hms("2003-07-24 12:00:00"), y=6000, size = 5, label ="paste(R_RMSD == 22.6,'%')", parse=T)
 # #geom_text(aes(x=ymd_hms("2003-07-24 12:00:00"), y=750, label="R_RMSD = 27.6%",size=5))
 # ggsave("D:/R/Pictures/Shoot/Iversen_91DefoliationLLheight1.png", width=8, height=4, dpi=500)


```
###2000-2002
```{r,  fig.height=8, fig.width=10}
obsYield3<-obsA%>% 
  dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Variable=="shootbiomass")
 obsYield3

simD3B<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2000-10-24 12:00:00")%>%
  dplyr::filter(Clock.Today<"2002-07-01 12:00:00")%>%
  dplyr::filter(Name==c("Iversen_9SowingDateSD1Waterirr","Iversen_9SowingDateSD2Waterirr","Iversen_9SowingDateSD3Waterirr","Iversen_9SowingDateSD4Waterirr"))%>%
   dplyr::filter(Variable=="shootbiomass")

DF<-data.frame(Name=c("Iversen_9SowingDateSD1Waterirr","Iversen_9SowingDateSD2Waterirr","Iversen_9SowingDateSD3Waterirr","Iversen_9SowingDateSD4Waterirr"),ID= c("E2ILLS1","E2ILLS2","E2ILLS3","E2ILLS4"))
simD3<-merge(DF,simD3B, by=c("Name"))

simD3%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 2)+
  geom_point(data=obsYield3, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Shoot DM ('*kg~DM~ha^-1*')')))+mytheme3



# dat_text3 <- data.frame(
#   label = c("R_RMSE=38.9%","R_RMSE=46.2%","R_RMSE=52.9%", "R_RMSE=54.9%"),
#   ID= c("E2ILLS1","E2ILLS2","E2ILLS3","E2ILLS4"),
#   x= ymd_hms("2001-05-24 12:00:00", "2001-05-24 12:00:00","2001-05-24 12:00:00","2001-05-24 12:00:00"),
#    y=c(6500,6500,6500,6500)) 
# 
#  p1a  +geom_text(data=dat_text3, mapping = aes(x=x,y=y, label = label),hjust   = -0.1,vjust   = -1,size=5)+mytheme3
 
#ggsave("D:/R/Pictures/Shoot/Iversen_9SowingDateSDWatershoot.png", width=8, height=8, dpi=500)
  
  
```
##2014-2018
```{r,  fig.height=4, fig.width=8}
obsYield4<-obsA%>%
  dplyr::filter(Collection=="2014_2018")%>%
  dplyr::filter(Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD4<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="shootbiomass")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~ID,ncol = 1)+
  geom_point(data=obsYield4, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab(bquote(bold('Shoot DM ('*kg~ha^-1*')')))+
  mytheme3
  #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=8500, size = 5, label ="paste(R_RMSD == 77.4,'%')" , parse=T)
 #geom_text(aes(x=ymd_hms("2016-07-24 12:00:00"), y=920,label="R_RMSD = 40%",size=5))
 #ggsave("D:/R/Pictures/Shoot/Iversen_121DefoliationLLFDFD5shoot1.png", width=8, height=4, dpi=500)
  
```
##Shootbiomass
```{r,,fig.height=4, fig.width=10}

mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "shootbiomass") %>% 
  dplyr::filter(FD== "FD5")%>%
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(ID))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("shoot biomass")+mytheme3+
  facet_wrap(~Collection, ncol = 4)+
  theme(legend.title=element_blank())+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```
##Shootbiomass
```{r,,fig.height=6, fig.width=10}

mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "shootbiomass") %>% 
  dplyr::filter(FD== "FD5")%>%
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(ID))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("shoot biomass")+mytheme3+
  facet_wrap(~Month, ncol = 4)+
  theme(legend.title=element_blank())+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```
## RMSE
###shoot
```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "shootbiomass") %>% 
  dplyr::filter(FD== "FD5")%>%
  # dplyr::filter(Defoliation.x== "LL")%>%
 #filter(Variable == "NodeNumber") %>%
  filter(Collection!="2010_2012")%>%
  #mutate(Rotation= as.factor(Rotation.x))%>%
  #mutate(GrowthSeason=as.factor(GrowthSeason.x))%>%
  group_by(Name) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```
####leaf biomass
##2002-2004
```{r,  fig.height=4, fig.width=8}
ObsLeaf2<-obsA%>% 
  dplyr::filter(Collection=="2002_2004")%>%
  dplyr::filter(Variable=="LeafWt")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")

simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2002-06-01")%>%
  dplyr::filter(Variable=="LeafWt")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
str(simD2)
simD2$Variable<- factor(simD2$Variable, levels=c("LeafWt")) 

simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(~ID)+ggtitle(paste0("E3ILL","(Iversen_91DefoliationLL)"))+
  geom_point(data=ObsLeaf2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Leaf biomass (kg/ha)")+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=18, size = 5, label ="paste(R_RMSD == 64.5,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationLLFDFD5nodenumber1.png", width=8, height=4, dpi=500)
#ggsave("D:/R/Pictures/C5/Yield/Iversen_91DefoliationLLyield.png", width=8, height=8, dpi=500)
  


```
##2014-2018
```{r,  fig.height=4, fig.width=8}
ObsLeaf4<-obsA%>% 
  dplyr::filter(Collection=="2014_2018")%>%
  dplyr::filter(Variable=="LeafWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD4<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="LeafWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD4$Variable<- factor(simD4$Variable, levels=c("LeafWt"))
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(~ID)+ggtitle(paste0("E5ILLFD5","(Iversen_121DefoliationLLFDFD5)"))+
  geom_point(data=ObsLeaf4, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Leaf biomass(kg/ha)")+
 #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=18, size = 5, label ="paste(R_RMSD == 64.5,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationLLFDFD5nodenumber1.png", width=8, height=4, dpi=500)
#ggsave("D:/R/Pictures/C5/Yield/Iversen_121DefoliationLLFDFD5yield.png", width=8, height=8, dpi=500)
  

```


##Leaf biomass
```{r,,fig.height=4, fig.width=10}

mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "LeafWt") %>% 
  dplyr::filter(FD== "FD5")%>%
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(ID))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Leaf biomass")+mytheme3+
  facet_wrap(~Collection, ncol = 4)+
  theme(legend.title=element_blank())+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

## RMSE
###leaf
```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "LeafWt") %>% 
  dplyr::filter(FD== "FD5")%>%
  # dplyr::filter(Defoliation.x== "LL")%>%
 #filter(Variable == "NodeNumber") %>%
  filter(Collection!="2010_2012")%>%
  #mutate(Rotation= as.factor(Rotation.x))%>%
  #mutate(GrowthSeason=as.factor(GrowthSeason.x))%>%
  group_by(Name) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```
####Stem biomass
##2002-2004
```{r,  fig.height=4, fig.width=8}
ObsStem2<-obsA%>% 
  dplyr::filter(Collection=="2002_2004")%>%
  dplyr::filter(Variable=="StemWt")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")

simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2002-06-01")%>%
  dplyr::filter(Variable=="StemWt")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
str(simD2)
simD2$Variable<- factor(simD2$Variable, levels=c("StemWt")) 

simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(~ID)+ggtitle(paste0("E3ILL","(Iversen_91DefoliationLL)"))+
  geom_point(data=ObsStem2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Stem biomass (kg/ha)")+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=18, size = 5, label ="paste(R_RMSD == 64.5,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationLLFDFD5nodenumber1.png", width=8, height=4, dpi=500)
#ggsave("D:/R/Pictures/C5/Yield/Iversen_91DefoliationLLyield.png", width=8, height=8, dpi=500)
  


```

##2014-2018
```{r,  fig.height=4, fig.width=8}
ObsStem4<-obsA%>% 
  dplyr::filter(Collection=="2014_2018")%>%
  dplyr::filter(Variable=="StemWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD4<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="StemWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD4$Variable<- factor(simD4$Variable, levels=c("StemWt"))
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(~ID)+ggtitle(paste0("E5ILLFD5","(Iversen_121DefoliationLLFDFD5)"))+
  geom_point(data=ObsStem4, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Stem biomass(kg/ha)")+
 #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=18, size = 5, label ="paste(R_RMSD == 64.5,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationLLFDFD5nodenumber1.png", width=8, height=4, dpi=500)
#ggsave("D:/R/Pictures/C5/Yield/Iversen_121DefoliationLLFDFD5yield.png", width=8, height=8, dpi=500)
  

```

##Stem biomass
```{r,,fig.height=4, fig.width=10}

mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "StemWt") %>% 
  dplyr::filter(FD== "FD5")%>%
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(ID))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Stem biomass")+mytheme3+
  facet_wrap(~Collection, ncol = 4)+
  theme(legend.title=element_blank())+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

## RMSE
###Stem
```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "StemWt") %>% 
  dplyr::filter(FD== "FD5")%>%
  # dplyr::filter(Defoliation.x== "LL")%>%
 #filter(Variable == "NodeNumber") %>%
  filter(Collection!="2010_2012")%>%
  #mutate(Rotation= as.factor(Rotation.x))%>%
  #mutate(GrowthSeason=as.factor(GrowthSeason.x))%>%
  group_by(Name) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```




####Rootbiomass
##2002-2004
```{r,  fig.height=4, fig.width=8}
ObsR2<-obsA%>% 
  dplyr::filter(Collection=="2002_2004")%>%
  dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")

simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2002-06-01")%>%
  dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
str(simD2)
simD2$Variable<- factor(simD2$Variable, levels=c("shootbiomass","RootWt")) 

simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(~ID)+ggtitle(paste0("E3ILL","(Iversen_91DefoliationLL)"))+
  geom_point(data=ObsR2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Biomass (kg/ha)")+
  #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=18, size = 5, label ="paste(R_RMSD == 64.5,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationLLFDFD5nodenumber1.png", width=8, height=4, dpi=500)
#ggsave("D:/R/Pictures/C5/Yield/Iversen_91DefoliationLLyield.png", width=8, height=8, dpi=500)
  


```
##2014-2018
```{r,  fig.height=4, fig.width=8}
ObsR4<-obsA%>% 
  dplyr::filter(Collection=="2014_2018")%>%
  dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD4<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Variable=="RootWt")%>%
  dplyr::filter(Name=="Iversen_121DefoliationLLFDFD5")

simD4$Variable<- factor(simD4$Variable, levels=c("shootbiomass","RootWt"))
str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_grid(~ID)+ggtitle(paste0("E5ILLFD5","(Iversen_121DefoliationLLFDFD5)"))+
  geom_point(data=ObsR4, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Root biomass(kg/ha)")+
 #remove grid lines 
   theme(
     panel.spacing=unit(.01, "lines"),
     panel.border = element_rect(colour = "black",size=1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black",size = 1),
     axis.text.x = element_text(face = "plain", color = "black", size = 14, vjust=0.5, hjust = 1),
     axis.text.y = element_text(face = "plain", color = "black", size = 14),
     axis.title.x=element_text(face="bold",colour="black",size = 14),
     axis.title.y=element_text(face="bold",colour="black",size = 14),
     strip.background = element_rect(colour = "black", fill = "white",size=1),
     strip.text.x = element_text(size=14, angle=0, face = "plain"), 
     strip.text.y = element_text(size=14, face="plain"),
     legend.title = element_text(colour="black", size=14, face="bold"),
     axis.text = element_text(face = "bold", vjust = 0.5, size = 14))
   #annotate("text", x=ymd_hms("2016-07-24 12:00:00"), y=18, size = 5, label ="paste(R_RMSD == 64.5,'%')", parse=T)
   #ggsave("D:/R/Pictures/C5/Node/Iversen_121DefoliationLLFDFD5nodenumber1.png", width=8, height=4, dpi=500)
#ggsave("D:/R/Pictures/C5/Yield/Iversen_121DefoliationLLFDFD5yield.png", width=8, height=8, dpi=500)
  

```


##root biomass
```{r,,fig.height=4, fig.width=10}

mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "RootWt") %>% 
  dplyr::filter(FD== "FD5")%>%
  dplyr::filter(Collection!="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, colour= factor(ID))) +
  geom_point(size=2)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Root biomass")+mytheme3+
  facet_wrap(~Collection, ncol = 4)+
  theme(legend.title=element_blank())+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

## RMSE
###root
```{r}
str(mergedf)

mergedf %>%
  dplyr::filter(Variable== "RootWt") %>% 
  dplyr::filter(FD== "FD5")%>%
  # dplyr::filter(Defoliation.x== "LL")%>%
 #filter(Variable == "NodeNumber") %>%
  filter(Collection!="2010_2012")%>%
  #mutate(Rotation= as.factor(Rotation.x))%>%
  #mutate(GrowthSeason=as.factor(GrowthSeason.x))%>%
  group_by(Name) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

  
```

