---
title: "R Notebook"
output: html_notebook
---
## load library
```{r Load,echo=TRUE, include = TRUE, warning=FALSE, fig.height=8, fig.width=8}
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)

```
##load Observed data
```{r, echo=FALSE}
upDir <- "D:\\APSIMX2\\Prototypes\\Lucerne\\"
obsF <- "D:\\Model work\\APSIMX\\"
rawObs <- read.table(paste0(obsF, "ObsDataForStats.txt"), 
                      header = TRUE)
unique(rawObs$Name)
```
## Tidy up Observed data
```{r, echo=FALSE}
head(rawObs)
```

* Sort out formats
* Create factor labels
```{r}
# get time format right
obsData <- rawObs %>% mutate(Clock.Today = dmy(Clock.Today))
str(obsData)
head(obsData)
summary(obsData)
```
## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc
  #nse <- 1-(sum((sim - mean(sim))^2)/sum((meas - mean(meas))^2))
  #rsr<- sqrt(sum((sim - mean(sim))^2)/sqrt(sum((meas - mean(meas))^2)

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r,round(r2*100,1))

  return(out)

}
```

## Test stats functions used

```{r}
s <- c(4231.972,3935.604,3779.652,3627.687,3363.499,3230.566,2868.114,2868.827)
m <- c(4987.66,5636.09,4754.06,4114.53,4141.72,3704.06,5142.19,4762.03)

x <- gauchStats(s,m)

tempDf <- data.frame(statName=c("SB","NU","LC","r_MSD","R2"), statValue=x)
# kable(tempDf, digits= 2)
tempDf2 <- data.frame(Predicted=s, Observed=m)

x <- tempDf2 %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>% 
  t() 

df <- data.frame(stat = row.names(x),statvalue = x[,1])

df %>%
  kable(format = "markdown")
```
## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}

db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneValidation.db"
con <- dbConnect(SQLite(), dbname = db.address, flags = SQLITE_RW)
alltables <- dbListTables(con)
alltables
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(DbTable)
str(df)
summary(df)
head(df) # simulation results
```
# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"_Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)

# myDb %>%
#   dplyr::select(Name) %>%
#   unique()

```
## node appearance analysis
## load metTT
## Select datasets for chapter 1  
```{r}
obsD <- obsData %>%
  dplyr::filter(Water=="irr")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")
  
obsD
```

## Merge TTsum with Observed Data
```{r}
 met <- "D:\\R\\Data statistic\\"
 metTT <- read.table(paste0(met, "metTT.txt"), 
                     header = TRUE)

dfTp <- metTT %>% dplyr::select(Clock.Today, TTsum1, TTsum5,Pp,mean)%>%
  mutate(Clock.Today=dmy(Clock.Today))
dfTp
        

obscom<-merge(dfTp,obsD, by=c("Clock.Today")) 
obscom

```
##Tb validation
## X-intercept
```{r,fig.height=4, fig.width=10}
# primary leaf appearance rate (LAR,days/leaf)
obscom%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  ggplot(aes(x=Clock.Today,y=Observed),color= factor(Name))+
  geom_point(size=3)+theme_bw()+
  facet_wrap(~Name,ncol=2)

  
mainN<-obscom%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  group_by(Name,StartDate,FinishDate,GrowthSeason,Rotation,mean)%>%
  do(mod = lm(Observed~Interval,data=.)) %>%
  mutate(Slope = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)

mainN
mainN%>%
  ggplot(aes(x=mean, y= Slope))+
  geom_point(size=3)+theme_bw()+
  #facet_grid(GrowthSeason~Rotation)+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  #coord_fixed(ratio = 1) +
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Tmean")+ylab("LAR")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))





```




## calculate phyllo

```{r}

nodes <- obscom %>%dplyr::filter(Variable=="NodeNumber")

phylloData <- nodes %>%
  group_by(Name,GrowthSeason,Rotation) %>%
  do(mod = lm(TTsum1 ~Observed,data=.)) %>%
  mutate(Slope = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)
  #nodes$GrowthRotation<-factor(paste(nodes$GrowthSeason,nodes$Rotation))
  #ggplot(nodes, x=GrowthRotation, y=Slope)+geom_line(size=2)

#write.csv(phylloData,"D:/R/Data statistic/Data.csv", row.names = FALSE)
phylloData
   

```
##Tb=5
```{r}

nodes <- obscom %>%dplyr::filter(Variable=="NodeNumber")

phylloData1 <- nodes %>%
  group_by(Name,GrowthSeason,Rotation) %>%
  do(mod = lm(TTsum5 ~Observed,data=.)) %>%
  mutate(Slope1 = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)
  #nodes$GrowthRotation<-factor(paste(nodes$GrowthSeason,nodes$Rotation))
  #ggplot(nodes, x=GrowthRotation, y=Slope)+geom_line(size=2)

#write.csv(phylloData,"D:/R/Data statistic/Data.csv", row.names = FALSE)
phylloData1

```
```{r}
phyll <- "D:\\R\\Data statistic\\"
StartGrazing <- read.table(paste0(phyll, "Phyllo.txt"), 
                      header = TRUE)
StartGrazing1<-StartGrazing %>%
  mutate(Clock.Today = dmy(Clock.Today))%>%
  mutate(DateFinish= dmy(DateFinish))
phylloData
StartGrazing1


PhylloPp <- merge(StartGrazing1,phylloData,by=c("Name","GrowthSeason","Rotation"))
PhylloPp
PhylloPp%>%
ggplot(aes(x=Pp,y=Slope,color=factor(Name)))+geom_point(size=2)+theme_bw()+
   facet_wrap(~PpT,ncol=2)+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) 
# PpTI and PpTD
PhylloPpI<-PhylloPp%>%
  dplyr::filter(PpT=="I")
PhylloPpD<-PhylloPp%>%
  dplyr::filter(PpT=="D")

  cor.test(PhylloPpI$Pp,PhylloPpI$Slope,method="spearman")
   cor.test(PhylloPpD$Pp,PhylloPpD$Slope,method="spearman")
   
phyppmodelI<-lm(Pp~Slope,data=PhylloPpI)
phyppmodelD<-lm(Pp~Slope,data=PhylloPpD)

summary(phyppmodelI)
summary(phyppmodelD)
```







```{r,warning=False}
PhylloPp%>%
ggplot(aes(x=Pp, y= Slope, 
          color= factor(Name))) +
  geom_point(size=3)+theme_bw() +
  #ggtitle("Phyllochron")  +
  # facet_wrap(~Name, ncol = 3)+
  facet_wrap(~Stage, ncol=2)+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  #coord_fixed(ratio = 1) +
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Photoperiod")+ylab("Phyllochron")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
# seedling and regrowth 
PhylloPpS<-PhylloPp%>%
  dplyr::filter(Stage=="seedling")
PhylloPpR<-PhylloPp%>%
  dplyr::filter(Stage=="regrowth")

  cor.test(PhylloPpS$Pp,PhylloPpS$Slope,method="spearman")
   cor.test(PhylloPpR$Pp,PhylloPpR$Slope,method="spearman")
   
phyppmodelS<-lm(Pp~Slope,data=PhylloPpS)
phyppmodelR<-lm(Pp~Slope,data=PhylloPpR)

summary(phyppmodelS)
summary(phyppmodelR)
   
  
```
##height analysis!!!

```{r}
# obscom
# Height <- obscom %>% dplyr::filter(
#        mutate(Internode=Height/NodeNumber)
# Height
# Height%>%
#   ggplot(aes(x=mean,y=Observed,color=factor(Name)))+theme_bw()+
#   geom_point(size=3)+
#   facet_wrap(~Name)+
#   geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
#   theme(legend.title=element_blank(),legend.position = "blank")+xlab("Height")+ylab("Date")+
#   theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
#   theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```


```{r}
HeightR <- Height %>%
group_by(Name,GrowthSeason,Rotation,StartDate,FinishDate) %>%
   do(mod = lm(TTsum1 ~Observed,data=.)) %>%
   mutate(Slope = summary(mod)$coeff[2]) %>%
   dplyr::select(-mod)
HeightR
Heightcom <- merge(StartGrazing1,HeightR,by=c("Name","GrowthSeason","Rotation"))
 Heightcom%>%
   ggplot(aes(x=Pp,y=Slope,color=factor(Name)))+geom_point(size=2)+theme_bw()+
   facet_wrap(~PpT,ncol=2)+
   geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) 
   


```

## leaf area index analysis
## light interception and biomass 
## partitioning











































## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,SWC,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  tidyr::gather("Variable","Predicted",LAI:NodeNumber) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)

head(obsD)
mergedf<-merge(obsD,simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)

```

## Node number
#Time series
## obs Vs Pre for each experiment
## 1997-2001
```{r,fig.height=4, fig.width=8}
obsD%>%
    mutate(Name = as.factor(Name)) %>%
    mutate(Variable = as.factor(Variable)) %>%
    mutate(Clock.Today = ymd_hms(Clock.Today))
  obsD$Clock.Today1 <-as.POSIXct(paste(obsD$Clock.Today,obsD$Time),format="%Y-%m-%d %H:%M:%S")
  obsD1<-obsD%>%dplyr::filter(Variable=="NodeNumber")%>%
  mutate(Clock.Today1= ymd_hms(Clock.Today1))
  summary(obsD1)
  obsD2<-obsD1%>%dplyr::filter(Collection=="1997_2001")
  
 
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Variable=="NodeNumber")%>%
   dplyr::filter(Name=="Iversen_8Waterirr")
 str(simD1)
 
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~Name,ncol = 2)+
 geom_point(data=obsD2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
 theme(axis.title.x=element_text(face="bold",colour="black",size = 14))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 14))

```

```{r, fig.width=3, fig.height=6, warning=FALSE}
mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
    dplyr::filter(Collection=="1997_2001")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw() +
   geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1) +
  ggtitle("Node Number")  +
  facet_wrap(~Name, ncol = 1)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```
## 2000-2002
```{r,  fig.height=8, fig.width=8}
obsD%>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))
obsD2<-obsD%>%dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Collection=="2000_2002")
obsD2

simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2000-10-24 12:00:00")%>%
  dplyr::filter(Clock.Today<"2002-07-01 12:00:00")%>%
  dplyr::filter(Name!="Iversen_8Waterdry")%>%
  dplyr::filter(Name!="Iversen_8Waterirr")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="MooraDefoliation")%>%
  dplyr::filter(Name!="NekiaDefoliation")%>%
  dplyr::filter(Name!="QuairadingDefoliation")%>%
  dplyr::filter(Name!="RoseworthyWaterdry")%>%
  dplyr::filter(Name!="RoseworthyWaterirr")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD1Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD2Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD3Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD4Waterdry")%>%
  dplyr::filter(Variable=="NodeNumber")
  str(simD2)
simD2%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 2)+
  geom_point(data=obsD2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  facet_wrap(~Name,ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 14))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 14))

```








```{r,  fig.height=8, fig.width=10}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
    dplyr::filter(Collection=="2000_2002")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_wrap(~Name, ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

## 2002-2004
```{r,  fig.height=4, fig.width=8}
obsD%>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))
obsD3<-obsD%>%dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Collection=="2002_2004")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
  

simD3<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  dplyr::filter(Variable=="NodeNumber")
  
str(simD3)
simD3%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 1)+
  geom_point(data=obsD3, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 14))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 14))
```


```{r,  fig.height=4 fig.width=8}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
    dplyr::filter(Collection=="2002_2004")%>%
    dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  #ggtitle("Node Number")+
  facet_wrap(~Name, ncol = 3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```
