---
title: "R Notebook"
output: html_notebook
---

```{r Load,echo=TRUE, include = TRUE, warning=FALSE, fig.height=8, fig.width=8}
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)

```

# load data
```{r, echo=FALSE}
upDir <- "D:\\APSIMX2\\Prototypes\\Lucerne\\"
obsF <- "D:\\Model work\\APSIMX\\"
rawObs <- read.table(paste0(obsF, "ObsDataForStats.txt"), 
                      header = TRUE)
unique(rawObs$Name)
```

## Tidy up data
```{r, echo=FALSE}
head(rawObs)
```

* Sort out formats
* Create factor labels
```{r}
# get time format right
obsData <- rawObs %>% mutate(Clock.Today = dmy(Clock.Today))
str(obsData)
head(obsData)
summary(obsData)
```
## Define stats function

* Using Gauch et al. 2003 (Model evaluation by comparison of model-based predictions and measured values. Agron. J. 95, 1442-1446) 
```{r Stats, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

# # R2
# testDF <- data.frame(a=c(1,2,3,4,5), b=c(10,20,10,40,50))
# 
# myR2 <- function(p,o) {
#  return(summary(lm(p~o, na.action=na.exclude))$r.squared) 
# }
# 
# testDF %>%
#   summarise(thisR2 = myR2(a,b))

# gauch MSE components
gauchStats <- function(sim, meas) {

  n_s <- length(sim)
  n_m <- length(meas)
  model <- lm(meas~sim)
  sim_sq <- sum((sim - mean(sim))^2)
  mes_sq <- sum((meas - mean(meas))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]

  sb <- (sum(mean(meas)) - sum(mean(sim)))^2
  nu <- (1-slope)^2 * (sim_sq/n_s)
  lc <- (1-r2) * (mes_sq/n_m)
  msd <- sb+nu+lc

  sb_r <- round((sb/msd)*100,1)
  nu_r <- round((nu/msd)*100,1)
  lc_r <- round((lc/msd)*100,1)

  msd_r <- sb_r+nu_r+lc_r

  # select which variables to output
  out <- c(sb_r,nu_r,lc_r, msd_r, round(r2*100,1))

  return(out)

}
```

## Test stats functions used

```{r}
s <- c(4231.972,3935.604,3779.652,3627.687,3363.499,3230.566,2868.114,2868.827)
m <- c(4987.66,5636.09,4754.06,4114.53,4141.72,3704.06,5142.19,4762.03)

x <- gauchStats(s,m)

tempDf <- data.frame(statName=c("SB","NU","LC","r_MSD","R2"), statValue=x)
# kable(tempDf, digits= 2)
tempDf2 <- data.frame(Predicted=s, Observed=m)

x <- tempDf2 %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>% 
  t() 

df <- data.frame(stat = row.names(x),statvalue = x[,1])

df %>%
  kable(format = "markdown")
```
## Load simulated database
## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```
# load address of db
# set table to be enquierd
# load table into an object
# make it a dataframe
# change date to corerct format 
# explore the df
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneValidation.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
summary(df)
head(df) # simulation results
```
# get sim names (different table)
# merge names 
# remove unecessary variables
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)

# myDb %>%
#   dplyr::select(Name) %>%
#   unique()

```
## Prepare merge
## Add info for merging
## select variables that are for comparing with observed data

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,SWC,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  tidyr::gather("Variable","Predicted",LAI:NodeNumber) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)

head(obsData)
mergedf<-merge(obsData,simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)

```


## Node number
#Time series
## obs Vs Pre for each experiment
## 2010-2012
```{r,fig.height=10, fig.width=8}
obsData%>%
    mutate(Name = as.factor(Name)) %>%
    mutate(Variable = as.factor(Variable)) %>%
    mutate(Clock.Today = ymd_hms(Clock.Today))
  obsData$Clock.Today1 <-as.POSIXct(paste(obsData$Clock.Today,obsData$Time),format="%Y-%m-%d %H:%M:%S")
  obsD<-obsData%>%dplyr::filter(Variable=="NodeNumber")%>%
  mutate(Clock.Today1= ymd_hms(Clock.Today1))
  summary(obsD)
  obsD2<-obsD%>%dplyr::filter(Collection=="2010_2012")
  
 
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Clock.Today>"2010-10-03 12:00:00")%>%
   dplyr::filter(Variable=="NodeNumber")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~Name,ncol = 2)+
 geom_point(data=obsD2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
 theme(axis.title.x=element_text(face="bold",colour="black",size = 14))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 14))

```
## 1997-2001
```{r fig.height=4, fig.width=8}
obsData%>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable))
obsData$Clock.Today1 <-as.POSIXct(paste(obsData$Clock.Today,obsData$Time),format="%Y-%m-%d %H:%M:%S")
obsD<-obsData%>%dplyr::filter(Variable=="NodeNumber")%>%
  mutate(Clock.Today1= ymd_hms(Clock.Today1))
obsD3<-obsD%>%dplyr::filter(Collection=="1997_2001")%>%
 dplyr::filter(Name=="Iversen_8Waterirr")
summary(obsD3)
  
simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  mutate(Name = factor(Name)) %>%
   dplyr::filter(Variable=="NodeNumber")%>%
  #dplyr::filter(Name=="Iversen_8Waterdry"|Name=="Iversen_8Waterirr")
  dplyr::filter(Name=="Iversen_8Waterirr")
str(simD2)
simD2%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
   #facet_wrap(~Name,ncol = 1)+
  geom_point(data=obsD3, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
 
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```

##2002-2004
```{r,  fig.height=4, fig.width=8}
obsData%>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))
obsData$Clock.Today1 <-as.POSIXct(paste(obsData$Clock.Today,obsData$Time),format="%Y-%m-%d %H:%M:%S")
obsD<-obsData%>%dplyr::filter(Variable=="NodeNumber")%>%
  mutate(Clock.Today1= ymd_hms(Clock.Today1))
obsD2<-obsD%>%dplyr::filter(Collection=="2002_2004")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL")
  

simD3<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today<"2004-11-01 12:00:00")%>%
  dplyr::filter(Clock.Today>"2002-07-02 12:00:00")%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  dplyr::filter(Variable=="NodeNumber")%>%
  dplyr::filter(Name!="NekiaDefoliation")
str(simD3)
simD3%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  #facet_wrap(~Name,ncol = 1)+
  geom_point(data=obsD2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 14))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 14))
  
  


```
##2000-2002
```{r,  fig.height=8, fig.width=8}
obsData%>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))
obsData$Clock.Today1 <-as.POSIXct(paste(obsData$Clock.Today,obsData$Time),format="%Y-%m-%d %H:%M:%S")
obsD<-obsData%>%dplyr::filter(Variable=="NodeNumber")%>%
  mutate(Clock.Today1= ymd_hms(Clock.Today1))
obsD2<-obsD%>%dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD1Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD2Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD3Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD4Waterdry")
  

simD4<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2000-10-24 12:00:00")%>%
  dplyr::filter(Clock.Today<"2002-07-01 12:00:00")%>%
  dplyr::filter(Name!="Iversen_8Waterdry")%>%
  dplyr::filter(Name!="Iversen_8Waterirr")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Name!="MooraDefoliation")%>%
  dplyr::filter(Name!="NekiaDefoliation")%>%
  dplyr::filter(Name!="QuairadingDefoliation")%>%
  dplyr::filter(Name!="RoseworthyWaterdry")%>%
  dplyr::filter(Name!="RoseworthyWaterirr")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD1Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD2Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD3Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD4Waterdry")%>%
  dplyr::filter(Variable=="NodeNumber")
  str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 2)+
  geom_point(data=obsD2, aes(x=Clock.Today1, y=Observed),colour="green",size=3)+
  facet_wrap(~Name,ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 14))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 14))
  
  


```


# Statistic and Graph
```{r,  fig.height=10, fig.width=8}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_wrap(~Collection, ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```
##2010-2012
```{r,  fig.height=10, fig.width=10}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
  dplyr::filter(Collection=="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_grid(GrowthSeason~Rotation)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```



```{r,  fig.height=10, fig.width=8}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
    dplyr::filter(Collection=="2010_2012")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_wrap(~Name, ncol = 4)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```


## 2002-2004
```{r,  fig.height=4 fig.width=8}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
    dplyr::filter(Collection=="2002_2004")%>%
    dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  #facet_wrap(~Name, ncol = 3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

```{r,  fig.height=8, fig.width=10}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
    dplyr::filter(Collection=="2002_2004")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_grid(GrowthSeason~Rotation)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```




## 2000-2002
```{r,  fig.height=11, fig.width=10}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
    dplyr::filter(Collection=="2000_2002")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD1Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD2Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD3Waterdry")%>%
  dplyr::filter(Name!="Iversen_9SowingDateSD4Waterdry")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_wrap(~Name, ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

```{r,  fig.height=10, fig.width=10}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
    dplyr::filter(Collection=="2000_2002")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_grid(GrowthSeason~Rotation)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```




## 1997-2001
```{r,  fig.height=8, fig.width=8}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
    dplyr::filter(Collection=="1997_2001")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Node Number")+
  facet_wrap(~Name, ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

```{r,fig.height=8, fig.width=8}
mergedf
summary(mergedf)
str(mergedf)


```


```{r, fig.width=8, fig.height=8, warning=FALSE}
mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
    dplyr::filter(Collection=="1997_2001")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw() +
   geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1) +
  ggtitle("Node Number")  +
  facet_wrap(~Rotation, ncol = 4)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

```{r, fig.width=8, fig.height=10, warning=FALSE}
mergedf %>%
    dplyr::filter(Variable== "NodeNumber") %>% 
    dplyr::filter(Collection=="1997_2001")%>%
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw() +
   geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1) +
  ggtitle("Node Number")  +
  # facet_grid(.~Rotation) + # Rotation
  facet_wrap(~GrowthSeason, ncol = 4)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```




## RMSE

```{r}
str(mergedf)

mergedf %>%
 #filter(Variable == "NodeNumber") %>%
 #filter(Collection=="2010-2012")%>%
  mutate(Rotation= as.factor(Rotation))%>%
  mutate(GrowthSeason=as.factor(GrowthSeason))%>%
  group_by(Variable,Collection) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

# %>%
#   group_by(Variable,Name) %>%
#   summarise_each(funs(mean))
  
```

```{r}
mergedf %>%
 filter(Variable == "NodeNumber") %>%
 #filter(Collection=="1997-2001")%>%
  mutate(Rotation= as.factor(Rotation))%>%
  mutate(GrowthSeason=as.factor(GrowthSeason))%>%
  group_by(GrowthSeason,Collection) %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) 

```

   






<!-- ##New Learn  -->

<!-- ```{r} -->


<!-- df2 <- data.frame(Predicted=c(1,2,3,4,5),Observed=c(1,2,3,4,5)) -->

<!-- df2 %>% -->
<!-- statFun(Predicted,Observed) -->

<!-- statFun <- function (pred, obs){ -->

<!--   df <- data.frame(pred=pred,obs=obs) -->

<!--  out <- df %>%  -->
<!--     summarise( -->
<!--     n = n(), -->
<!--     r2 = gauchStats(pred,obs)[5], -->
<!--     r_rmse = round(rmse(pred,obs)/mean(obs)*100,1), -->
<!--     nse = round(NSE(pred,obs),1), -->
<!--     sb = gauchStats(pred,obs)[1], -->
<!--     nu = gauchStats(pred,obs)[2], -->
<!--     lc = gauchStats(pred,obs)[3] -->
<!--     ) -->

<!--  return(out) -->

<!-- } -->

<!-- mergedf %>% -->
<!-- statFun(Predicted,Observed) -->


<!-- mergedf %>% -->
<!--   filter(Variable == "NodeNumber") %>% -->
<!--   filter(Collection=="1997-2001")%>% -->

<!--   summarise( -->
<!--     n = n(), -->
<!--     r2 = gauchStats(Predicted,Observed)[5], -->
<!--   #  rmse = round(rmse(Predicted,Observed),0), -->
<!--     r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1), -->
<!--     nse = round(NSE(Predicted,Observed),1), -->
<!--     sb = gauchStats(Predicted,Observed)[1], -->
<!--   nu = gauchStats(Predicted,Observed)[2], -->
<!--   lc = gauchStats(Predicted,Observed)[3] -->
<!--   ) %>% -->
<!--   summarise_each(funs(mean)) -->

<!-- ``` -->



# Soil water contect

```{r, , fig.height=8, fig.width=10}
mergedf %>%
    dplyr::filter(Variable== "SWC") %>% 
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=2)+
  geom_smooth(method = "lm", se = TRUE, linetype = 3, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1) +
  ggtitle("Soil water content")+
  facet_wrap(~Name, ncol = 4)+
  theme(legend.title=element_blank())
 
```

```{r}
mergedf %>%
  filter(Variable == "SWC") %>%
  summarise(
    n = n(),
    r2 = gauchStats(Predicted,Observed)[5],
  #  rmse = round(rmse(Predicted,Observed),0),
    r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
    nse = round(NSE(Predicted,Observed),1),
    sb = gauchStats(Predicted,Observed)[1],
  nu = gauchStats(Predicted,Observed)[2],
  lc = gauchStats(Predicted,Observed)[3]
  ) %>%
  summarise_each(funs(mean))
```

<!-- # LAI graph and stats -->
<!-- #Time series -->
<!-- ```{r,  fig.height=50, fig.width=8} -->
<!-- obsData%>% -->
<!--   mutate(Name = as.factor(Name)) %>% -->
<!--   mutate(Variable = as.factor(Variable)) %>% -->
<!--   mutate(Clock.Today = ymd_hms(Clock.Today)) -->
<!-- obsData$Clock.Today1 <-as.POSIXct(paste(obsData$Clock.Today,obsData$Time),format="%Y-%m-%d %H:%M:%S") -->
<!-- obsD<-obsData%>%dplyr::filter(Variable=="LAI")%>% -->
<!--   mutate(Clock.Today1= ymd_hms(Clock.Today1)) -->


<!-- simD%>% -->
<!--   mutate(Clock.Today = ymd_hms(Clock.Today))%>% -->
<!-- dplyr::filter(Variable=="LAI")%>% -->
<!-- ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=0.5)+theme_bw()+ -->
<!--   facet_wrap(~Name,ncol = 2)+ -->
<!--   geom_point(data=obsD, aes(x=Clock.Today1, y=Observed),colour="green",size=2)+ -->
<!--   theme(legend.title=element_blank(),legend.position = "blank")+ -->
<!--   ggtitle("Leaf area index") -->

<!-- ``` -->



# ## stem and leaf
# #Time series
# ```{r,  fig.height=45, fig.width=8}
# obsData%>%
#   mutate(Name = as.factor(Name)) %>%
#   mutate(Variable = as.factor(Variable)) %>%
#   mutate(Clock.Today = ymd_hms(Clock.Today))
# obsData$Clock.Today1 <-as.POSIXct(paste(obsData$Clock.Today,obsData$Time),format="%Y-%m-%d %H:%M:%S")
# obsD<-obsData%>%dplyr::filter(Variable=="StemWt")%>%
#   mutate(Clock.Today1= ymd_hms(Clock.Today1))
#   
# 
# simD%>%
#   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
# dplyr::filter(Variable=="StemWt")%>%
# ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=0.5)+theme_bw()+
#   facet_wrap(~Name,ncol = 2)+
#   geom_point(data=obsD, aes(x=Clock.Today1, y=Observed),colour="green",size=2)+
#   theme(legend.title=element_blank(),legend.position = "blank")+
#   ggtitle("Stem dry matter")
#   
# ```
#  
# ```{r}
# mergedf %>%
#     dplyr::filter(Variable== "StemWt") %>% 
#   ggplot(aes(x=Observed, y= Predicted, 
#           colour= factor(Name))) +
#   geom_point(size=1.5)+
#   geom_smooth(method = "lm", se = TRUE, linetype = 3, colour="darkgrey") +
#   geom_abline(intercept = 0, slope = 1) +
#   coord_fixed(ratio = 1) +
#   facet_grid(~Name)+
#   ggtitle("stem dry matter")+
#   theme(legend.title=element_blank())
# ```
# ```{r}
# mergedf %>%
#   filter(Variable == "StemWt") %>%
#   summarise(
#     n = n(),
#     r2 = gauchStats(Predicted,Observed)[5],
#   #  rmse = round(rmse(Predicted,Observed),0),
#     r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
#     nse = round(NSE(Predicted,Observed),1),
#     sb = gauchStats(Predicted,Observed)[1],
#   nu = gauchStats(Predicted,Observed)[2],
#   lc = gauchStats(Predicted,Observed)[3]
#   ) %>%
#   summarise_each(funs(mean))
# ```
# 
# ##Leaf dry matter
# #Time series
# ```{r,  fig.height=45, fig.width=8}
# obsData%>%
#   mutate(Name = as.factor(Name)) %>%
#   mutate(Variable = as.factor(Variable)) %>%
#   mutate(Clock.Today = ymd_hms(Clock.Today))
# obsData$Clock.Today1 <-as.POSIXct(paste(obsData$Clock.Today,obsData$Time),format="%Y-%m-%d %H:%M:%S")
# obsD<-obsData%>%dplyr::filter(Variable=="StemWt")%>%
#   mutate(Clock.Today1= ymd_hms(Clock.Today1))
#   
# 
# simD%>%
#   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
# dplyr::filter(Variable=="StemWt")%>%
# ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=0.5)+theme_bw()+
#   facet_wrap(~Name,ncol = 2)+
#   geom_point(data=obsD, aes(x=Clock.Today1, y=Observed),colour="green",size=2)+
#   theme(legend.title=element_blank(),legend.position = "blank")+
#   ggtitle("Stem dry matter")
#   
# ```
# 
# 
# ```{r}
# mergedf %>%
#     dplyr::filter(Variable== "LeafWt") %>% 
#   ggplot(aes(x=Observed, y= Predicted, 
#           colour= factor(Name))) +
#   geom_point(size=1.5)+
#   geom_smooth(method = "lm", se = TRUE, linetype = 3, colour="darkgrey") +
#   geom_abline(intercept = 0, slope = 1) +
#   coord_fixed(ratio = 1) +
#   ggtitle("Leaf dry matter")+
#   theme(legend.title=element_blank())
# ```
# ```{r}
# mergedf %>%
#   filter(Variable == "LeafWt") %>%
#   summarise(
#     n = n(),
#     r2 = gauchStats(Predicted,Observed)[5],
#   #  rmse = round(rmse(Predicted,Observed),0),
#     r_rmse = round(rmse(Predicted,Observed)/mean(Observed)*100,1),
#     nse = round(NSE(Predicted,Observed),1),
#     sb = gauchStats(Predicted,Observed)[1],
#   nu = gauchStats(Predicted,Observed)[2],
#   lc = gauchStats(Predicted,Observed)[3]
#   ) %>%
#   summarise_each(funs(mean))
# ```
# 
# ```{r}
# SWC <- myDb %>%
#   dplyr::select(Name,Clock.Today,SWmm.1.,SWmm.2.,SWmm.3.,SWmm.4.,SWmm.5.,SWmm.6.,SWmm.7.,SWmm.8.,SWmm.9.,SWmm.10.,SWmm.11.,SWmm.12.,SWmm.13.,SWmm.14.,SWmm.15.,SWmm.16.,SWmm.17.,SWmm.18.,SWmm.19.,SWmm.20.,SWmm.21.,SWmm.22.,SWmm.23.) %>%
#   mutate(Name = as.factor(Name)) %>%
#   mutate(Clock.Today = ymd_hms(Clock.Today))
# summary(SWC)
# 
# ```
# ```{r}
# obsSWC <- "D:\\R\\"
# obsSW <- read.table(paste0(obsSWC, "Soil water 00_04.txt"), 
#                           header = TRUE)%>%
#  mutate(Name = as.factor(Name)) %>%
#   mutate(Clock.Today = dmy(Clock.Today))
# 
# summary(obsSW)
#SWCdf<-merge(SWC,obsSW,by=c("Clock.Today","Name"))

#SWCdf %>%
  #dplyr::filter(factor=="dry")%>%
  #ggplot(aes(x=SWmm.1., y= SW.1., 
          #colour= factor(Name))) +
  #geom_point(size=2)+
  #geom_smooth(method = "lm", se = TRUE, linetype = 3, colour="darkgrey") +
  #geom_abline(intercept = 0, slope = 1) +
  #coord_fixed(ratio = 1) +
  #theme(legend.title=element_blank())

```

```{r}
# SWC1 <- SWC %>%
#   dplyr::select(Name,Clock.Today,SWmm.1.,SWmm.2.,SWmm.3.,SWmm.4.,SWmm.5.,SWmm.6.,SWmm.7.,SWmm.8.,SWmm.9.,SWmm.10.,SWmm.11.,SWmm.12.,SWmm.13.,SWmm.14.,SWmm.15.,SWmm.16.,SWmm.17.,SWmm.18.,SWmm.19.,SWmm.20.,SWmm.21.,SWmm.22.) %>%
#   tidyr::gather("Variable","Predicted",SWmm.1.:SWmm.22.) %>%
#   mutate(Name = as.factor(Name)) %>%
#   mutate(Variable = as.factor(Variable)) %>%
#   mutate(Clock.Today = ymd_hms(Clock.Today))
# 
# obsSW1 <- obsSW %>%
#   dplyr::select(Name,Clock.Today,SWmm.1.,SWmm.2.,SWmm.3.,SWmm.4.,SWmm.5.,SWmm.6.,SWmm.7.,SWmm.8.,SWmm.9.,SWmm.10.,SWmm.11.,SWmm.12.,SWmm.13.,SWmm.14.,SWmm.15.,SWmm.16.,SWmm.17.,SWmm.18.,SWmm.19.,SWmm.20.,SWmm.21.,SWmm.22.) %>%
#   tidyr::gather("Variable","Observed",SWmm.1.:SWmm.22.)%>%
#   mutate(Variable = as.factor(Variable)) 
#   
# str(SWC1)
# str(obsSW1)
# 
# SWCmmdf<-merge(obsSW1,SWC1,by=c("Name","Clock.Today","Variable"))

  
```

