---
title: "R Notebook"
output: html_notebook
---
## soil water script

```{r Load, warning=FALSE}
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
```

##Work dir
```{r}
Dir <- "D:\\APSIMX2\\Prototypes\\Lucerne\\"
obsF <- "D:\\Model work\\APSIMX\\"
rawObs <- read.table(paste0(obsF, "ObsDataForStats.txt"), 
                      header = TRUE)
unique(rawObs$Name)

```

## create function to read data (Justin's script)
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}
GetApsimNGTable <- function(dbLoc, table) 
{
  connection <- dbConnect(SQLite(), dbname = dbLoc, flags = SQLITE_RW)
  table <- dbReadTable(connection, table, row.names=NULL)
  dbDisconnect(connection)
  return(table)
}

```

## Load sim data
```{r}
db.address <- "D:\\APSIMX2\\Prototypes\\Lucerne\\LucerneValidation.db"
tableName<-"Report"
DbTable <- GetApsimNGTable(db.address,tableName)
df <- as.data.frame(DbTable)
df$Clock.Today <- ymd_hms(df$Clock.Today)
str(df)
summary(df)
head(df) # simulation results
```

# get sim names (different table)
# merge names 
```{r}
simNameDf <- as.data.frame (GetApsimNGTable(db.address,"Simulations"))
myDb <- merge(df, simNameDf, by.x= c("SimulationID"), by.y= c("ID"))


#str(myDb)
head(myDb)
summary(myDb)
```

```{r}
simD <- myDb %>%
  dplyr::select(Name,Clock.Today,LAI,SWC,Height,shootbiomass,RootWt, StemWt, LeafWt,NodeNumber) %>%
  tidyr::gather("Variable","Predicted",LAI:NodeNumber) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))

head(simD)
obsData <- rawObs %>% mutate(Clock.Today = dmy(Clock.Today))
str(obsData)
head(obsData)
summary(obsData)

mergedf<-merge(obsData,simD,by=c("Clock.Today","Name","Variable"))
summary(mergedf)
str(mergedf)

```


## Soil water content
#Time series
## obs Vs Pre for each experiment
## 2010-2012
```{r,fig.height=10, fig.width=8}
obsData%>%
    mutate(Name = as.factor(Name)) %>%
    mutate(Variable = as.factor(Variable)) %>%
    mutate(Clock.Today = ymd_hms(Clock.Today))
  obsData$Clock.Today1 <-as.POSIXct(paste(obsData$Clock.Today,obsData$Time),format="%Y-%m-%d %H:%M:%S")
  obsD<-obsData%>%dplyr::filter(Variable=="SWC")%>%
  mutate(Clock.Today1= ymd_hms(Clock.Today1))
  summary(obsD)
  obsD2<-obsD%>%dplyr::filter(Collection=="2010_2012")
  
 
  unique(simD$Name)
  
 #levOrder <- c("Iversen_12SowingDateSD1","Iversen_12SowingDateSD2","Iversen_12SowingDateSD3","Iversen_12SowingDateSD4","Iversen_12SowingDateSD5","Iversen_12SowingDateSD6","Iversen_12SowingDateSD7","Iversen_12SowingDateSD8", "Iversen_12SowingDateSD9","Iversen_12SowingDateSD10 ","Iversen_8Waterdry"," Iversen_8Waterirr"," Iversen_91DefoliationLL","Iversen_91DefoliationLS","Iversen_91DefoliationSL","Iversen_91DefoliationSS","Iversen_9SowingDateSD1Waterirr","Iversen_9SowingDateSD2Waterirr","Iversen_9SowingDateSD3Waterirr","Iversen_9SowingDateSD4Waterirr","Iversen_9SowingDateSD1Waterdry","Iversen_9SowingDateSD2Waterdry","Iversen_9SowingDateSD3Waterdry","Iversen_9SowingDateSD4Waterdry")
 # mutate(Name=factor(Name, levels=levOrder, labels = c("Heigh (cm)"....)))
 #mutate(simD,Name=factor(Name, levels=levOrder))
        
 simD1<-simD%>%
   mutate(Clock.Today = ymd_hms(Clock.Today))%>%
   dplyr::filter(Clock.Today>"2010-10-03 12:00:00")%>%
   dplyr::filter(Variable=="SWC")
 str(simD1)
 simD1%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
 facet_wrap(~Name,ncol = 2)+
 geom_point(data=obsD2, aes(x=Clock.Today1, y=Observed),colour="brown",size=3)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Soil water content")+
 theme(axis.title.x=element_text(face="bold",colour="black",size = 14))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 14))
 
 
 

```
## 1997-2001
```{r fig.height=8, fig.width=8}
obsData%>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable))
obsData$Clock.Today1 <-as.POSIXct(paste(obsData$Clock.Today,obsData$Time),format="%Y-%m-%d %H:%M:%S")
obsD<-obsData%>%dplyr::filter(Variable=="SWC")%>%
  mutate(Clock.Today1= ymd_hms(Clock.Today1))
obsD3<-obsD%>%dplyr::filter(Collection=="1997_2001")
summary(obsD3)
  
simD2<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  mutate(Name = factor(Name)) %>%
   dplyr::filter(Variable=="SWC")%>%
  dplyr::filter(Name=="Iversen_8Waterdry"|Name=="Iversen_8Waterirr")
str(simD2)
simD2%>%
 ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
   facet_wrap(~Name,ncol = 1)+
  geom_point(data=obsD3, aes(x=Clock.Today1, y=Observed),colour="brown",size=3)+
 
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Soil water content")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```

##2002-2004
```{r,  fig.height=10, fig.width=8}
obsData%>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))
obsData$Clock.Today1 <-as.POSIXct(paste(obsData$Clock.Today,obsData$Time),format="%Y-%m-%d %H:%M:%S")
obsD<-obsData%>%dplyr::filter(Variable=="SWC")%>%
  mutate(Clock.Today1= ymd_hms(Clock.Today1))
obsD2<-obsD%>%dplyr::filter(Collection=="2002_2004")
  

simD3<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today<"2004-11-01 12:00:00")%>%
  dplyr::filter(Clock.Today>"2002-07-02 12:00:00")%>%
dplyr::filter(Variable=="SWC")
str(simD3)
simD3%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 1)+
  geom_point(data=obsD2, aes(x=Clock.Today1, y=Observed),colour="brown",size=3)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 14))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 14))
  
  


```
##2000-2002
```{r,  fig.height=10, fig.width=8}
obsData%>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))
obsData$Clock.Today1 <-as.POSIXct(paste(obsData$Clock.Today,obsData$Time),format="%Y-%m-%d %H:%M:%S")
obsD<-obsData%>%dplyr::filter(Variable=="SWC")%>%
  mutate(Clock.Today1= ymd_hms(Clock.Today1))
obsD2<-obsD%>%dplyr::filter(Collection=="2000_2002")
  

simD4<-simD%>%
  mutate(Clock.Today = ymd_hms(Clock.Today))%>%
  dplyr::filter(Clock.Today>"2000-10-24 12:00:00")%>%
  dplyr::filter(Clock.Today<"2002-07-01 12:00:00")%>%
  dplyr::filter(Name!="Iversen_8Waterdry")%>%
  dplyr::filter(Name!="Iversen_8Waterirr")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLS")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSL")%>%
  dplyr::filter(Name!="Iversen_91DefoliationSS")%>%
  dplyr::filter(Variable=="SWC")
  str(simD4)
simD4%>%
ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=1)+theme_bw()+
  facet_wrap(~Name,ncol = 2)+
  geom_point(data=obsD2, aes(x=Clock.Today1, y=Observed),colour="brown",size=3)+
  facet_wrap(~Name,ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Date")+ylab("Node number")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 14))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 14))
  
  


```

```{r,  fig.height=10, fig.width=8}
mergedf
summary(mergedf)
str(mergedf)

mergedf %>%
    dplyr::filter(Variable== "SWC") %>% 
  ggplot(aes(x=Observed, y= Predicted, 
          colour= factor(Name))) +
  geom_point(size=3)+theme_bw()+
  geom_smooth(method = "lm", se = TRUE, linetype = 1, colour="darkgrey") +
  geom_abline(intercept = 0, slope = 1) +
  coord_fixed(ratio = 1)+
  ggtitle("Soil water content")+
  facet_wrap(~Collection, ncol = 2)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Observed")+ylab("Predicted")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```













































## Select SW soil water
## convert dataframe

```{r}
SWC <- myDb %>%
  dplyr::select(Name,Clock.Today,SWmm.1.,SWmm.2.,SWmm.3.,SWmm.4.,SWmm.5.,SWmm.6.,SWmm.7.,SWmm.8.,SWmm.9.,SWmm.10.,SWmm.11.,SWmm.12.,SWmm.13.,SWmm.14.,SWmm.15.,SWmm.16.,SWmm.17.,SWmm.18.,SWmm.19.,SWmm.20.,SWmm.21.,SWmm.22.,SWmm.23.) %>%
  mutate(Name = as.factor(Name)) %>%
  mutate(Clock.Today = ymd_hms(Clock.Today))
SWC1<-SWC%>%
  dplyr::select(Name,Clock.Today,SWmm.1.,SWmm.2.,SWmm.3.,SWmm.4.,SWmm.5.,SWmm.6.,SWmm.7.,SWmm.8.,SWmm.9.,SWmm.10.,SWmm.11.,SWmm.12.,SWmm.13.,SWmm.14.,SWmm.15.,SWmm.16.,SWmm.17.,SWmm.18.,SWmm.19.,SWmm.20.,SWmm.21.,SWmm.22.) %>%
  tidyr::gather("Variable","Predicted",SWmm.1.:SWmm.22.) %>%
  mutate(Variable = as.factor(Variable)) 

summary(SWC1)
str(SWC1)
```

```{r}
obsSWC <- "D:\\R\\"
obsSW <- read.table(paste0(obsSWC, "Soil water 97_04.txt"), 
                          header = TRUE)%>%
 mutate(Name = as.factor(Name)) %>%
  mutate(Clock.Today = ymd(Clock.Today))
obsSW$Clock.Today1 <-as.POSIXct(paste(obsSW$Clock.Today,obsSW$Time),format="%Y-%m-%d %H:%M:%S")
obsSW%>%
mutate(Clock.Today1 = ymd_hms(Clock.Today1))
obsSW1<-obsSW%>%
  dplyr::select(Name,Clock.Today1,SWmm.1.,SWmm.2.,SWmm.3.,SWmm.4.,SWmm.5.,SWmm.6.,SWmm.7.,SWmm.8.,SWmm.9.,SWmm.10.,SWmm.11.,SWmm.12.,SWmm.13.,SWmm.14.,SWmm.15.,SWmm.16.,SWmm.17.,SWmm.18.,SWmm.19.,SWmm.20.,SWmm.21.,SWmm.22.) %>%
  tidyr::gather("Variable","Observed",SWmm.1.:SWmm.22.) %>%
  mutate(Variable = as.factor(Variable))
unique(obsSW1$Variable)
str(obsSW1)
summary(obsSW1)
```

##Irrigated simulation per layer

```{r,fig.height=50, fig.width=8}
  obsSW2<-obsSW1 %>%
  dplyr::filter(Name=="Iversen_9SowingDateSD1Waterirr")%>%
  dplyr::arrange(desc(Variable))
  str(obsSW2)

  SWC1%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD1Waterirr")%>%
  dplyr::arrange(desc(Variable))%>%
  
  ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=0.5)+theme_bw()+
  facet_wrap(~Variable,ncol = 1)+
  geom_point(data=obsSW2, aes(x=Clock.Today1, y=Observed),colour="brown",size=2)+
  theme(legend.title=element_blank(),legend.position = "blank")+
  ggtitle("Soil water content")

```

##Dryland simulation per layer
```{r fig.height=50, fig.width=8}
  obsSW3<-obsSW1 %>%
  dplyr::filter(Name=="Iversen_9SowingDateSD1Waterdry")
  str(obsSW3)

  SWC1%>%
  dplyr::filter(Name=="Iversen_9SowingDateSD1Waterdry")%>%
  
  ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=0.5)+theme_bw()+
  facet_wrap(~Variable,ncol = 1)+
  geom_point(data=obsSW3, aes(x=Clock.Today1, y=Observed),colour="green",size=2)+
  theme(legend.title=element_blank(),legend.position = "blank")+
  ggtitle("Soil water content")

```

##Irrigated simulation per layer
```{r fig.height=50, fig.width=8}
  obsSW4<-obsSW1 %>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")
  str(obsSW4)
  obsSW4
  

  SWC1%>%
  dplyr::filter(Name=="Iversen_91DefoliationLL")%>%
  
  ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=0.5)+theme_bw()+
  facet_wrap(~Variable, ncol =1)+
  geom_point(data=obsSW4, aes(x=Clock.Today1, y=Observed),colour="green",size=2)+
  theme(legend.title=element_blank(),legend.position = "blank")+
  ggtitle("Soil water content")

```


##Irrigated simulation per layer for I8
```{r fig.height=50, fig.width=8}
  obsSW5<-obsSW1 %>%
  dplyr::filter(Name=="Iversen_8Waterirr")
  str(obsSW5)
  obsSW5
  

  SWC1%>%
  dplyr::filter(Name=="Iversen_8Waterirr")%>%
  
  ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=0.5)+theme_bw()+
  facet_wrap(~Variable, ncol =1)+
  geom_point(data=obsSW5, aes(x=Clock.Today1, y=Observed),colour="green",size=2)+
  theme(legend.title=element_blank(),legend.position = "blank")+
  ggtitle("Soil water content")

```

##dryland simulation per layer for I8
```{r fig.height=50, fig.width=8}
  obsSW6<-obsSW1 %>%
  dplyr::filter(Name=="Iversen_8Waterdry")
  str(obsSW6)
  obsSW6
  

  SWC1%>%
  dplyr::filter(Name=="Iversen_8Waterdry")%>%
  
  ggplot(aes(x=Clock.Today,y=Predicted))+geom_line(size=0.5)+theme_bw()+
  facet_wrap(~Variable, ncol =1)+
  geom_point(data=obsSW6, aes(x=Clock.Today1, y=Observed),colour="green",size=2)+
  theme(legend.title=element_blank(),legend.position = "blank")+
  ggtitle("Soil water content")

```