---
title: "R Notebook"
output: html_notebook
---

## calculate Tt and Ttsum use Beta function

```{r Load, warning=FALSE, fig.height=8, fig.width=8}
# install.packages("zoo")
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)
```

## Load met file
```{r LoadSim, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

met.address <- "D:\\R\\"
met <- read.table(paste0(met.address, "lincolnmet.txt"),
                  header = TRUE)
met%>%
  mutate(Clock.Today=dmy(Clock.Today))

```


## Create Beta function
### Beta function from Bangyou Zheng,CISRO.

```{r}
# we_beta <- function(mint, maxt, t_min, t_opt, t_max, t_ref = t_opt, maxt_weight = 0.5) {
  
# Just you used a single temp param as you'll have in the each 8-h period below
# So tav is a single value - last parameter is not necessary anymore

  we_beta <- function(tav, t_min, t_opt, t_max, t_ref = t_opt) {  

   # tav <- maxt_weight * maxt + (1 - maxt_weight) * mint
   
    res <- ifelse ((tav > t_min) & (tav < t_max),
    {
        a <- log(2.0) / log((t_max - t_min) / (t_opt - t_min))
        
        refeff <- t_opt * (2 * ((tav - t_min)^a) * ((t_opt - t_min)^a) -
                               ((tav - t_min) ^ (2 * a))) / ((t_opt - t_min) ^ (2 * a))
        
        a <- log(2.0) / log((t_max - t_min) / (t_opt - t_min))
        
        refefft <- t_opt * (2 * ((t_ref - t_min)^a) * ((t_opt - t_min)^a) -
                                ((t_ref - t_min) ^ (2 * a))) / ((t_opt - t_min) ^ (2 * a))
        refeff / refefft
    }, 0)

    return (res)
}

```

# Check with params

```{r}

we_beta(0,2,30,45)
we_beta(2,2,30,45)
we_beta(15,2,30,45)
we_beta(30,2,30,45)
we_beta(45,2,30,45)

# Result must be:
# [1] 0
# [1] 0
# [1] 0.4951535
# [1] 1
# [1] 0

```

## Show me the baby

```{r}
df<-data.frame(T=c(-5:45),TT=25)

df %>%
  rowwise() %>%
  mutate(TT=we_beta(T,2,30,40)) %>%
  ggplot(aes(x=T,y=TT)) +
  geom_point()

```

# Create REF Jones CA, Ritchie JT, Kiniry JR, Godwin DC (1986) Subroutine structure.In 'CERES-Maize: A simulation model of maize growth anddevelopment'. (Eds CA Jones, JR Kiniry) pp. 49-194. (Texas A&M University Press: Texas, USA

```{r}

TTfunc <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
  } 
  
  Topt <- 30
  TTav <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2
            + 0.0053 * n^3) * (Tmax-Tmin)) + Tmin # 8-h temperature
    
    TT_tn <- we_beta(tn,2,30,40) * tn # beta-fun parameters are hardcoded here ... these can/should be externalised
    
    TTsum <- max(TT_tn,0) + TTsum
    
 #   print(TT_tn)
    
    }
  TTav <- TTsum/8
  
  return(TTav)
  }



```

##Test

```{r}
df2<-data.frame(mint=c(0:40)) %>%
  mutate(maxt=mint+0.2*mint)  %>%
  rowwise() %>%
  mutate(TT=TTfunc(mint,maxt)) %>%
  mutate(Tav=((maxt+mint)*0.5)) 

summary(df2)

```

```{r,fig.height=4, fig.width=5}
df2 %>%
  ggplot(aes(x=Tav,y=TT)) +
  geom_point(size=1.5)+theme_bw()+xlab("Ta(°C)")+ylab("Tt (°Cd)")+
 theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```
### Tb=1
##create beta function
## Interpolate in 8 periods as 3 hours intervals
## calculate TTWE1
```{r}
TTfunc <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
  } 
  
  Topt <- 30
  TTav <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2
            + 0.0053 * n^3) * (Tmax-Tmin)) + Tmin # 8-h temperature
    
    TT_tn <- we_beta(tn,1,30,40) * tn # beta-fun parameters are hardcoded here ... these can/should be externalised
    
    TTsum <- max(TT_tn,0) + TTsum
    
 #   print(TT_tn)
    
    }
  TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc(10,30)

```
## calculate TTWE1
```{r}

metTTWE1 <- met%>%
  mutate(Clock.Today=dmy(Clock.Today))%>%
   filter(Clock.Today>="1996-01-01") %>%
  rowwise() %>%
  mutate(TTWE1=TTfunc(mint,maxt))
metTTWE1
write.csv(metTTWE1,"D:/R/metTTWE/metTTWE1.csv", row.names = FALSE)

```
```{r}
metTTWE1%>%
  ggplot(aes(x=mean, y=TTWE1))+
  geom_point()

```
### Tb=2
##create beta function
## Interpolate in 8 periods as 3 hours intervals
## calculate TTWE2
```{r}
TTfunc2 <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
  } 
  
  Topt <- 30
  TTav <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2
            + 0.0053 * n^3) * (Tmax-Tmin)) + Tmin # 8-h temperature
    
    TT_tn <- we_beta(tn,2,30,40) * tn # beta-fun parameters are hardcoded here ... these can/should be externalised
    
    TTsum <- max(TT_tn,0) + TTsum
    
 #   print(TT_tn)
    
    }
  TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc2(10,30)

```
#TT2
```{r}
metTTWE2 <- met%>%
  mutate(Clock.Today=dmy(Clock.Today))%>%
   filter(Clock.Today>="1996-01-01") %>%
  rowwise() %>%
  mutate(TTWE2=TTfunc2(mint,maxt))
metTTWE2
write.csv(metTTWE2,"D:/R/metTTWE/metTTWE2.csv", row.names = FALSE)
```
```{r}
metTTWE2%>%
  ggplot(aes(x=mean, y=TTWE2))+
  geom_point()

```

### Tb=3
##create beta function
## Interpolate in 8 periods as 3 hours intervals
## calculate TTWE3
```{r}
TTfunc3 <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
  } 
  
  Topt <- 30
  TTav <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2
            + 0.0053 * n^3) * (Tmax-Tmin)) + Tmin # 8-h temperature
    
    TT_tn <- we_beta(tn,3,30,40) * tn # beta-fun parameters are hardcoded here ... these can/should be externalised
    
    TTsum <- max(TT_tn,0) + TTsum
    
 #   print(TT_tn)
    
    }
  TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc3(10,30)

```

```{r}
metTTWE3 <- met %>%
  mutate(Clock.Today=dmy(Clock.Today))%>%
   filter(Clock.Today>="1996-01-01") %>%
  rowwise() %>%
  mutate(TTWE3=TTfunc3(mint,maxt))
metTTWE3
write.csv(metTTWE3,"D:/R/metTTWE/metTTWE3.csv", row.names = FALSE)
```

```{r}
metTTWE3%>%
  ggplot(aes(x=mean, y=TTWE3))+
  geom_point()

```
### Tb=4
##create beta function
## Interpolate in 8 periods as 3 hours intervals
## calculate TTWE4
```{r}
TTfunc4 <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
  } 
  
  Topt <- 30
  TTav <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2
            + 0.0053 * n^3) * (Tmax-Tmin)) + Tmin # 8-h temperature
    
    TT_tn <- we_beta(tn,4,30,40) * tn # beta-fun parameters are hardcoded here ... these can/should be externalised
    
    TTsum <- max(TT_tn,0) + TTsum
    
 #   print(TT_tn)
    
    }
  TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc4(10,30)

```
```{r}
metTTWE4 <- met%>%
  mutate(Clock.Today=dmy(Clock.Today))%>%
   filter(Clock.Today>="1996-01-01") %>%
  rowwise() %>%
  mutate(TTWE4=TTfunc4(mint,maxt))
metTTWE4
write.csv(metTTWE4,"D:/R/metTTWE/metTTWE4.csv", row.names = FALSE)
```
### Tb=5
##create beta function
## Interpolate in 8 periods as 3 hours intervals
## calculate TTWE5
```{r}
TTfunc5 <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
  } 
  
  Topt <- 30
  TTav <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2
            + 0.0053 * n^3) * (Tmax-Tmin)) + Tmin # 8-h temperature
    
    TT_tn <- we_beta(tn,5,30,40) * tn # beta-fun parameters are hardcoded here ... these can/should be externalised
    
    TTsum <- max(TT_tn,0) + TTsum
    
 #   print(TT_tn)
    
    }
  TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc5(10,30)

```

```{r}
metTTWE5 <- met %>%
  mutate(Clock.Today=dmy(Clock.Today))%>%
   filter(Clock.Today>="1996-01-01") %>%
  rowwise() %>%
  mutate(TTWE5=TTfunc5(mint,maxt))
metTTWE5
write.csv(metTTWE5,"D:/R/metTTWE/metTTWE5.csv", row.names = FALSE)
```
##Combine metTTWE
```{r,fig.height=5, fig.width=10,warning=FALSE}
multmerge = function(mypath){
filenames=list.files(path=mypath, full.names=TRUE)
datalist = lapply(filenames, function(x){read.csv(file=x,header=T)})
Reduce(function(x,y) {merge(x,y)}, datalist)}

mergemetTTWE=multmerge("D:/R/MetTTWE")
mergemetTTWE
```
## creat TTsum
```{r}
mergemetTTWE$TTWEsum1<-cumsum(mergemetTTWE$TTWE1)
mergemetTTWE$TTWEsum2<-cumsum(mergemetTTWE$TTWE2)
mergemetTTWE$TTWEsum3<-cumsum(mergemetTTWE$TTWE3)
mergemetTTWE$TTWEsum4<-cumsum(mergemetTTWE$TTWE4)
mergemetTTWE$TTWEsum5<-cumsum(mergemetTTWE$TTWE5)
metTTwe<-mergemetTTWE%>%
  mutate(Clock.Today=ymd(Clock.Today))
metTTwe
write.csv(metTTwe,"D:/R/metTTWE/metTTwe.csv", row.names = FALSE)
```
## Load metTTbs file
## merge metTTbs and metTTWE
```{r LoadSim, include = TRUE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

met.address <- "D:\\R\\MetTT\\"
metTTbs <- read.table(paste0(met.address, "metTTBS.txt"),
                  header = TRUE)
metTTbs1<-metTTbs%>%
  mutate(Clock.Today=dmy(Clock.Today))
metTTbs1
metTTwe%>%
  mutate(Clock.Today=dmy(Clock.Today))
##merge two data table together  

metTTs<-merge(metTTwe,metTTbs1,by=c("year","day","rain","maxt","mint","mean","radn","wind","vp","Pp", "Clock.Today"))
metTTs
write.csv(metTTs,"D:/R/metTTs.csv", row.names = FALSE)

```
