---
title: "R Notebook"
output: html_notebook
---

## Read met file.
## Read Observed data
## calculate Tt and Ttsum

```{r Load, warning=FALSE, fig.height=8, fig.width=8}
# install.packages("zoo")
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)


```

# load data
```{r, echo=FALSE}
upDir <- "D:\\APSIMX2\\Prototypes\\Lucerne\\"
obsF <- "D:\\Model work\\APSIMX\\"
obs <- read.table(paste0(obsF, "ObsDataForStats.txt"), 
                      header = TRUE)

obs<-obs%>%
  mutate(Rotation = factor(Rotation))
obs <- obs %>% mutate(Clock.Today = dmy(Clock.Today))
head(obs)
```

```{r}
# get time format right
obsData <- obs %>% mutate(Clock.Today = dmy(Clock.Today))
str(obsData)
head(obsData)
summary(obsData)
```


## Load met file
```{r LoadSim, include = FALSE, echo=FALSE, warning=FALSE, fig.height=8, fig.width=8}

met.address <- "D:\\R\\"
met <- read.table(paste0(met.address, "lincolnmet.txt"), 
                      header = TRUE)
metData <- met %>% mutate(Clock.Today = dmy(Clock.Today))
metData$Tt5<-(metData$maxt-metData$mint)/2-metData$Tb5
str(metData)


```
## graph

```{r, fig.height=10, fig.width=10}

metData %>%
  ggplot(aes(x=Clock.Today,y=maxt)) +
  geom_point()

```
## load function
## Define Tt cardinal temperatures
#Create Thermal time cardinal temperatures (lucerne.xml in APSIM line 206)
Considered an overall average the following references:
Tb: 0.0
Top range:18-25
Tmax: 40
```{r,fig.height=4, fig.width=6}
Thermaltime <-data.frame(a=c(5, 30, 40),b=c(0, 25, 0))
Thermaltime%>%
  ggplot(aes(x=a, y=b))+
  labs(x="Mean air temperature (°C)")+
  labs(y="Thermal Time (°Cd/day)") +
  theme_bw()+
  geom_line(size=1)+
  theme(legend.title=element_blank(),legend.position = "blank")+
 theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```


```{r,fig.height=4, fig.width=6}
tt_card <- data.frame(temp=c(1.0,  5.0,  10,  15,  30,  40),
                      TT=c(0.0,  3.0,  6.5, 10,  25,  0.0))
tt_card %>%
  ggplot(aes(x=temp, y=TT))+
  labs(x="Mean air temperature (°C)")+
  labs(y="Thermal Time (°Cd/day)") +
  theme_bw()+
  geom_line(size=1)+
  theme(legend.title=element_blank(),legend.position = "blank")+
 theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

```
# Create and test interpolation function 
```{r}

temp_ref  <- 25 # x-axes reference
temp <- tt_card$temp # x-axes
TT <- tt_card$TT # y-axes


int_func <- function(temp,TT,temp_ref){

# if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   out <- TT[length(TT)] 
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
# else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  
int_func(temp,TT,temp_ref)

```
#create REF Jones CA, Ritchie JT, Kiniry JR, Godwin DC (1986) Subroutine structure.In 'CERES-Maize: A simulation model of maize growth anddevelopment'. (Eds CA Jones, JR Kiniry) pp. 49-194. (Texas A&M University Press: Texas, USA

```{r}

TTfunc <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
 } 
  
  TTav  <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2
            + 0.0053 * n^3) * (Tmax-Tmin)) + 
      Tmin # 8-h temperature
    
    TT_tn <- int_func(tt_card$temp, tt_card$T,tn) 
    
    TTsum <- max(TT_tn,0) + TTsum
    
 #   print(TT_tn)
    
    }
  TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc(10,30)

```
```{r ReadCalcTt}

Tb=5 # assuming a base temperature of 8 for the simple calculation

metTT <- metData %>%
   filter(Clock.Today>"1998-01-01") %>%
  rowwise() %>%
  mutate(TTday=TTfunc(mint,maxt), TTday_s=max(((mint+maxt)/2)-Tb,0), diff=(TTday_s/TTday)*100)
```



```{r}
metTT %>% 
ggplot(aes(x=TTday_s, y= TTday)) +
    geom_point(shape=21,alpha=0.2) +
  geom_abline(intercept = 0, slope = 1)


```

## creat TTsum
```{r}

metTT$TTsum<-cumsum(metTT$TTday)

```

## Merge TTsum with Observed Data
```{r}
dfTp <- metTT %>% dplyr::select(Clock.Today, TTsum, Pp)%>%
  mutate(Clock.Today=ymd(Clock.Today))

obscom<-merge(dfTp,obs, by=c("Clock.Today")) 

write.csv(metTT,"D:/R/Data statistic/metTT.csv", row.names = FALSE)

```


## calculate phyllo

```{r}

nodes <- obscom %>%dplyr::filter(Variable=="NodeNumber")

phylloData <- nodes %>%
  group_by(Name,GrowthSeason,Rotation,Collection) %>%
  do(mod = lm(TTsum ~Observed,data=.)) %>%
  mutate(Slope = summary(mod)$coeff[2]) %>%
  dplyr::select(-mod)
  #nodes$GrowthRotation<-factor(paste(nodes$GrowthSeason,nodes$Rotation))
  #ggplot(nodes, x=GrowthRotation, y=Slope)+geom_line(size=2)

write.csv(phylloData,"D:/R/Data statistic/Data.csv", row.names = FALSE)
phylloData
  

```
### load phyllochron data
### check met file
```{r}
phyllo.address <- "D:\\R\\Data statistic\\"
phyllo <- read.table(paste0(phyllo.address, "Phyllochron.txt"), 
                       header = TRUE)
phyllo
phyllo1 <- phyllo %>% mutate(Clock.Today = dmy(Clock.Today))

phyllo1
summary(metTT)

```

##merge with met file for photoperiod
```{r}
phyphoto<-merge(phyllo1,metTT,by=c("Clock.Today"))


phyphoto

```




```{r,fig.height=8, fig.width=8,warning=FALSE}
df <- data.frame(Photoperiod=c(8.5,10.5,12.5,16.5),Phyollchron = c(51,51,34,34))
df%>%
  ggplot(aes(x=Photoperiod,y=Phyollchron))+theme_bw()+geom_line(size=1)+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

phyphoto1<-phyphoto %>%
  dplyr::filter(Water=="irr")%>%
  dplyr::filter(Collection!="2002_2004")%>%
  dplyr::filter(Name!="Iversen_91DefoliationLL")
 
  
 
df %>%
  ggplot(aes(x=Photoperiod, y=Phyollchron)) +theme_bw()+geom_line(size=1)+
 geom_point(data=phyphoto1, aes(x=Pp, y=Phyllochron),colour="black",size=3)+
  facet_wrap(~Name, ncol=2)+
  #facet_wrap(~Stage, ncol=2)+
 theme(legend.title=element_blank(),legend.position = "blank")+xlab("Photoperiod")+ylab("Phyollchron")+
 theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
 theme(axis.title.y=element_text(face="bold",colour="black",size = 12))
```

##use lm for linear regression model between photoperiod and phyllochron 
```{r,fig.height=5, fig.width=8,warning=FALSE}
phyphoto1%>%
  ggplot(aes(x=Pp, y=Phyllochron),colour= factor(Name)) +theme_bw()+geom_point(size=2)+
  facet_wrap(~Stage,ncol = 2)+
  geom_smooth(method="lm",forumula=Pp~Phyllochron)+
  theme(legend.title=element_blank(),legend.position = "blank")+xlab("Photoperiod")+ylab("Phyllochron")+
  theme(axis.title.x=element_text(face="bold",colour="black",size = 12))+
  theme(axis.title.y=element_text(face="bold",colour="black",size = 12))

  


```

##ANOVA analysis
```{r}
phyphoto2<- phyphoto1%>%
  dplyr::filter(Stage=="Seedling")
AnovaResult <- aov(Phyllochron~Pp, data=phyphoto2)
summary(AnovaResult)

```

```{r}
phyphoto2<- phyphoto1%>%
  dplyr::filter(Stage=="Regrowth")
AnovaResult <- aov(Pp~Phyllochron, data=phyphoto2)
summary(AnovaResult)

```

