---
title: "R Notebook"
output: html_notebook
---

# Example script to test how to implement various Tt calculations

```{r Load, warning=FALSE, fig.height=8, fig.width=8}
# install.packages("zoo")
library(dplyr)
library(ggplot2)
library(lubridate)   
library(hydroGOF)
library(xtable)
library(knitr)
library(tidyr)
library(RSQLite)
library(agricolae)
library(scales)
library(zoo)
```

# get raw data

```{r}
upDir <- "D:/R/"
obsData <- "D:/R/"

ExpList_raw<- read.table(paste0(obsData, "ExperimentList.txt"),
                       header = TRUE)
summary(ExpList_raw)
ExpList_raw

```

## Tidy up and clean up data

```{r}
ExpList_worked <- ExpList_raw %>%
  mutate(StartDate=dmy(StartDate),MidDate=dmy(MidDate),FinishDate=dmy(FinishDate)) %>%
  mutate(SowingDate=as.factor(ifelse(SowingDate=="no","Sd_No",paste0("Sd_",SowingDate)))) %>% # assume this is typo to be fixed?
  mutate(GrowthSeason=as.factor(paste0("Gs_",GrowthSeason))) %>% # creating more intuitive labels here
  mutate(Rotation=as.factor(paste0("Rt_",Rotation))) %>%
  mutate(ExpUnitCode=as.factor(paste0(Experiment,Water,Defoliation,SowingDate,FD,GrowthSeason,Rotation))) 

  
summary(ExpList_worked)
```

### Get met files

```{r}

upDir <- "D:/R/"
obsData <- "D:/R/"


MetLincoln_raw<- read.table(paste0(obsData,"Lincolnmet.txt"),
                       header = TRUE)

MetLincoln_worked <- MetLincoln_raw %>%
  mutate(Clock.Today=dmy(Clock.Today))%>%
  filter(Clock.Today>="1996-01-01")

summary(MetLincoln_worked)

```

## Define functions to calculate Thermel-time

### Method 1: simple Tt with fixed Tb (not for use in your project)

- for testing script only
- ... and show how to set functions

Describe method 1

```{r}

# Set a fixed base temperature
TB <- 5

# Tt calc method 1
ttBaby <- function(tn,tx, tb){
  
  # test if Tn is < Tx as robustness
  if(tn>tx) {
    print("Minimum temp > max temp")
    break
    }
  
  ta <- (tn+tx)*0.5
  
  return(max(0,ta-tb))
  
}

# Test it

TN<- -10
TX<- 0
TB<- 5

ttBaby(TN,TX,TB) # should give 10 as result


```

### Method 2: we_beta function 

Describe method 2

```{r}

  we_beta <- function(temp_input, t_min, t_opt, t_max, t_ref = t_opt) {  

   # temp_input <- maxt_weight * maxt + (1 - maxt_weight) * mint
   
    res <- ifelse ((temp_input > t_min) & (temp_input < t_max),
    {
        a <- log(2.0) / log((t_max - t_min) / (t_opt - t_min))
        
        refeff <- t_opt * (2 * ((temp_input - t_min)^a) * ((t_opt - t_min)^a) -
                               ((temp_input - t_min) ^ (2 * a))) / ((t_opt - t_min) ^ (2 * a))
        
        a <- log(2.0) / log((t_max - t_min) / (t_opt - t_min))
        
        refefft <- t_opt * (2 * ((t_ref - t_min)^a) * ((t_opt - t_min)^a) -
                                ((t_ref - t_min) ^ (2 * a))) / ((t_opt - t_min) ^ (2 * a))
        refeff / refefft
    }, 0)

    return (res)
  }

# test it
#betaParam <- c(i,30,40) # temperatures 

# for(i in 0:5){
#   
#   betaParam<- c(i,30,40)
#   
#   x<-we_beta(15,betaParam[1],betaParam[2],betaParam[3])
#   print(x)
# }



#####################################################################################

# TT calculation using beta function

TTfunc_beta <- function(Tmin ,Tmax, bp){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
  } 
  
#  Topt <- 30
  TTav <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2
            + 0.0053 * n^3) * (Tmax-Tmin)) + Tmin # 8-h temperature
    
    TT_tn <- we_beta(tn,bp[1],bp[2],bp[3]) * tn 
    TTsum <- max(TT_tn,0) + TTsum
    
 #   print(TT_tn)
    
    }
  TTav <- TTsum/8
  
  return(TTav)
}

# # test TT function
# TTfunc_beta(5,20,betaParam)
# 
# TTbeta<-MetLincoln_worked %>%
#   rowwise() %>%
#   mutate(TTbeta=TTfunc_beta(mint,maxt,betaParam))
# TTbeta
#testing change parameters value

df_all_tb<-data.frame()

for(i in 1:5){
  
  betaParam <- c(i,30,40)
  
  loopIndex<-i
  
  df_res<-MetLincoln_worked %>%
  mutate(Tb=loopIndex) %>%
  rowwise() %>%
  mutate(TTbeta=TTfunc_beta(mint,maxt,betaParam))
  
  df_all_tb<-rbind(df_all_tb,df_res)
  
}
df_all_tb
write.csv(df_all_tb,"D:/R/TtAll/df_all_tb.csv", row.names = FALSE)

```
```{r}
#test
MetLincoln<-MetLincoln_worked%>%
  mutate(Dif=maxt-mint)%>%
  filter(Dif<0)
MetLincoln
```



## Method 3: broken stick and fick function 

Based on: APSIM from Jones CA, Ritchie JT, Kiniry JR, Godwin DC (1986) Subroutine structure.In 'CERES-Maize: A simulation model of maize growth anddevelopment'. (Eds CA Jones, JR Kiniry) pp. 49-194. (Texas A&M University Press: Texas, USA

```{r}

# Create a TT linear interpolation function

# Aim: Interpolates linearly between two known x-y pairs

int_func <- function(temp,TT,temp_ref){

# if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   out <- TT[length(TT)] 
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
# else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  

# Test and test interpolation function 

# Set an input cardinal temperature df
tt_card <- data.frame(x_ref=c(1.0,  5.0,  10,  15,  30,  40),
                      y_ref=c(0.0,  3.0,  6.5, 10,  25,  0.0))

temp_ref  <- 25 # random input x-axes value to test
temp <- tt_card$x_ref # x-axes
TT <- tt_card$y_ref # y-axes

int_func(temp,TT,temp_ref) # result must be 20

####################################################################################

# Create TT calculation based on broken-stick
# that uses the interpolation function
# Aim: Finds thermal-time in between any given broken-stick cardinal temperature set

TTfunc_broken <- function(Tmin ,Tmax, tt_card){ # Tmin and Tmax are numeric, tt_card is data.frame         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
 } 
  
  TTav  <- 0
  TTsum <- 0
  
  perPerDay <- 8 # how many periods per day - hardwired param here
  
  # break 24 h into 8 periods of 3 h
  for(n in 1:perPerDay){ 
    
    tn <- 0 # temperature at period n (x axes)
    
    TT_tn <- 0 # thermal-time at period n (y axes)
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2
            + 0.0053 * n^3) * (Tmax-Tmin)) + 
      Tmin # 8-h temperature
    
    TT_tn <- int_func(tt_card$x_ref, tt_card$y_ref,tn) # finds TT (y axes) for a given temperature (x axes) at period n
    
    TTsum <- max(TT_tn,0) + TTsum
    
 #   print(TT_tn)
    
    }

  TTav <- TTsum/perPerDay
  
  return(TTav)
  }

# test thermal-time function
# TTfunc_broken(10,30, tt_card) # result must be 15.47005
# TTbroken<-MetLincoln_worked %>%
#  rowwise() %>%
#  mutate(TTbroken=TTfunc_broken(mint,maxt,tt_card))
#  TTbroken
 ###########################################################
 df_all_broken<-data.frame()

for(i in 1:5){
  
  tt_card <- data.frame(x_ref=c(i, 15,  30,  40),
                        y_ref=c(0.0, 10,  25,  0.0))
  
  loopIndex<-i
  
  df_res_broken<-MetLincoln_worked %>%
  mutate(Tbb=loopIndex) %>%
  rowwise() %>%
  mutate(TTbroken=TTfunc_broken(mint,maxt, tt_card))
  
  df_all_broken<-rbind(df_all_broken,df_res_broken)
  
}

df_all_broken
write.csv(df_all_broken,"D:/R/TtAll/df_all_broken.csv", row.names = FALSE)
 ###########################################################
 df_all_fick<-data.frame()

for(i in 1:5){
  
  tt_card <- data.frame(x_ref=c(i, 30,  40),
                        y_ref=c(0.0,  25,  0.0))
  
  loopIndex<-i
  
  df_res_fick<-MetLincoln_worked %>%
  mutate(TbF=loopIndex) %>%
  rowwise() %>%
  mutate(TTfick=TTfunc_broken(mint,maxt, tt_card))
  
  df_all_fick<-rbind(df_all_fick,df_res_fick)
  
}

df_all_fick
write.csv(df_all_fick,"D:/R/TtAll/df_all_fick.csv", row.names = FALSE)
```

##combine three datasets together

```{r}
# df_Tb<- df_all_tb%>%
#     mutate(year=factor(year),day=factor(day),rain=factor(rain),maxt=factor(maxt),mint=factor(mint),
#     mean=factor(mean),radn=factor(radn),wind=factor(wind),vp=factor(vp),Clock.Today=dmy(Clock.Today),Pp=factor(Pp))
#   
# df_Tbroken<-df_all_broken %>% 
#   mutate(year=factor(year),day=factor(day),rain=factor(rain),maxt=factor(maxt),mint=factor(mint),mean=factor(mean),radn=factor(radn),wind=factor(wind),vp=factor(vp),Clock.Today=dmy(Clock.Today),Pp=factor(Pp))
# 
# 
# df_Tfick<-df_all_fick%>%
#   mutate(year=factor(year),day=factor(day),rain=factor(rain),maxt=factor(maxt),mint=factor(mint),mean=factor(mean),radn=factor(radn),wind=factor(wind),vp=factor(vp),Clock.Today=dmy(Clock.Today),Pp=factor(Pp))
# 
# mergeTt<- merge(df_all_broken,df_all_fick,by=C("Clock.Today"))
```

```{r}
upDir <- "D:/R/"
obsData <- "D:/R/TtAll/"

TtAll<- read.table(paste0(obsData, "TtAll.txt"),
                       header = TRUE)%>%
  mutate(Clock.Today=dmy(Clock.Today))
TtAll

```


## Apply different Tt methods

- Segment datasets in individual rotations
- Apply all methdos to calculate Tt
- Calculate Tt sums for each method

```{r}

# add function to "turn-off" rowise() in dplyr. FIXME: maybe there's a better/simpler solution?
ungroup.rowwise_df <- function(x) {
  class(x) <- c( "tbl_df", "data.frame")
  x
}

uniTb <- unique(TtAll$Tb)

UniExp <- unique(ExpList_worked$ExpUnitCode)

df.all <- data.frame()
 
for(i in 1:length(uniTb)){
  
  TtAll1 <- TtAll %>%
  filter(Tb==uniTb[i])  
  

for(i in 1:length(UniExp))
{

 # print(i)
  
 Exp.sub <- ExpList_worked %>%
   filter(ExpUnitCode==UniExp[i]) 
  
 StDate <- ymd(Exp.sub$StartDate)
 EndDate <- ymd(Exp.sub$FinishDate)
  
Met.sub<-TtAll1 %>%
  filter(between(Clock.Today,StDate,EndDate))
  

tt.df <- Met.sub %>% 
  rowwise() %>%
  mutate(ExpName=Exp.sub$ExpUnitCode, 
         Experiment=Exp.sub$Experiment,
         Water=Exp.sub$Water,
         Defoliation=Exp.sub$Defoliation,
         SowingDate=Exp.sub$SowingDate,
         FD=Exp.sub$FD,
         GrowthSeason=Exp.sub$GrowthSeason,
         Rotation=Exp.sub$Rotation) %>%
         ungroup.rowwise_df()%>% 
         mutate( Tt_beta_sum = cumsum(cumsum(TTbeta)),
                  Tt_fick_sum =cumsum(cumsum(TTfick)),
                  Tt_broken_sum= cumsum(cumsum(TTbroken)))
 df.all <- rbind(df.all,tt.df)

}}

summary(df.all)
df.all
write.csv(df.all,"D:/R/TtAll/df.all.csv", row.names = FALSE)

```

